### 2024-11-06 paper/paper.tex
Imported acmart

%%
%% This is file `sample-manuscript.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `all,proceedings,bibtex,manuscript')
%%
%% IMPORTANT NOTICE:
%%
%% For the copyright see the source file.
%%
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-manuscript.tex.
%%
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%%
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%%
%% Commands for TeXCount
%TC:macro \cite [option:text,text]
%TC:macro \citep [option:text,text]
%TC:macro \citet [option:text,text]
%TC:envir table 0 1
%TC:envir table* 0 1
%TC:envir tabular [ignore] word
%TC:envir displaymath 0 word
%TC:envir math 0 word
%TC:envir comment 0 0
%%
%%
%% The first command in your LaTeX source must be the \documentclass
%% command.
%%
%% For submission and review of your manuscript please change the
%% command to \documentclass[manuscript, screen, review]{acmart}.
%%
%% When submitting camera ready or to TAPS, please change the command
%% to \documentclass[sigconf]{acmart} or whichever template is required
%% for your publication.
%%
%%
\documentclass[manuscript,screen,review]{acmart}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmlicensed}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{XXXXXXX.XXXXXXX}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Conference acronym 'XX]{Make sure to enter the correct
  conference title from your rights confirmation emai}{June 03--05,
  2018}{Woodstock, NY}
%%
%%  Uncomment \acmBooktitle if the title of the proceedings is different
%%  from ``Proceedings of ...''!
%%
%%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
%%  June 03--05, 2018, Woodstock, NY}
\acmISBN{978-1-4503-XXXX-X/18/06}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% For managing citations, it is recommended to use bibliography
%% files in BibTeX format.
%%
%% You can then either use BibTeX with the ACM-Reference-Format style,
%% or BibLaTeX with the acmnumeric or acmauthoryear sytles, that include
%% support for advanced citation of software artefact from the
%% biblatex-software package, also separately available on CTAN.
%%
%% Look at the sample-*-biblatex.tex files for templates showcasing
%% the biblatex styles.
%%

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{The Name of the Title Is Hope}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Ben Trovato}
\authornote{Both authors contributed equally to this research.}
\email{trovato@corporation.com}
\orcid{1234-5678-9012}
\author{G.K.M. Tobin}
\authornotemark[1]
\email{webmaster@marysville-ohio.com}
\affiliation{%
  \institution{Institute for Clarity in Documentation}
  \city{Dublin}
  \state{Ohio}
  \country{USA}
}

\author{Lars Th{\o}rv{\"a}ld}
\affiliation{%
  \institution{The Th{\o}rv{\"a}ld Group}
  \city{Hekla}
  \country{Iceland}}
\email{larst@affiliation.org}

\author{Valerie B\'eranger}
\affiliation{%
  \institution{Inria Paris-Rocquencourt}
  \city{Rocquencourt}
  \country{France}
}

\author{Aparna Patel}
\affiliation{%
 \institution{Rajiv Gandhi University}
 \city{Doimukh}
 \state{Arunachal Pradesh}
 \country{India}}

\author{Huifen Chan}
\affiliation{%
  \institution{Tsinghua University}
  \city{Haidian Qu}
  \state{Beijing Shi}
  \country{China}}

\author{Charles Palmer}
\affiliation{%
  \institution{Palmer Research Laboratories}
  \city{San Antonio}
  \state{Texas}
  \country{USA}}
\email{cpalmer@prl.com}

\author{John Smith}
\affiliation{%
  \institution{The Th{\o}rv{\"a}ld Group}
  \city{Hekla}
  \country{Iceland}}
\email{jsmith@affiliation.org}

\author{Julius P. Kumquat}
\affiliation{%
  \institution{The Kumquat Consortium}
  \city{New York}
  \country{USA}}
\email{jpkumquat@consortium.net}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Trovato et al.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  A clear and well-documented \LaTeX\ document is presented as an
  article formatted for publication by ACM in a conference proceedings
  or journal publication. Based on the ``acmart'' document class, this
  article presents and explains many of the common variations, as well
  as many of the formatting elements an author may use in the
  preparation of the documentation of their work.
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>00000000.0000000.0000000</concept_id>
  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>00000000.00000000.00000000</concept_id>
  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>00000000.00000000.00000000</concept_id>
  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>00000000.00000000.00000000</concept_id>
  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
\ccsdesc[300]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
\ccsdesc{Do Not Use This Code~Generate the Correct Terms for Your Paper}
\ccsdesc[100]{Do Not Use This Code~Generate the Correct Terms for Your Paper}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{Do, Not, Us, This, Code, Put, the, Correct, Terms, for,
  Your, Paper}

\received{20 February 2007}
\received[revised]{12 March 2009}
\received[accepted]{5 June 2009}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\section{Introduction}
ACM's consolidated article template, introduced in 2017, provides a
consistent \LaTeX\ style for use across ACM publications, and
incorporates accessibility and metadata-extraction functionality
necessary for future Digital Library endeavors. Numerous ACM and
SIG-specific \LaTeX\ templates have been examined, and their unique
features incorporated into this single new template.

If you are new to publishing with ACM, this document is a valuable
guide to the process of preparing your work for publication. If you
have published with ACM before, this document provides insight and
instruction into more recent changes to the article template.

The ``\verb|acmart|'' document class can be used to prepare articles
for any ACM publication --- conference or journal, and for any stage
of publication, from review to final ``camera-ready'' copy, to the
author's own version, with {\itshape very} few changes to the source.

\section{Template Overview}
As noted in the introduction, the ``\verb|acmart|'' document class can
be used to prepare many different kinds of documentation --- a
double-anonymous initial submission of a full-length technical paper, a
two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
journal article, a SIGCHI Extended Abstract, and more --- all by
selecting the appropriate {\itshape template style} and {\itshape
  template parameters}.

This document will explain the major features of the document
class. For further information, the {\itshape \LaTeX\ User's Guide} is
available from
\url{https://www.acm.org/publications/proceedings-template}.

\subsection{Template Styles}

The primary parameter given to the ``\verb|acmart|'' document class is
the {\itshape template style} which corresponds to the kind of publication
or SIG publishing the work. This parameter is enclosed in square
brackets and is a part of the {\verb|documentclass|} command:
\begin{verbatim}
  \documentclass[STYLE]{acmart}
\end{verbatim}

Journals use one of three template styles. All but three ACM journals
use the {\verb|acmsmall|} template style:
\begin{itemize}
\item {\texttt{acmsmall}}: The default journal template style.
\item {\texttt{acmlarge}}: Used by JOCCH and TAP.
\item {\texttt{acmtog}}: Used by TOG.
\end{itemize}

The majority of conference proceedings documentation will use the {\verb|acmconf|} template style.
\begin{itemize}
\item {\texttt{sigconf}}: The default proceedings template style.
\item{\texttt{sigchi}}: Used for SIGCHI conference articles.
\item{\texttt{sigplan}}: Used for SIGPLAN conference articles.
\end{itemize}

\subsection{Template Parameters}

In addition to specifying the {\itshape template style} to be used in
formatting your work, there are a number of {\itshape template parameters}
which modify some part of the applied template style. A complete list
of these parameters can be found in the {\itshape \LaTeX\ User's Guide.}

Frequently-used parameters, or combinations of parameters, include:
\begin{itemize}
\item {\texttt{anonymous,review}}: Suitable for a ``double-anonymous''
  conference submission. Anonymizes the work and includes line
  numbers. Use with the \texttt{\acmSubmissionID} command to print the
  submission's unique ID on each page of the work.
\item{\texttt{authorversion}}: Produces a version of the work suitable
  for posting by the author.
\item{\texttt{screen}}: Produces colored hyperlinks.
\end{itemize}

This document uses the following string as the first command in the
source file:
\begin{verbatim}
\documentclass[manuscript,screen,review]{acmart}
\end{verbatim}

\section{Modifications}

Modifying the template --- including but not limited to: adjusting
margins, typeface sizes, line spacing, paragraph and list definitions,
and the use of the \verb|\vspace| command to manually adjust the
vertical spacing between elements of your work --- is not allowed.

{\bfseries Your document will be returned to you for revision if
  modifications are discovered.}

\section{Typefaces}

The ``\verb|acmart|'' document class requires the use of the
``Libertine'' typeface family. Your \TeX\ installation should include
this set of packages. Please do not substitute other typefaces. The
``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
as they will override the built-in typeface families.

\section{Title Information}

The title of your work should use capital letters appropriately -
\url{https://capitalizemytitle.com/} has useful rules for
capitalization. Use the {\verb|title|} command to define the title of
your work. If your work has a subtitle, define it with the
{\verb|subtitle|} command.  Do not insert line breaks in your title.

If your title is lengthy, you must define a short version to be used
in the page headers, to prevent overlapping text. The \verb|title|
command has a ``short title'' parameter:
\begin{verbatim}
  \title[short title]{full title}
\end{verbatim}

\section{Authors and Affiliations}

Each author must be defined separately for accurate metadata
identification.  As an exception, multiple authors may share one
affiliation. Authors' names should not be abbreviated; use full first
names wherever possible. Include authors' e-mail addresses whenever
possible.

Grouping authors' names or e-mail addresses, or providing an ``e-mail
alias,'' as shown below, is not acceptable:
\begin{verbatim}
  \author{Brooke Aster, David Mehldau}
  \email{dave,judy,steve@university.edu}
  \email{firstname.lastname@phillips.org}
\end{verbatim}

The \verb|authornote| and \verb|authornotemark| commands allow a note
to apply to multiple authors --- for example, if the first two authors
of an article contributed equally to the work.

If your author list is lengthy, you must define a shortened version of
the list of authors to be used in the page headers, to prevent
overlapping text. The following command should be placed just after
the last \verb|\author{}| definition:
\begin{verbatim}
  \renewcommand{\shortauthors}{McCartney, et al.}
\end{verbatim}
Omitting this command will force the use of a concatenated list of all
of the authors' names, which may result in overlapping text in the
page headers.

The article template's documentation, available at
\url{https://www.acm.org/publications/proceedings-template}, has a
complete explanation of these commands and tips for their effective
use.

Note that authors' addresses are mandatory for journal articles.

\section{Rights Information}

Authors of any work published by ACM will need to complete a rights
form. Depending on the kind of work, and the rights management choice
made by the author, this may be copyright transfer, permission,
license, or an OA (open access) agreement.

Regardless of the rights management choice, the author will receive a
copy of the completed rights form once it has been submitted. This
form contains \LaTeX\ commands that must be copied into the source
document. When the document source is compiled, these commands and
their parameters add formatted text to several areas of the final
document:
\begin{itemize}
\item the ``ACM Reference Format'' text on the first page.
\item the ``rights management'' text on the first page.
\item the conference information in the page header(s).
\end{itemize}

Rights information is unique to the work; if you are preparing several
works for an event, make sure to use the correct set of commands with
each of the works.

The ACM Reference Format text is required for all articles over one
page in length, and is optional for one-page articles (abstracts).

\section{CCS Concepts and User-Defined Keywords}

Two elements of the ``acmart'' document class provide powerful
taxonomic tools for you to help readers find your work in an online
search.

The ACM Computing Classification System ---
\url{https://www.acm.org/publications/class-2012} --- is a set of
classifiers and concepts that describe the computing
discipline. Authors can select entries from this classification
system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
commands to be included in the \LaTeX\ source.

User-defined keywords are a comma-separated list of words and phrases
of the authors' choosing, providing a more flexible way of describing
the research being presented.

CCS concepts and user-defined keywords are required for for all
articles over two pages in length, and are optional for one- and
two-page articles (or abstracts).

\section{Sectioning Commands}

Your work should use standard \LaTeX\ sectioning commands:
\verb|section|, \verb|subsection|, \verb|subsubsection|, and
\verb|paragraph|. They should be numbered; do not remove the numbering
from the commands.

Simulating a sectioning command by setting the first word or words of
a paragraph in boldface or italicized text is {\bfseries not allowed.}

\section{Tables}

The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
high-quality tables.

Table captions are placed {\itshape above} the table.

Because tables cannot be split across pages, the best placement for
them is typically the top of the page nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and the
table caption.  The contents of the table itself must go in the
\textbf{tabular} environment, to be aligned properly in rows and
columns, with the desired horizontal and vertical rules.  Again,
detailed instructions on \textbf{tabular} material are found in the
\textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table~\ref{tab:freq} is included in the input file; compare the
placement of the table here with the table in the printed output of
this document.

\begin{table}
  \caption{Frequency of Special Characters}
  \label{tab:freq}
  \begin{tabular}{ccl}
    \toprule
    Non-English or Math&Frequency&Comments\\
    \midrule
    \O & 1 in 1,000& For Swedish names\\
    $\pi$ & 1 in 5& Common in math\\
    \$ & 4 in 5 & Used in business\\
    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
  \bottomrule
\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of the page's
live area, use the environment \textbf{table*} to enclose the table's
contents and the table caption.  As with a single-column table, this
wide table will ``float'' to a location deemed more
desirable. Immediately following this sentence is the point at which
Table~\ref{tab:commands} is included in the input file; again, it is
instructive to compare the placement of the table here with the table
in the printed output of this document.

\begin{table*}
  \caption{Some Typical Commands}
  \label{tab:commands}
  \begin{tabular}{ccl}
    \toprule
    Command &A Number & Comments\\
    \midrule
    \texttt{{\char'134}author} & 100& Author \\
    \texttt{{\char'134}table}& 300 & For tables\\
    \texttt{{\char'134}table*}& 400& For wider tables\\
    \bottomrule
  \end{tabular}
\end{table*}

Always use midrule to separate table header rows from data rows, and
use it only for this purpose. This enables assistive technologies to
recognise table headers and support their users in navigating tables
more easily.

\section{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of the three are
discussed in the next sections.

\subsection{Inline (In-text) Equations}
A formula that appears in the running text is called an inline or
in-text formula.  It is produced by the \textbf{math} environment,
which can be invoked with the usual
\texttt{{\char'134}begin\,\ldots{\char'134}end} construction or with
the short form \texttt{\$\,\ldots\$}. You can use any of the symbols
and structures, from $\alpha$ to $\omega$, available in
\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a few
examples of in-text equations in context. Notice how this equation:
\begin{math}
  \lim_{n\rightarrow \infty}x=0
\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsection{Display Equations}
A numbered display equation---one set off by vertical space from the
text and centered horizontally---is produced by the \textbf{equation}
environment. An unnumbered display equation is produced by the
\textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols and
structures available in \LaTeX\@; this section will just give a couple
of examples of display equations in context.  First, consider the
equation, shown as an inline equation above:
\begin{equation}
  \lim_{n\rightarrow \infty}x=0
\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}
  \sum_{i=0}^{\infty} x + 1
\end{displaymath}
and follow it with another numbered equation:
\begin{equation}
  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\section{Figures}

The ``\verb|figure|'' environment should be used for figures. One or
more images can be placed within a figure. If your figure contains
third-party material, you must clearly identify it as such, as shown
in the example below.
\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{sample-franklin}
  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
    Ewing, Inc. [Public domain], via Wikimedia
    Commons. (\url{https://goo.gl/VLCRBB}).}
  \Description{A woman and a girl in white dresses sit in an open car.}
\end{figure}

Your figures should contain a caption which describes the figure to
the reader.

Figure captions are placed {\itshape below} the figure.

Every figure should also have a figure description unless it is purely
decorative. These descriptions convey what’s in the image to someone
who cannot see it. They are also used by search engine crawlers for
indexing images, and when images cannot be loaded.

A figure description must be unformatted plain text less than 2000
characters long (including spaces).  {\bfseries Figure descriptions
  should not repeat the figure caption – their purpose is to capture
  important information that is not already provided in the caption or
  the main text of the paper.} For figures that convey important and
complex new information, a short text description may not be
adequate. More complex alternative descriptions can be placed in an
appendix and referenced in a short figure description. For example,
provide a data table capturing the information in a bar chart, or a
structured list representing a graph.  For additional information
regarding how best to write figure descriptions and why doing this is
so important, please see
\url{https://www.acm.org/publications/taps/describing-figures/}.

\subsection{The ``Teaser Figure''}

A ``teaser figure'' is an image, or set of images in one figure, that
are placed after all author and affiliation information, and before
the body of the article, spanning the page. If you wish to have such a
figure in your article, place the command immediately before the
\verb|\maketitle| command:
\begin{verbatim}
  \begin{teaserfigure}
    \includegraphics[width=\textwidth]{sampleteaser}
    \caption{figure caption}
    \Description{figure description}
  \end{teaserfigure}
\end{verbatim}

\section{Citations and Bibliographies}

The use of \BibTeX\ for the preparation and formatting of one's
references is strongly recommended. Authors' names should be complete
--- use full first names (``Donald E. Knuth'') not initials
(``D. E. Knuth'') --- and the salient identifying features of a
reference should be included: title, year, volume, number, pages,
article DOI, etc.

The bibliography is included in your source document with these two
commands, placed just before the \verb|\end{document}| command:
\begin{verbatim}
  \bibliographystyle{ACM-Reference-Format}
  \bibliography{bibfile}
\end{verbatim}
where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
suffix, of the \BibTeX\ file.

Citations and references are numbered by default. A small number of
ACM publications have citations and references formatted in the
``author year'' style; for these exceptions, please include this
command in the {\bfseries preamble} (before the command
``\verb|\begin{document}|'') of your \LaTeX\ source:
\begin{verbatim}
  \citestyle{acmauthoryear}
\end{verbatim}

  Some examples.  A paginated journal article \cite{Abril07}, an
  enumerated journal article \cite{Cohen07}, a reference to an entire
  issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
  monograph/whole book in a series (see 2a in spec. document)
  \cite{Harel79}, a divisible-book such as an anthology or compilation
  \cite{Editor00} followed by the same example, however we only output
  the series if the volume number is given \cite{Editor00a} (so
  Editor00a's series should NOT be present since it has no vol. no.),
  a chapter in a divisible book \cite{Spector90}, a chapter in a
  divisible book in a series \cite{Douglass98}, a multi-volume work as
  book \cite{Knuth97}, a couple of articles in a proceedings (of a
  conference, symposium, workshop for example) (paginated proceedings
  article) \cite{Andler79, Hagerup1993}, a proceedings article with
  all possible elements \cite{Smith10}, an example of an enumerated
  proceedings article \cite{VanGundy07}, an informally published work
  \cite{Harel78}, a couple of preprints \cite{Bornmann2019,
    AnzarootPBM14}, a doctoral dissertation \cite{Clarkson85}, a
  master's thesis: \cite{anisi03}, an online document / world wide web
  resource \cite{Thornburg01, Ablamowicz07, Poker06}, a video game
  (Case 1) \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05}
  and (Case 3) a patent \cite{JoeScientist001}, work accepted for
  publication \cite{rous08}, 'YYYYb'-test for prolific author
  \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
  contain 'duplicate' DOI and URLs (some SIAM articles)
  \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
  multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
  couple of citations with DOIs:
  \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
  citations: \cite{TUGInstmem, Thornburg01, CTANacmart}.
  Artifacts: \cite{R} and \cite{UMassCitations}.

\section{Acknowledgments}

Identification of funding sources and other support, and thanks to
individuals and groups that assisted in the research and the
preparation of the work should be included in an acknowledgment
section, which is placed just before the reference section in your
document.

This section has a special environment:
\begin{verbatim}
  \begin{acks}
  ...
  \end{acks}
\end{verbatim}
so that the information contained therein can be more easily collected
during the article metadata extraction phase, and to ensure
consistency in the spelling of the section heading.

Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.

\section{Appendices}

If your work needs an appendix, add it before the
``\verb|\end{document}|'' command at the conclusion of your source
document.

Start the appendix with the ``\verb|appendix|'' command:
\begin{verbatim}
  \appendix
\end{verbatim}
and note that in the appendix, sections are lettered, not
numbered. This document has two appendices, demonstrating the section
and subsection identification method.

\section{Multi-language papers}

Papers may be written in languages other than English or include
titles, subtitles, keywords and abstracts in different languages (as a
rule, a paper in a language other than English should include an
English title and an English abstract).  Use \verb|language=...| for
every language used in the paper.  The last language indicated is the
main language of the paper.  For example, a French paper with
additional titles and abstracts in English and German may start with
the following command
\begin{verbatim}
\documentclass[sigconf, language=english, language=german,
               language=french]{acmart}
\end{verbatim}

The title, subtitle, keywords and abstract will be typeset in the main
language of the paper.  The commands \verb|\translatedXXX|, \verb|XXX|
begin title, subtitle and keywords, can be used to set these elements
in the other languages.  The environment \verb|translatedabstract| is
used to set the translation of the abstract.  These commands and
environment have a mandatory first argument: the language of the
second argument.  See \verb|sample-sigconf-i13n.tex| file for examples
of their usage.

\section{SIGCHI Extended Abstracts}

The ``\verb|sigchi-a|'' template style (available only in \LaTeX\ and
not in Word) produces a landscape-orientation formatted article, with
a wide left margin. Three environments are available for use with the
``\verb|sigchi-a|'' template style, and produce formatted output in
the margin:
\begin{description}
\item[\texttt{sidebar}:]  Place formatted text in the margin.
\item[\texttt{marginfigure}:] Place a figure in the margin.
\item[\texttt{margintable}:] Place a table in the margin.
\end{description}

%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
To Robert, for the bagels and explaining CMYK and color spaces.
\end{acks}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{references}

%%
%% If your work has an appendix, this is the place to put it.
\appendix

\section{Research Methods}

\subsection{Part One}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
lacinia dolor. Integer ultricies commodo sem nec semper.

\subsection{Part Two}

Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
eros. Vivamus non purus placerat, scelerisque diam eu, cursus
ante. Etiam aliquam tortor auctor efficitur mattis.

\section{Online Resources}

Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
enim maximus. Vestibulum gravida massa ut felis suscipit
congue. Quisque mattis elit a risus ultrices commodo venenatis eget
dui. Etiam sagittis eleifend elementum.

Nam interdum magna at lectus dignissim, ac dignissim lorem
rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
massa et mattis lacinia.

\end{document}
\endinput
%%
%% End of file `sample-manuscript.tex'.

### 2024-11-07 paper/paper.tex
First outline

@@
 %%
-\documentclass[manuscript,screen,review]{acmart}
+% \documentclass[manuscript,screen,review]{acmart}
+\documentclass[acmsmall,sigconf]{acmart}
 
@@
 
-%% Rights management information.  This information is sent to you
-%% when you complete the rights form.  These commands have SAMPLE
-%% values in them; it is your responsibility as an author to replace
-%% the commands and values with those provided to you when you
-%% complete the rights form.
-\setcopyright{acmlicensed}
-\copyrightyear{2018}
-\acmYear{2018}
-\acmDOI{XXXXXXX.XXXXXXX}
+% %% Rights management information.  This information is sent to you
+% %% when you complete the rights form.  These commands have SAMPLE
+% %% values in them; it is your responsibility as an author to replace
+% %% the commands and values with those provided to you when you
+% %% complete the rights form.
+% \setcopyright{acmlicensed}
+% \copyrightyear{2018}
+% \acmYear{2018}
+% \acmDOI{XXXXXXX.XXXXXXX}
 
-%% These commands are for a PROCEEDINGS abstract or paper.
-\acmConference[Conference acronym 'XX]{Make sure to enter the correct
-  conference title from your rights confirmation emai}{June 03--05,
-  2018}{Woodstock, NY}
-%%
-%%  Uncomment \acmBooktitle if the title of the proceedings is different
-%%  from ``Proceedings of ...''!
-%%
-%%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
-%%  June 03--05, 2018, Woodstock, NY}
-\acmISBN{978-1-4503-XXXX-X/18/06}
+% %% These commands are for a PROCEEDINGS abstract or paper.
+% \acmConference[Conference acronym 'XX]{Make sure to enter the correct
+%   conference title from your rights confirmation emai}{June 03--05,
+%   2018}{Woodstock, NY}
+% %%
+% %%  Uncomment \acmBooktitle if the title of the proceedings is different
+% %%  from ``Proceedings of ...''!
+% %%
+% %%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
+% %%  June 03--05, 2018, Woodstock, NY}
+% \acmISBN{978-1-4503-XXXX-X/18/06}
 
@@
 %% used to denote shared contribution to the research.
-\author{Ben Trovato}
-\authornote{Both authors contributed equally to this research.}
-\email{trovato@corporation.com}
-\orcid{1234-5678-9012}
-\author{G.K.M. Tobin}
-\authornotemark[1]
-\email{webmaster@marysville-ohio.com}
+\author{Chih-Cheng Rex Yuan}
+\email{hello@rexyuan.com}
 \affiliation{%
-  \institution{Institute for Clarity in Documentation}
-  \city{Dublin}
-  \state{Ohio}
-  \country{USA}
+  \institution{Institute of Information Science, Academia Sinica}
+  \city{Taipei}
+  \country{Taiwan}
 }
 
-\author{Lars Th{\o}rv{\"a}ld}
+\author{Bow-Yaw Wang}
+\email{bywang@iis.sinica.edu.tw}
 \affiliation{%
-  \institution{The Th{\o}rv{\"a}ld Group}
-  \city{Hekla}
-  \country{Iceland}}
-\email{larst@affiliation.org}
-
-\author{Valerie B\'eranger}
-\affiliation{%
-  \institution{Inria Paris-Rocquencourt}
-  \city{Rocquencourt}
-  \country{France}
+  \institution{Institute of Information Science, Academia Sinica}
+  \city{Taipei}
+  \country{Taiwan}
 }
-
-\author{Aparna Patel}
-\affiliation{%
- \institution{Rajiv Gandhi University}
- \city{Doimukh}
- \state{Arunachal Pradesh}
- \country{India}}
-
-\author{Huifen Chan}
-\affiliation{%
-  \institution{Tsinghua University}
-  \city{Haidian Qu}
-  \state{Beijing Shi}
-  \country{China}}
-
-\author{Charles Palmer}
-\affiliation{%
-  \institution{Palmer Research Laboratories}
-  \city{San Antonio}
-  \state{Texas}
-  \country{USA}}
-\email{cpalmer@prl.com}
-
-\author{John Smith}
-\affiliation{%
-  \institution{The Th{\o}rv{\"a}ld Group}
-  \city{Hekla}
-  \country{Iceland}}
-\email{jsmith@affiliation.org}
-
-\author{Julius P. Kumquat}
-\affiliation{%
-  \institution{The Kumquat Consortium}
-  \city{New York}
-  \country{USA}}
-\email{jpkumquat@consortium.net}
 
@@
 %% of authors' names for this purpose.
-\renewcommand{\shortauthors}{Trovato et al.}
+% \renewcommand{\shortauthors}{Trovato et al.}
 
@@
 \begin{abstract}
-  A clear and well-documented \LaTeX\ document is presented as an
-  article formatted for publication by ACM in a conference proceedings
-  or journal publication. Based on the ``acmart'' document class, this
-  article presents and explains many of the common variations, as well
-  as many of the formatting elements an author may use in the
-  preparation of the documentation of their work.
+  abstract
 \end{abstract}
 
-%%
-%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
-%% Please copy and paste the code instead of the example below.
-%%
-\begin{CCSXML}
-<ccs2012>
- <concept>
-  <concept_id>00000000.0000000.0000000</concept_id>
-  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
-  <concept_significance>500</concept_significance>
- </concept>
- <concept>
-  <concept_id>00000000.00000000.00000000</concept_id>
-  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
-  <concept_significance>300</concept_significance>
- </concept>
- <concept>
-  <concept_id>00000000.00000000.00000000</concept_id>
-  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
- <concept>
-  <concept_id>00000000.00000000.00000000</concept_id>
-  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
-</ccs2012>
-\end{CCSXML}
+% %%
+% %% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
+% %% Please copy and paste the code instead of the example below.
+% %%
+% \begin{CCSXML}
+% <ccs2012>
+%  <concept>
+%   <concept_id>00000000.0000000.0000000</concept_id>
+%   <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
+%   <concept_significance>500</concept_significance>
+%  </concept>
+%  <concept>
+%   <concept_id>00000000.00000000.00000000</concept_id>
+%   <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
+%   <concept_significance>300</concept_significance>
+%  </concept>
+%  <concept>
+%   <concept_id>00000000.00000000.00000000</concept_id>
+%   <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
+%   <concept_significance>100</concept_significance>
+%  </concept>
+%  <concept>
+%   <concept_id>00000000.00000000.00000000</concept_id>
+%   <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
+%   <concept_significance>100</concept_significance>
+%  </concept>
+% </ccs2012>
+% \end{CCSXML}
 
-\ccsdesc[500]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
-\ccsdesc[300]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
-\ccsdesc{Do Not Use This Code~Generate the Correct Terms for Your Paper}
-\ccsdesc[100]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
+% \ccsdesc[500]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
+% \ccsdesc[300]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
+% \ccsdesc{Do Not Use This Code~Generate the Correct Terms for Your Paper}
+% \ccsdesc[100]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
 
-%%
-%% Keywords. The author(s) should pick words that accurately describe
-%% the work being presented. Separate the keywords with commas.
-\keywords{Do, Not, Us, This, Code, Put, the, Correct, Terms, for,
-  Your, Paper}
+% %%
+% %% Keywords. The author(s) should pick words that accurately describe
+% %% the work being presented. Separate the keywords with commas.
+% \keywords{Do, Not, Us, This, Code, Put, the, Correct, Terms, for,
+%   Your, Paper}
 
@@
 \section{Introduction}
-ACM's consolidated article template, introduced in 2017, provides a
-consistent \LaTeX\ style for use across ACM publications, and
-incorporates accessibility and metadata-extraction functionality
-necessary for future Digital Library endeavors. Numerous ACM and
-SIG-specific \LaTeX\ templates have been examined, and their unique
-features incorporated into this single new template.
 
-If you are new to publishing with ACM, this document is a valuable
-guide to the process of preparing your work for publication. If you
-have published with ACM before, this document provides insight and
-instruction into more recent changes to the article template.
+\section{Related Work}
 
-The ``\verb|acmart|'' document class can be used to prepare articles
-for any ACM publication --- conference or journal, and for any stage
-of publication, from review to final ``camera-ready'' copy, to the
-author's own version, with {\itshape very} few changes to the source.
+\section{Auditing Framework}
 
-\section{Template Overview}
-As noted in the introduction, the ``\verb|acmart|'' document class can
-be used to prepare many different kinds of documentation --- a
-double-anonymous initial submission of a full-length technical paper, a
-two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
-journal article, a SIGCHI Extended Abstract, and more --- all by
-selecting the appropriate {\itshape template style} and {\itshape
-  template parameters}.
+\subsection{Preliminaries}
 
-This document will explain the major features of the document
-class. For further information, the {\itshape \LaTeX\ User's Guide} is
-available from
-\url{https://www.acm.org/publications/proceedings-template}.
+\subsection{Fairness Measures}
 
-\subsection{Template Styles}
+\subsection{Differential Privacy}
 
-The primary parameter given to the ``\verb|acmart|'' document class is
-the {\itshape template style} which corresponds to the kind of publication
-or SIG publishing the work. This parameter is enclosed in square
-brackets and is a part of the {\verb|documentclass|} command:
-\begin{verbatim}
-  \documentclass[STYLE]{acmart}
-\end{verbatim}
+\subsection{Synthetic Data}
 
-Journals use one of three template styles. All but three ACM journals
-use the {\verb|acmsmall|} template style:
-\begin{itemize}
-\item {\texttt{acmsmall}}: The default journal template style.
-\item {\texttt{acmlarge}}: Used by JOCCH and TAP.
-\item {\texttt{acmtog}}: Used by TOG.
-\end{itemize}
+\section{Methodology}
 
-The majority of conference proceedings documentation will use the {\verb|acmconf|} template style.
-\begin{itemize}
-\item {\texttt{sigconf}}: The default proceedings template style.
-\item{\texttt{sigchi}}: Used for SIGCHI conference articles.
-\item{\texttt{sigplan}}: Used for SIGPLAN conference articles.
-\end{itemize}
+\subsection{Differential Private Synthetic Data}
 
-\subsection{Template Parameters}
+\subsection{Fairness Checker}
 
-In addition to specifying the {\itshape template style} to be used in
-formatting your work, there are a number of {\itshape template parameters}
-which modify some part of the applied template style. A complete list
-of these parameters can be found in the {\itshape \LaTeX\ User's Guide.}
+\subsection{Implementation}
 
-Frequently-used parameters, or combinations of parameters, include:
-\begin{itemize}
-\item {\texttt{anonymous,review}}: Suitable for a ``double-anonymous''
-  conference submission. Anonymizes the work and includes line
-  numbers. Use with the \texttt{\acmSubmissionID} command to print the
-  submission's unique ID on each page of the work.
-\item{\texttt{authorversion}}: Produces a version of the work suitable
-  for posting by the author.
-\item{\texttt{screen}}: Produces colored hyperlinks.
-\end{itemize}
+\section{Results}
 
-This document uses the following string as the first command in the
-source file:
-\begin{verbatim}
-\documentclass[manuscript,screen,review]{acmart}
-\end{verbatim}
+\subsection{Adult Income Dataset}
 
-\section{Modifications}
+\subsection{COMPAS Dataset}
 
-Modifying the template --- including but not limited to: adjusting
-margins, typeface sizes, line spacing, paragraph and list definitions,
-and the use of the \verb|\vspace| command to manually adjust the
-vertical spacing between elements of your work --- is not allowed.
+\subsection{One More Dataset}
 
-{\bfseries Your document will be returned to you for revision if
-  modifications are discovered.}
+\section{Discussion}
 
-\section{Typefaces}
+\subsection{Accuracy}
 
-The ``\verb|acmart|'' document class requires the use of the
-``Libertine'' typeface family. Your \TeX\ installation should include
-this set of packages. Please do not substitute other typefaces. The
-``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
-as they will override the built-in typeface families.
+\subsection{Impossibility}
 
-\section{Title Information}
+\section{Conclusion}
 
-The title of your work should use capital letters appropriately -
-\url{https://capitalizemytitle.com/} has useful rules for
-capitalization. Use the {\verb|title|} command to define the title of
-your work. If your work has a subtitle, define it with the
-{\verb|subtitle|} command.  Do not insert line breaks in your title.
+Some examples.  A paginated journal article \cite{Abril07}
 
-If your title is lengthy, you must define a short version to be used
-in the page headers, to prevent overlapping text. The \verb|title|
-command has a ``short title'' parameter:
-\begin{verbatim}
-  \title[short title]{full title}
-\end{verbatim}
+% \begin{table}
+%   \caption{Frequency of Special Characters}
+%   \label{tab:freq}
+%   \begin{tabular}{ccl}
+%     \toprule
+%     Non-English or Math&Frequency&Comments\\
+%     \midrule
+%     \O & 1 in 1,000& For Swedish names\\
+%     $\pi$ & 1 in 5& Common in math\\
+%     \$ & 4 in 5 & Used in business\\
+%     $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
+%   \bottomrule
+% \end{tabular}
+% \end{table}
 
-\section{Authors and Affiliations}
+% \begin{table*}
+%   \caption{Some Typical Commands}
+%   \label{tab:commands}
+%   \begin{tabular}{ccl}
+%     \toprule
+%     Command &A Number & Comments\\
+%     \midrule
+%     \texttt{{\char'134}author} & 100& Author \\
+%     \texttt{{\char'134}table}& 300 & For tables\\
+%     \texttt{{\char'134}table*}& 400& For wider tables\\
+%     \bottomrule
+%   \end{tabular}
+% \end{table*}
 
-Each author must be defined separately for accurate metadata
-identification.  As an exception, multiple authors may share one
-affiliation. Authors' names should not be abbreviated; use full first
-names wherever possible. Include authors' e-mail addresses whenever
-possible.
-
-Grouping authors' names or e-mail addresses, or providing an ``e-mail
-alias,'' as shown below, is not acceptable:
-\begin{verbatim}
-  \author{Brooke Aster, David Mehldau}
-  \email{dave,judy,steve@university.edu}
-  \email{firstname.lastname@phillips.org}
-\end{verbatim}
-
-The \verb|authornote| and \verb|authornotemark| commands allow a note
-to apply to multiple authors --- for example, if the first two authors
-of an article contributed equally to the work.
-
-If your author list is lengthy, you must define a shortened version of
-the list of authors to be used in the page headers, to prevent
-overlapping text. The following command should be placed just after
-the last \verb|\author{}| definition:
-\begin{verbatim}
-  \renewcommand{\shortauthors}{McCartney, et al.}
-\end{verbatim}
-Omitting this command will force the use of a concatenated list of all
-of the authors' names, which may result in overlapping text in the
-page headers.
-
-The article template's documentation, available at
-\url{https://www.acm.org/publications/proceedings-template}, has a
-complete explanation of these commands and tips for their effective
-use.
-
-Note that authors' addresses are mandatory for journal articles.
-
-\section{Rights Information}
-
-Authors of any work published by ACM will need to complete a rights
-form. Depending on the kind of work, and the rights management choice
-made by the author, this may be copyright transfer, permission,
-license, or an OA (open access) agreement.
-
-Regardless of the rights management choice, the author will receive a
-copy of the completed rights form once it has been submitted. This
-form contains \LaTeX\ commands that must be copied into the source
-document. When the document source is compiled, these commands and
-their parameters add formatted text to several areas of the final
-document:
-\begin{itemize}
-\item the ``ACM Reference Format'' text on the first page.
-\item the ``rights management'' text on the first page.
-\item the conference information in the page header(s).
-\end{itemize}
-
-Rights information is unique to the work; if you are preparing several
-works for an event, make sure to use the correct set of commands with
-each of the works.
-
-The ACM Reference Format text is required for all articles over one
-page in length, and is optional for one-page articles (abstracts).
-
-\section{CCS Concepts and User-Defined Keywords}
-
-Two elements of the ``acmart'' document class provide powerful
-taxonomic tools for you to help readers find your work in an online
-search.
-
-The ACM Computing Classification System ---
-\url{https://www.acm.org/publications/class-2012} --- is a set of
-classifiers and concepts that describe the computing
-discipline. Authors can select entries from this classification
-system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
-commands to be included in the \LaTeX\ source.
-
-User-defined keywords are a comma-separated list of words and phrases
-of the authors' choosing, providing a more flexible way of describing
-the research being presented.
-
-CCS concepts and user-defined keywords are required for for all
-articles over two pages in length, and are optional for one- and
-two-page articles (or abstracts).
-
-\section{Sectioning Commands}
-
-Your work should use standard \LaTeX\ sectioning commands:
-\verb|section|, \verb|subsection|, \verb|subsubsection|, and
-\verb|paragraph|. They should be numbered; do not remove the numbering
-from the commands.
-
-Simulating a sectioning command by setting the first word or words of
-a paragraph in boldface or italicized text is {\bfseries not allowed.}
-
-\section{Tables}
-
-The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
-package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
-high-quality tables.
-
-Table captions are placed {\itshape above} the table.
-
-Because tables cannot be split across pages, the best placement for
-them is typically the top of the page nearest their initial cite.  To
-ensure this proper ``floating'' placement of tables, use the
-environment \textbf{table} to enclose the table's contents and the
-table caption.  The contents of the table itself must go in the
-\textbf{tabular} environment, to be aligned properly in rows and
-columns, with the desired horizontal and vertical rules.  Again,
-detailed instructions on \textbf{tabular} material are found in the
-\textit{\LaTeX\ User's Guide}.
-
-Immediately following this sentence is the point at which
-Table~\ref{tab:freq} is included in the input file; compare the
-placement of the table here with the table in the printed output of
-this document.
-
-\begin{table}
-  \caption{Frequency of Special Characters}
-  \label{tab:freq}
-  \begin{tabular}{ccl}
-    \toprule
-    Non-English or Math&Frequency&Comments\\
-    \midrule
-    \O & 1 in 1,000& For Swedish names\\
-    $\pi$ & 1 in 5& Common in math\\
-    \$ & 4 in 5 & Used in business\\
-    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-  \bottomrule
-\end{tabular}
-\end{table}
-
-To set a wider table, which takes up the whole width of the page's
-live area, use the environment \textbf{table*} to enclose the table's
-contents and the table caption.  As with a single-column table, this
-wide table will ``float'' to a location deemed more
-desirable. Immediately following this sentence is the point at which
-Table~\ref{tab:commands} is included in the input file; again, it is
-instructive to compare the placement of the table here with the table
-in the printed output of this document.
-
-\begin{table*}
-  \caption{Some Typical Commands}
-  \label{tab:commands}
-  \begin{tabular}{ccl}
-    \toprule
-    Command &A Number & Comments\\
-    \midrule
-    \texttt{{\char'134}author} & 100& Author \\
-    \texttt{{\char'134}table}& 300 & For tables\\
-    \texttt{{\char'134}table*}& 400& For wider tables\\
-    \bottomrule
-  \end{tabular}
-\end{table*}
-
-Always use midrule to separate table header rows from data rows, and
-use it only for this purpose. This enables assistive technologies to
-recognise table headers and support their users in navigating tables
-more easily.
-
-\section{Math Equations}
-You may want to display math equations in three distinct styles:
-inline, numbered or non-numbered display.  Each of the three are
-discussed in the next sections.
-
-\subsection{Inline (In-text) Equations}
-A formula that appears in the running text is called an inline or
-in-text formula.  It is produced by the \textbf{math} environment,
-which can be invoked with the usual
-\texttt{{\char'134}begin\,\ldots{\char'134}end} construction or with
-the short form \texttt{\$\,\ldots\$}. You can use any of the symbols
-and structures, from $\alpha$ to $\omega$, available in
-\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a few
-examples of in-text equations in context. Notice how this equation:
-\begin{math}
-  \lim_{n\rightarrow \infty}x=0
-\end{math},
-set here in in-line math style, looks slightly different when
-set in display style.  (See next section).
-
-\subsection{Display Equations}
-A numbered display equation---one set off by vertical space from the
-text and centered horizontally---is produced by the \textbf{equation}
-environment. An unnumbered display equation is produced by the
-\textbf{displaymath} environment.
-
-Again, in either environment, you can use any of the symbols and
-structures available in \LaTeX\@; this section will just give a couple
-of examples of display equations in context.  First, consider the
-equation, shown as an inline equation above:
-\begin{equation}
-  \lim_{n\rightarrow \infty}x=0
-\end{equation}
-Notice how it is formatted somewhat differently in
-the \textbf{displaymath}
-environment.  Now, we'll enter an unnumbered equation:
-\begin{displaymath}
-  \sum_{i=0}^{\infty} x + 1
-\end{displaymath}
-and follow it with another numbered equation:
-\begin{equation}
-  \sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
-\end{equation}
-just to demonstrate \LaTeX's able handling of numbering.
-
-\section{Figures}
-
-The ``\verb|figure|'' environment should be used for figures. One or
-more images can be placed within a figure. If your figure contains
-third-party material, you must clearly identify it as such, as shown
-in the example below.
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=\linewidth]{sample-franklin}
-  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
-    Ewing, Inc. [Public domain], via Wikimedia
-    Commons. (\url{https://goo.gl/VLCRBB}).}
-  \Description{A woman and a girl in white dresses sit in an open car.}
-\end{figure}
-
-Your figures should contain a caption which describes the figure to
-the reader.
-
-Figure captions are placed {\itshape below} the figure.
-
-Every figure should also have a figure description unless it is purely
-decorative. These descriptions convey what’s in the image to someone
-who cannot see it. They are also used by search engine crawlers for
-indexing images, and when images cannot be loaded.
-
-A figure description must be unformatted plain text less than 2000
-characters long (including spaces).  {\bfseries Figure descriptions
-  should not repeat the figure caption – their purpose is to capture
-  important information that is not already provided in the caption or
-  the main text of the paper.} For figures that convey important and
-complex new information, a short text description may not be
-adequate. More complex alternative descriptions can be placed in an
-appendix and referenced in a short figure description. For example,
-provide a data table capturing the information in a bar chart, or a
-structured list representing a graph.  For additional information
-regarding how best to write figure descriptions and why doing this is
-so important, please see
-\url{https://www.acm.org/publications/taps/describing-figures/}.
-
-\subsection{The ``Teaser Figure''}
-
-A ``teaser figure'' is an image, or set of images in one figure, that
-are placed after all author and affiliation information, and before
-the body of the article, spanning the page. If you wish to have such a
-figure in your article, place the command immediately before the
-\verb|\maketitle| command:
-\begin{verbatim}
-  \begin{teaserfigure}
-    \includegraphics[width=\textwidth]{sampleteaser}
-    \caption{figure caption}
-    \Description{figure description}
-  \end{teaserfigure}
-\end{verbatim}
-
-\section{Citations and Bibliographies}
-
-The use of \BibTeX\ for the preparation and formatting of one's
-references is strongly recommended. Authors' names should be complete
---- use full first names (``Donald E. Knuth'') not initials
-(``D. E. Knuth'') --- and the salient identifying features of a
-reference should be included: title, year, volume, number, pages,
-article DOI, etc.
-
-The bibliography is included in your source document with these two
-commands, placed just before the \verb|\end{document}| command:
-\begin{verbatim}
-  \bibliographystyle{ACM-Reference-Format}
-  \bibliography{bibfile}
-\end{verbatim}
-where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
-suffix, of the \BibTeX\ file.
-
-Citations and references are numbered by default. A small number of
-ACM publications have citations and references formatted in the
-``author year'' style; for these exceptions, please include this
-command in the {\bfseries preamble} (before the command
-``\verb|\begin{document}|'') of your \LaTeX\ source:
-\begin{verbatim}
-  \citestyle{acmauthoryear}
-\end{verbatim}
-
-  Some examples.  A paginated journal article \cite{Abril07}, an
-  enumerated journal article \cite{Cohen07}, a reference to an entire
-  issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
-  monograph/whole book in a series (see 2a in spec. document)
-  \cite{Harel79}, a divisible-book such as an anthology or compilation
-  \cite{Editor00} followed by the same example, however we only output
-  the series if the volume number is given \cite{Editor00a} (so
-  Editor00a's series should NOT be present since it has no vol. no.),
-  a chapter in a divisible book \cite{Spector90}, a chapter in a
-  divisible book in a series \cite{Douglass98}, a multi-volume work as
-  book \cite{Knuth97}, a couple of articles in a proceedings (of a
-  conference, symposium, workshop for example) (paginated proceedings
-  article) \cite{Andler79, Hagerup1993}, a proceedings article with
-  all possible elements \cite{Smith10}, an example of an enumerated
-  proceedings article \cite{VanGundy07}, an informally published work
-  \cite{Harel78}, a couple of preprints \cite{Bornmann2019,
-    AnzarootPBM14}, a doctoral dissertation \cite{Clarkson85}, a
-  master's thesis: \cite{anisi03}, an online document / world wide web
-  resource \cite{Thornburg01, Ablamowicz07, Poker06}, a video game
-  (Case 1) \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05}
-  and (Case 3) a patent \cite{JoeScientist001}, work accepted for
-  publication \cite{rous08}, 'YYYYb'-test for prolific author
-  \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
-  contain 'duplicate' DOI and URLs (some SIAM articles)
-  \cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
-  multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
-  couple of citations with DOIs:
-  \cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
-  citations: \cite{TUGInstmem, Thornburg01, CTANacmart}.
-  Artifacts: \cite{R} and \cite{UMassCitations}.
-
-\section{Acknowledgments}
-
-Identification of funding sources and other support, and thanks to
-individuals and groups that assisted in the research and the
-preparation of the work should be included in an acknowledgment
-section, which is placed just before the reference section in your
-document.
-
-This section has a special environment:
-\begin{verbatim}
-  \begin{acks}
-  ...
-  \end{acks}
-\end{verbatim}
-so that the information contained therein can be more easily collected
-during the article metadata extraction phase, and to ensure
-consistency in the spelling of the section heading.
-
-Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.
-
-\section{Appendices}
-
-If your work needs an appendix, add it before the
-``\verb|\end{document}|'' command at the conclusion of your source
-document.
-
-Start the appendix with the ``\verb|appendix|'' command:
-\begin{verbatim}
-  \appendix
-\end{verbatim}
-and note that in the appendix, sections are lettered, not
-numbered. This document has two appendices, demonstrating the section
-and subsection identification method.
-
-\section{Multi-language papers}
-
-Papers may be written in languages other than English or include
-titles, subtitles, keywords and abstracts in different languages (as a
-rule, a paper in a language other than English should include an
-English title and an English abstract).  Use \verb|language=...| for
-every language used in the paper.  The last language indicated is the
-main language of the paper.  For example, a French paper with
-additional titles and abstracts in English and German may start with
-the following command
-\begin{verbatim}
-\documentclass[sigconf, language=english, language=german,
-               language=french]{acmart}
-\end{verbatim}
-
-The title, subtitle, keywords and abstract will be typeset in the main
-language of the paper.  The commands \verb|\translatedXXX|, \verb|XXX|
-begin title, subtitle and keywords, can be used to set these elements
-in the other languages.  The environment \verb|translatedabstract| is
-used to set the translation of the abstract.  These commands and
-environment have a mandatory first argument: the language of the
-second argument.  See \verb|sample-sigconf-i13n.tex| file for examples
-of their usage.
-
-\section{SIGCHI Extended Abstracts}
-
-The ``\verb|sigchi-a|'' template style (available only in \LaTeX\ and
-not in Word) produces a landscape-orientation formatted article, with
-a wide left margin. Three environments are available for use with the
-``\verb|sigchi-a|'' template style, and produce formatted output in
-the margin:
-\begin{description}
-\item[\texttt{sidebar}:]  Place formatted text in the margin.
-\item[\texttt{marginfigure}:] Place a figure in the margin.
-\item[\texttt{margintable}:] Place a table in the margin.
-\end{description}
+% \begin{figure}[h]
+%   \centering
+%   \includegraphics[width=\linewidth]{sample-franklin}
+%   \caption{1907 Franklin Model D roadster. Photograph by Harris \&
+%     Ewing, Inc. [Public domain], via Wikimedia
+%     Commons. (\url{https://goo.gl/VLCRBB}).}
+%   \Description{A woman and a girl in white dresses sit in an open car.}
+% \end{figure}
 
@@
 %% consistent spelling of the heading.
-\begin{acks}
-To Robert, for the bagels and explaining CMYK and color spaces.
-\end{acks}
+% \begin{acks}
+% To Robert, for the bagels and explaining CMYK and color spaces.
+% \end{acks}
 
@@
 %% If your work has an appendix, this is the place to put it.
-\appendix
-
-\section{Research Methods}
-
-\subsection{Part One}
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
-malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
-sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
-vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
-lacinia dolor. Integer ultricies commodo sem nec semper.
-
-\subsection{Part Two}
-
-Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
-ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
-ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
-eros. Vivamus non purus placerat, scelerisque diam eu, cursus
-ante. Etiam aliquam tortor auctor efficitur mattis.
-
-\section{Online Resources}
-
-Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
-pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
-enim maximus. Vestibulum gravida massa ut felis suscipit
-congue. Quisque mattis elit a risus ultrices commodo venenatis eget
-dui. Etiam sagittis eleifend elementum.
-
-Nam interdum magna at lectus dignissim, ac dignissim lorem
-rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
-massa et mattis lacinia.
+% \appendix
 

### 2024-11-09 paper/paper.tex
Added some diff priv

@@
 
+\usepackage{mathtools}
+
+\graphicspath{{images/}}
+\DeclareGraphicsExtensions{.pdf}
+
+\DeclarePairedDelimiter{\set}{\{}{\}}
+\DeclarePairedDelimiter{\tuple}{(}{)}
+\DeclarePairedDelimiter{\abs}{\lvert}{\rvert}
+\renewcommand{\implies}{\rightarrow}
+\newcommand{\db}{\mathcal{D}}
+\newcommand{\model}{\mathcal{M}}
+\newcommand{\priv}{R}
+\newcommand{\pos}{\hat{P}}
+\newcommand{\posm}{\hat{P}_\mathcal{M}}
+\newcommand{\tru}{T}
+\newcommand{\leg}{L}
+\newcommand{\sco}{\hat{S}}
+\newcommand{\scom}{\hat{S}_\mathcal{M}}
+\newcommand{\calib}{C}
+\newcommand{\prob}[1]{\text{Pr}[#1]}
+
 %%
@@
 
+A \emph{row} $r_i$ is a lookup table or dictionary.
+A \emph{database} $\db = \set{r_1, r_2, ...}$ is a collection of rows.
+The attributes of $\db$ is $\mathcal{A} = \set{A_1, A_2, ...}$.
+The domain of $A_i$ is $\Omega_i$.
+
+Let $C \subseteq \mathcal{A}$.
+Let $\Omega_C = \Pi_{i \in C} \Omega_i$.
+The \emph{marginal}\cite{barak2007privacy,mckenna2021winning} on $C$ is a vector $\mu \in \mathbb{R}^{\abs{\Omega_C}}$, indexed by domain element $t \in \Omega_C$, such that each entry is a count $\mu_t = \Sigma_{x \in \db} \vmathbb{1} [x_C = t]$ where $\vmathbb{1}$ is the indicator function.
+Let $M_C(\db)$ be the function that computes the marginal on $C$, i.e., $\mu = M_C(\db)$.
+
+A \emph{randomized mechanism} is a randomized algorithm $M$ that takes a database $\db$ and, after, introducing noise, outputs some results in set $R$.
+
+The $p$-norm is denoted by $L_p$ and the $p$-norm of a vector $x$ is denoted by $\Vert x \Vert_p$.
+
+The normal distribution or Gaussian distribution with mean $\mu$ and standard deviation $\sigma$ is denoted by $\mathcal{N}(\mu, \sigma^2)$.
+
+The Kullback–Leibler divergence between probability distributions $P$ and $Q$ is denoted by $D_{KL}(P \Vert Q)$.
+The generalization of it, R\'enyi divergence\cite{van2014renyi}, of order $\alpha$ is denoted by $D_\alpha(P \Vert Q)$.
+
 \subsection{Fairness Measures}
@@
 \subsection{Differential Privacy}
+
+\begin{definition}[Sensitivity\cite{dwork2014algorithmic}]\label{def:sensitivity}
+Let $f$ be a function that takes a database $\db$ and outputs a vector $\mathbb{R}^p$. The $L_2$ sensitivity of $f$ is for all databases $\db_1,\db_2$ that differ in exactly one row:
+\[
+\Delta^2_f = max_{\db_1,\db_2} \Vert f(\db_1) - f(\db_2) \Vert_p
+\]
+\end{definition}
+
+\begin{definition}[Gaussian Mechanism\cite{dwork2014algorithmic}]\label{def:gm}
+Let $f$ be a function that takes a database $\db$ and outputs a vector $\mathbb{R}^p$. The Gaussian Mechanism $M$ adds Gaussian noise with scale $\sigma$ to each of the $p$ outputs:
+\[
+M(\db) = f(\db) + \mathcal{N}(0, \sigma^2 \mathbb{I})
+\]
+\end{definition}
+
+\begin{definition}[Differential Privacy (DP) \cite{dwork2006calibrating,dwork2014algorithmic,mckenna2021winning}]\label{def:rdp}
+A randomized mechanism $M$ satisfies $(\epsilon,\delta)$-DP if, for all databases $\db_1,\db_2$ that differ in exactly one row and for all subsets $S$ of $R$, we have
+\[
+\prob{M(\db_1) \in S} \leq e^\epsilon \prob{M(\db_2) \in S} + \delta
+\]
+\end{definition}
+
+\begin{definition}[R\'enyi Differential Privacy (RDP)]\label{def:rdp}
+A randomized mechanism $M$ satisfies $(\alpha,\gamma)$-RDP for $\alpha \geq 1$ and $\gamma \geq 1$ if, for all databases $\db_1,\db_2$ that differ in exactly one row, we have
+\[
+D_\alpha(M(\db_1) \Vert M(\db_2)) \leq \gamma
+\]
+\end{definition}
+
+\begin{theorem}[RDP of the Gaussian Mechanism\cite{feldman2018privacy,mironov2017renyi}]
+The Gaussian Mechanism satisfies $(\alpha, \alpha \frac{\Delta^2_f}{2 \sigma^2})$-RDP.
+\end{theorem}
 
@@
 
-% \begin{figure}[h]
-%   \centering
-%   \includegraphics[width=\linewidth]{sample-franklin}
-%   \caption{1907 Franklin Model D roadster. Photograph by Harris \&
-%     Ewing, Inc. [Public domain], via Wikimedia
-%     Commons. (\url{https://goo.gl/VLCRBB}).}
-%   \Description{A woman and a girl in white dresses sit in an open car.}
-% \end{figure}
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\linewidth]{compas_mst}
+  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
+    Ewing, Inc. [Public domain], via Wikimedia
+    Commons. (\url{https://goo.gl/VLCRBB}).}
+  \Description{A woman and a girl in white dresses sit in an open car.}
+\end{figure}
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\linewidth]{adult_mst}
+  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
+    Ewing, Inc. [Public domain], via Wikimedia
+    Commons. (\url{https://goo.gl/VLCRBB}).}
+  \Description{A woman and a girl in white dresses sit in an open car.}
+\end{figure}
 

### 2024-11-09 paper/paper.tex
Added some fairness

@@
 \usepackage{mathtools}
+\usepackage{multirow}
 
@@
 
+\clearpage
+
 \section{Auditing Framework}
+
+Our framework considers a scenario with three parties-data provider, model maker, and 3rd party auditor.
+The data provider has access to real data; for example, a census bureau.
+The model maker have AI models; for example, an AI company.
+The 3rd party auditor takes the data from data provider and AI models from model makers and perform fairness audits on them; for example, an investigative journalist.
+
+In our original framework\cite{yuan2024ensuring}, after obtaining real data from data provider, the 3rd party auditor holds onto the real data for performing fairness audits.
+However, this may introduce privacy concerns such as security breach of the auditor.
+
+Thus, we introduce a new framework where the auditor generates synthetic data based on real data upon retrival of the real data, and then holds onto the synthetic data and discards the real data, preventing further privacy breaches.
 
@@
 The domain of $A_i$ is $\Omega_i$.
+
+For fairness measures\cite{yuan2024ensuring,pessach2022review}, let $Y$ to denote the ground truth of an outcome, let $\hat{Y}$ to denote the predicated result of an outcome, let $S$ denote protected attribute, and let $\epsilon$ denote some threshold.
+For non-binary prediction, such as a score, we use $\hat{V}$.
 
@@
 \subsection{Fairness Measures}
+
+We consider in this work various fairness measures listed in Table~\ref{tab:measures}. They can be broadly categorized into independence, separation, and sufficiency.
+
+\begin{definition}[Independence\cite{barocas2023fairness}]\label{def:independence}
+$(S, \hat{Y})$ satisfy independence if and only if $S \bot \hat{Y}$; that is
+\[
+P[\hat{Y} = 1 | S = 1] = P[\hat{Y} = 1 | S \neq 1]
+\]
+A relaxation of independence on a threshold is
+\[
+\abs{P[\hat{Y} = 1 | S = 1] - P[\hat{Y} = 1 | S \neq 1]} \leq \epsilon
+\]
+\end{definition}
+
+\begin{definition}[Separation\cite{barocas2023fairness}]\label{def:separation}
+$(S, Y, \hat{Y})$ satisfy separation if and only if $S \bot \hat{Y} | Y$; that is
+\begin{align*}
+P[\hat{Y} = 1 | S = 1, Y = 1] & = P[\hat{Y} = 1 | S \neq 1, Y = 1] \\
+P[\hat{Y} = 1 | S = 1, Y = 0] & = P[\hat{Y} = 1 | S \neq 1, Y = 0]
+\end{align*}
+A relaxation of independence on a threshold is
+\begin{align*}
+\abs{P[\hat{Y} = 1 | S = 1, Y = 1] - P[\hat{Y} = 1 | S \neq 1, Y = 1]} & \leq \epsilon \\
+\abs{P[\hat{Y} = 1 | S = 1, Y = 0] - P[\hat{Y} = 1 | S \neq 1, Y = 0]} & \leq \epsilon
+\end{align*}
+\end{definition}
+
+\begin{definition}[Sufficiency\cite{barocas2023fairness}]\label{def:separation}
+$(S, Y, \hat{Y})$ satisfy sufficiency if and only if $S \bot Y | \hat{Y}$; that is
+\begin{align*}
+P[Y = 1 | S = 1, \hat{Y} = 1] & = P[Y = 1 | S \neq 1, \hat{Y} = 1] \\
+P[Y = 1 | S = 1, \hat{Y} = 0] & = P[Y = 1 | S \neq 1, \hat{Y} = 0]
+\end{align*}
+A relaxation of independence on a threshold is
+\begin{align*}
+\abs{P[Y = 1 | S = 1, \hat{Y} = 1] - P[Y = 1 | S \neq 1, \hat{Y} = 1]} & \leq \epsilon \\
+\abs{P[Y = 1 | S = 1, \hat{Y} = 0] - P[Y = 1 | S \neq 1, \hat{Y} = 0]} & \leq \epsilon
+\end{align*}
+\end{definition}
+
+\begin{table*}[h]
+\caption{Fairness measures.}
+\label{tab:measures}
+\begin{tabular}{llc} % 'l' specifies left alignment for the first column
+\toprule
+\textbf{Category} & \textbf{Fairness Measure} & \textbf{Definition} \\
+\midrule
+\multirow{4}{*}{Independence} & Disparate Impact & $\frac{P[\hat{Y} = 1 | S \neq 1]}{P[\hat{Y} = 1 | S = 1]} \geq 1 - \epsilon$ \\
+& Demographic Parity & $\abs{P[\hat{Y} = 1 | S = 1] - P[\hat{Y} = 1 | S \neq 1]} \leq \epsilon$ \\
+& Conditional Statistical Parity & $\abs{P[\hat{Y} = 1 | S = 1, L = l] - P[\hat{Y} = 1 | S \neq 1, L = l]} \leq \epsilon$ \\
+& Mean Difference & $\abs{E[\hat{Y}|S = 1] - E[\hat{Y}|S \neq 1]} \leq \epsilon$ \\
+\multirow{4}{*}{Separation} & \multirow{2}{*}{Equalized Odds} & $\abs{P[\hat{Y} = 1 | S = 1, Y = 0] - P[\hat{Y} = 1 | S \neq 1, Y = 0]} \leq \epsilon$ \\
+& & $\abs{P[\hat{Y} = 1 | S = 1, Y = 1] - P[\hat{Y} = 1 | S \neq 1, Y = 1]} \leq \epsilon$ \\
+& Equal Opportunity & $\abs{P[\hat{Y} = 1 | S = 1, Y = 1] - P[\hat{Y} = 1 | S \neq 1, Y = 1]} \leq \epsilon$ \\
+& Predictive Equality & $\abs{P[\hat{Y} = 1 | S = 1, Y = 0] - P[\hat{Y} = 1 | S \neq 1, Y = 0]} \leq \epsilon$ \\
+\multirow{4}{*}{Sufficiency} & \multirow{2}{*}{Conditional Use Accuracy Equality} & $\abs{P[Y = 1 | S = 1, \hat{Y} = 1] - P[Y = 1 | S \neq 1, \hat{Y} = 1]} \leq \epsilon$ \\
+& & $\abs{P[Y = 0 | S = 1, \hat{Y} = 0] - P[Y = 0 | S \neq 1, \hat{Y} = 0]} \leq \epsilon$ \\
+& Predictive Parity & $\abs{P[Y = 1 | S = 1, \hat{Y} = 1] - P[Y = 1 | S \neq 1, \hat{Y} = 1]} \leq \epsilon$ \\
+& Equal Calibration & $\abs{P[Y = 1 | S = 1, \hat{V} = v] - P[Y = 1 | S \neq 1, \hat{V} = v]} \leq \epsilon$ \\
+\multirow{3}{*}{N/A} & Overall Accuracy Equality & $\abs{P[Y = \hat{Y} | S = 1] - P[Y = \hat{Y} | S \neq 1]} \leq \epsilon$ \\
+& Positive Balance & $\abs{E[\hat{V} | Y = 1, S = 1] - E[\hat{V} | Y = 1, S \neq 1]} \leq \epsilon$ \\
+& Negative Balance & $\abs{E[\hat{V} | Y = 0, S = 1] - E[\hat{V} | Y = 0, S \neq 1]} \leq \epsilon$ \\
+\bottomrule
+\end{tabular}
+\end{table*}
 
@@
 
-\subsection{Synthetic Data}
-
 \section{Methodology}
 
-\subsection{Differential Private Synthetic Data}
+\subsection{Differentially Private Synthetic Data}
 

### 2024-11-09 paper/paper.tex
Added example marginal

@@
 \usepackage{multirow}
+\usepackage{subcaption}
 
@@
 Let $M_C(\db)$ be the function that computes the marginal on $C$, i.e., $\mu = M_C(\db)$.
+We call marginals of $|C| = n$ attributes $n$-way marginals.
 
@@
 
+We employed the tools of the winner of the 2018 NIST Differential Privacy Synthetic Data Challenge competition\cite{NIST2018} by Ryan McKenna\cite{Ullman2022,McKenna2022,McKenna_privatePGM,mckenna2021winning,mckenna2019graphical}.
+
+The competition considers marginals of the synthetic data.
+The idea of marginal-based synthetic data generation is to create a model whose marginals of samples are similar to the marginals of the original data.
+For example, suppose we have an original database and it's 2-way marginal on sex(Male,Female) and race(White,Black) is as shown in Table~\ref{tab:marginal-example}.
+
+\begin{table}[h]
+\caption{Example marginals.}
+\label{tab:marginal-example}
+\centering
+\begin{subtable}[t]{0.45\linewidth}
+\centering
+\caption{Marginal of original data.}
+\begin{tabular}{cc}
+  \toprule
+  Attributes & Count \\
+  \midrule
+  Male,White & 24 \\
+  Female,White & 33 \\
+  Male,Black & 13 \\
+  Female,Black & 47 \\
+  \bottomrule
+\end{tabular}
+\end{subtable}
+\hspace{0.05\linewidth}
+\begin{subtable}[t]{0.45\linewidth}
+\centering
+\caption{Marginal of synthetic data.}
+\begin{tabular}{cc}
+  \toprule
+  Attributes & Count \\
+  \midrule
+  Male,White & 22 \\
+  Female,White & 35 \\
+  Male,Black & 10 \\
+  Female,Black & 46 \\
+  \bottomrule
+\end{tabular}
+\end{subtable}
+\end{table}
+
 \subsection{Fairness Checker}
@@
 \section{Conclusion}
-
-Some examples.  A paginated journal article \cite{Abril07}
 

### 2024-11-10 paper/paper.tex
Added some more

@@
 
+We employed the tools of the winner of the 2018 NIST Differential Privacy Synthetic Data Challenge competition\cite{NIST2018} by Ryan McKenna\cite{Ullman2022,McKenna2022,McKenna_privatePGM,mckenna2021winning,mckenna2019graphical} and the fairness checker tool from our previous research\cite{yuan2024ensuring}.
+
+The research is implemented in Python Jupyter notebooks and is publicly available.
+
 \subsection{Differentially Private Synthetic Data}
 
-We employed the tools of the winner of the 2018 NIST Differential Privacy Synthetic Data Challenge competition\cite{NIST2018} by Ryan McKenna\cite{Ullman2022,McKenna2022,McKenna_privatePGM,mckenna2021winning,mckenna2019graphical}.
-
-The competition considers marginals of the synthetic data.
+The NIST competition considers marginals of the synthetic data.
 The idea of marginal-based synthetic data generation is to create a model whose marginals of samples are similar to the marginals of the original data.
-For example, suppose we have an original database and it's 2-way marginal on sex(Male,Female) and race(White,Black) is as shown in Table~\ref{tab:marginal-example}.
+For example, suppose we have an original database with attributes including sex(Male,Female) and race(White,Black) and its 2-way marginal on them is as shown in Table~\ref{tab:marginal-example}.
+The marginal of the synthetic data is supposed to be similar to that of the original database.
 
@@
 
+The synthesis framework is three-fold; namely, select-measure-generate.
+We first select the important marginals to preserve, measure them by adding differential private noise, and then generate synthetic data.
+Underneath the hood, the tool employs a Markov random field(MRF) and the select step corresponds to marking cliques in a MRF.
+
+For the select step, we followed the techniques used by Ryan McKenna in the competition by calculating the mutual information(MI) of the given database and then create a maximum spanning tree(MST) with edge weights being the MIs.
+We further added edges according to a fraction of the upper bounds of each MI by calculating the Shannon entropies.
+
+For the measure and generate step, we simply followed the examples provided in the tool's repository.
+We added Gaussian noise to the marginals.
+we spent half of the privacy budget $\epsilon = 1$ on all 1-way marginals and the other on the MRF cliques.
+And then we generate synthetic data of size similar to the original database.
+By \cite{mckenna2021winning}, this procedure satisfies $(\alpha,\frac{\alpha}{2 \sigma^2})$-RDP for all $\alpha \geq 1$.
+
 \subsection{Fairness Checker}
 
-\subsection{Implementation}
+We used the fairness checker from \cite{yuan2024ensuring}.
+We set the privileged predicate $\priv$ to male and the positive predicate $\pos$ to the positive prediction of each of the corresponding dataset.
+
+\subsection{Test Models}
+
+We extracted various models from Kaggle.
+They are finetuned to perform well on the original dataset.
+For one, a random forest model is finetuned by searching hyperparameters settings\cite{Ipbyrne2023}.
+For another, a logistic regression model is finetuned by performing principal component analysis\cite{Prashant1112023}.
 

### 2024-11-26 paper/paper.tex
Some progress

@@
 \renewcommand{\implies}{\rightarrow}
-\newcommand{\db}{\mathcal{D}}
+\newcommand{\db}{D}
+\newcommand{\dbs}{\mathcal{D}}
 \newcommand{\model}{\mathcal{M}}
@@
 
-\section{Auditing Framework}
-
-Our framework considers a scenario with three parties-data provider, model maker, and 3rd party auditor.
-The data provider has access to real data; for example, a census bureau.
-The model maker have AI models; for example, an AI company.
-The 3rd party auditor takes the data from data provider and AI models from model makers and perform fairness audits on them; for example, an investigative journalist.
-
-In our original framework\cite{yuan2024ensuring}, after obtaining real data from data provider, the 3rd party auditor holds onto the real data for performing fairness audits.
-However, this may introduce privacy concerns such as security breach of the auditor.
-
-Thus, we introduce a new framework where the auditor generates synthetic data based on real data upon retrival of the real data, and then holds onto the synthetic data and discards the real data, preventing further privacy breaches.
-
-\subsection{Preliminaries}
+\section{Preliminaries}
 
@@
 A \emph{database} $\db = \set{r_1, r_2, ...}$ is a collection of rows.
-The attributes of $\db$ is $\mathcal{A} = \set{A_1, A_2, ...}$.
+The set of all databases is denoted $\dbs$.
+The attributes of a $\db$ is $\mathcal{A} = \set{A_1, A_2, ...}$.
 The domain of $A_i$ is $\Omega_i$.
-
-For fairness measures\cite{yuan2024ensuring,pessach2022review}, let $Y$ to denote the ground truth of an outcome, let $\hat{Y}$ to denote the predicated result of an outcome, let $S$ denote protected attribute, and let $\epsilon$ denote some threshold.
-For non-binary prediction, such as a score, we use $\hat{V}$.
-
-Let $C \subseteq \mathcal{A}$.
-Let $\Omega_C = \Pi_{i \in C} \Omega_i$.
-The \emph{marginal}\cite{barak2007privacy,mckenna2021winning} on $C$ is a vector $\mu \in \mathbb{R}^{\abs{\Omega_C}}$, indexed by domain element $t \in \Omega_C$, such that each entry is a count $\mu_t = \Sigma_{x \in \db} \vmathbb{1} [x_C = t]$ where $\vmathbb{1}$ is the indicator function.
-Let $M_C(\db)$ be the function that computes the marginal on $C$, i.e., $\mu = M_C(\db)$.
-We call marginals of $|C| = n$ attributes $n$-way marginals.
-
-A \emph{randomized mechanism} is a randomized algorithm $M$ that takes a database $\db$ and, after, introducing noise, outputs some results in set $R$.
-
-The $p$-norm is denoted by $L_p$ and the $p$-norm of a vector $x$ is denoted by $\Vert x \Vert_p$.
-
-The normal distribution or Gaussian distribution with mean $\mu$ and standard deviation $\sigma$ is denoted by $\mathcal{N}(\mu, \sigma^2)$.
-
-The Kullback–Leibler divergence between probability distributions $P$ and $Q$ is denoted by $D_{KL}(P \Vert Q)$.
-The generalization of it, R\'enyi divergence\cite{van2014renyi}, of order $\alpha$ is denoted by $D_\alpha(P \Vert Q)$.
 
@@
 
-We consider in this work various fairness measures listed in Table~\ref{tab:measures}. They can be broadly categorized into independence, separation, and sufficiency.
+For fairness measures\cite{yuan2024ensuring,pessach2022review}, let $Y$ to denote the ground truth of an outcome, let $\hat{Y}$ to denote the predicated result of an outcome, let $S$ denote the protected attribute, and let $\epsilon$ denote some threshold.
+For non-binary prediction, such as a score, we use $\hat{V}$.
 
-\begin{definition}[Independence\cite{barocas2023fairness}]\label{def:independence}
-$(S, \hat{Y})$ satisfy independence if and only if $S \bot \hat{Y}$; that is
-\[
-P[\hat{Y} = 1 | S = 1] = P[\hat{Y} = 1 | S \neq 1]
-\]
-A relaxation of independence on a threshold is
-\[
-\abs{P[\hat{Y} = 1 | S = 1] - P[\hat{Y} = 1 | S \neq 1]} \leq \epsilon
-\]
-\end{definition}
+Fairness measures can be broadly categorized into independence, separation, and sufficiency, which are defined by conditional independence in Table~\ref{tab:categories}.
 
-\begin{definition}[Separation\cite{barocas2023fairness}]\label{def:separation}
-$(S, Y, \hat{Y})$ satisfy separation if and only if $S \bot \hat{Y} | Y$; that is
+\begin{table}[h]
+\caption{Fairness categories.}
+\label{tab:categories}
+\begin{tabular}{cc}
+\toprule
+\textbf{Category} & \textbf{Definition} \\
+\midrule
+Independence & $S \bot \hat{Y}$ \\
+Separation & $S \bot \hat{Y} | Y$ \\
+Sufficiency & $S \bot Y | \hat{Y}$ \\
+\bottomrule
+\end{tabular}
+\end{table}
+
+These categories can be expanded into forms of probability. For example, the definition of separation is expanded to
 \begin{align*}
@@
 \end{align*}
-A relaxation of independence on a threshold is
+The definition can be relaxed. Its relaxation, for some parameter $\epsilon$, is
 \begin{align*}
@@
 \end{align*}
-\end{definition}
+which is also the definition of a fairness measure called equalized odds.
 
-\begin{definition}[Sufficiency\cite{barocas2023fairness}]\label{def:separation}
-$(S, Y, \hat{Y})$ satisfy sufficiency if and only if $S \bot Y | \hat{Y}$; that is
-\begin{align*}
-P[Y = 1 | S = 1, \hat{Y} = 1] & = P[Y = 1 | S \neq 1, \hat{Y} = 1] \\
-P[Y = 1 | S = 1, \hat{Y} = 0] & = P[Y = 1 | S \neq 1, \hat{Y} = 0]
-\end{align*}
-A relaxation of independence on a threshold is
-\begin{align*}
-\abs{P[Y = 1 | S = 1, \hat{Y} = 1] - P[Y = 1 | S \neq 1, \hat{Y} = 1]} & \leq \epsilon \\
-\abs{P[Y = 1 | S = 1, \hat{Y} = 0] - P[Y = 1 | S \neq 1, \hat{Y} = 0]} & \leq \epsilon
-\end{align*}
-\end{definition}
+We consider in this work various fairness measures listed in Table~\ref{tab:measures}.
+
+% \begin{definition}[Independence\cite{barocas2023fairness}]\label{def:independence}
+% $(S, \hat{Y})$ satisfy independence if and only if $S \bot \hat{Y}$; that is
+% \[
+% P[\hat{Y} = 1 | S = 1] = P[\hat{Y} = 1 | S \neq 1]
+% \]
+% A relaxation of independence on a threshold is
+% \[
+% \abs{P[\hat{Y} = 1 | S = 1] - P[\hat{Y} = 1 | S \neq 1]} \leq \epsilon
+% \]
+% \end{definition}
+
+% \begin{definition}[Separation\cite{barocas2023fairness}]\label{def:separation}
+% $(S, Y, \hat{Y})$ satisfy separation if and only if $S \bot \hat{Y} | Y$; that is
+% \begin{align*}
+% P[\hat{Y} = 1 | S = 1, Y = 1] & = P[\hat{Y} = 1 | S \neq 1, Y = 1] \\
+% P[\hat{Y} = 1 | S = 1, Y = 0] & = P[\hat{Y} = 1 | S \neq 1, Y = 0]
+% \end{align*}
+% A relaxation of independence on a threshold is
+% \begin{align*}
+% \abs{P[\hat{Y} = 1 | S = 1, Y = 1] - P[\hat{Y} = 1 | S \neq 1, Y = 1]} & \leq \epsilon \\
+% \abs{P[\hat{Y} = 1 | S = 1, Y = 0] - P[\hat{Y} = 1 | S \neq 1, Y = 0]} & \leq \epsilon
+% \end{align*}
+% \end{definition}
+
+% \begin{definition}[Sufficiency\cite{barocas2023fairness}]\label{def:separation}
+% $(S, Y, \hat{Y})$ satisfy sufficiency if and only if $S \bot Y | \hat{Y}$; that is
+% \begin{align*}
+% P[Y = 1 | S = 1, \hat{Y} = 1] & = P[Y = 1 | S \neq 1, \hat{Y} = 1] \\
+% P[Y = 1 | S = 1, \hat{Y} = 0] & = P[Y = 1 | S \neq 1, \hat{Y} = 0]
+% \end{align*}
+% A relaxation of independence on a threshold is
+% \begin{align*}
+% \abs{P[Y = 1 | S = 1, \hat{Y} = 1] - P[Y = 1 | S \neq 1, \hat{Y} = 1]} & \leq \epsilon \\
+% \abs{P[Y = 1 | S = 1, \hat{Y} = 0] - P[Y = 1 | S \neq 1, \hat{Y} = 0]} & \leq \epsilon
+% \end{align*}
+% \end{definition}
+
+% The $p$-norm is denoted by $L_p$ and the $p$-norm of a vector $x$ is denoted by $\Vert x \Vert_p$.
+
+% The normal distribution or Gaussian distribution with mean $\mu$ and standard deviation $\sigma$ is denoted by $\mathcal{N}(\mu, \sigma^2)$.
 
@@
 \label{tab:measures}
-\begin{tabular}{llc} % 'l' specifies left alignment for the first column
+\begin{tabular}{llc}
 \toprule
@@
 
-\begin{definition}[Sensitivity\cite{dwork2014algorithmic}]\label{def:sensitivity}
-Let $f$ be a function that takes a database $\db$ and outputs a vector $\mathbb{R}^p$. The $L_2$ sensitivity of $f$ is for all databases $\db_1,\db_2$ that differ in exactly one row:
-\[
-\Delta^2_f = max_{\db_1,\db_2} \Vert f(\db_1) - f(\db_2) \Vert_p
-\]
-\end{definition}
+% \begin{definition}[Sensitivity\cite{dwork2014algorithmic}]\label{def:sensitivity}
+% Let $f$ be a function that takes a database $\db$ and outputs a vector $\mathbb{R}^p$. The $L_2$ sensitivity of $f$ is for all databases $\db_1,\db_2$ that differ in exactly one row:
+% \[
+% \Delta^2_f = max_{\db_1,\db_2} \Vert f(\db_1) - f(\db_2) \Vert_p
+% \]
+% \end{definition}
+
+% \begin{definition}[Differential Privacy (DP) \cite{dwork2006calibrating,dwork2014algorithmic,mckenna2021winning}]\label{def:rdp}
+% A randomized mechanism $M$ satisfies $(\epsilon,\delta)$-DP if, for all databases $\db_1,\db_2$ that differ in exactly one row and for all subsets $S$ of $R$, we have
+% \[
+% \prob{M(\db_1) \in S} \leq e^\epsilon \prob{M(\db_2) \in S} + \delta
+% \]
+% \end{definition}
+
+A \emph{randomized mechanism} is a randomized algorithm $M : \dbs \implies R$ that takes a database and, after introducing noise, outputs some results.
 
 \begin{definition}[Gaussian Mechanism\cite{dwork2014algorithmic}]\label{def:gm}
-Let $f$ be a function that takes a database $\db$ and outputs a vector $\mathbb{R}^p$. The Gaussian Mechanism $M$ adds Gaussian noise with scale $\sigma$ to each of the $p$ outputs:
+Let $f : \dbs \implies \mathbb{R}^p$ be a function that takes a database and outputs a vector. The Gaussian Mechanism $M$ adds i.i.d. Gaussian noise with scale $\sigma$ to each of the $p$ outputs:
 \[
 M(\db) = f(\db) + \mathcal{N}(0, \sigma^2 \mathbb{I})
-\]
-\end{definition}
-
-\begin{definition}[Differential Privacy (DP) \cite{dwork2006calibrating,dwork2014algorithmic,mckenna2021winning}]\label{def:rdp}
-A randomized mechanism $M$ satisfies $(\epsilon,\delta)$-DP if, for all databases $\db_1,\db_2$ that differ in exactly one row and for all subsets $S$ of $R$, we have
-\[
-\prob{M(\db_1) \in S} \leq e^\epsilon \prob{M(\db_2) \in S} + \delta
 \]
@@
 \]
+where $D_\alpha$ is the R\'enyi divergence\cite{van2014renyi} of order $\alpha$.
 \end{definition}
@@
 
-\section{Methodology}
-
-We employed the tools of the winner of the 2018 NIST Differential Privacy Synthetic Data Challenge competition\cite{NIST2018} by Ryan McKenna\cite{Ullman2022,McKenna2022,McKenna_privatePGM,mckenna2021winning,mckenna2019graphical} and the fairness checker tool from our previous research\cite{yuan2024ensuring}.
-
-The research is implemented in Python Jupyter notebooks and is publicly available.
-
 \subsection{Differentially Private Synthetic Data}
 
-The NIST competition considers marginals of the synthetic data.
-The idea of marginal-based synthetic data generation is to create a model whose marginals of samples are similar to the marginals of the original data.
-For example, suppose we have an original database with attributes including sex(Male,Female) and race(White,Black) and its 2-way marginal on them is as shown in Table~\ref{tab:marginal-example}.
-The marginal of the synthetic data is supposed to be similar to that of the original database.
+Let $C \subseteq \mathcal{A}$ be a subset of attributes.
+Let $\Omega_C = \Pi_{i \in C} \Omega_i$.
+A \emph{marginal}\cite{barak2007privacy,mckenna2021winning} of $C$ is a vector $\mu \in \mathbb{R}^{\abs{\Omega_C}}$, indexed by domain element $t \in \Omega_C$, such that each entry is a count $\mu_t = \Sigma_{x \in \db} \vmathbb{1} [x_C = t]$ where $\vmathbb{1}$ is the indicator function; that is, it is the vector of the count of each possible element.
+
+Let $M_C(\db)$ be the function that computes the marginal of $C$ on $\db$, i.e., $\mu = M_C(\db)$. We call marginals of $|C| = n$ attributes $n$-way marginals.
+
+The task of differentially private synthetic data is, given a database $\db$, adding some noise such that it satisfies differential privacy guarantee and outputting another database $\db'$, such that the $L_1$ errors between some selected marginals $C_1,C_2,...$ of $\db$ and $\db'$ is small; that is, their marginals $(M_{C_1}(\db),M_{C_1}(\db')),(M_{C_2}(\db),M_{C_2}(\db')),...$ are similar.
+
+For example, suppose we have a database with attributes sex and race.
+The 2-way marginals of the original database and the synthetic database are shown in Table~\ref{tab:marginal-example}.
+The marginals of the synthetic data is supposed to be similar to that of the original database.
 
@@
 
-The synthesis framework is three-fold; namely, select-measure-generate.
-We first select the important marginals to preserve, measure them by adding differential private noise, and then generate synthetic data.
-Underneath the hood, the tool employs a Markov random field(MRF) and the select step corresponds to marking cliques in a MRF.
+\section{Auditing Framework}
 
-For the select step, we followed the techniques used by Ryan McKenna in the competition by calculating the mutual information(MI) of the given database and then create a maximum spanning tree(MST) with edge weights being the MIs.
-We further added edges according to a fraction of the upper bounds of each MI by calculating the Shannon entropies.
+Our auditing framework is tripartite. It consists of three parties: the data provider, the model maker, and the third-party auditor.
+
+The data provider is responsible for supplying the raw datasets which should originate from trustworthy sources, such as government agencies like a census bureau.
+
+The model maker develops AI models. These are AI companies or research labs specialized in training and optimizing AI models.
+
+The third-party auditor acts as an evaluator, using our framework to audit the AI models for fairness issues by combining both the datasets and the models.
+These may be investigative journalists or regulatory bodies.
+
+In the framework of our previous work\cite{yuan2024ensuring}, after obtaining real data from the data provider, the 3rd party auditor holds onto the real data for performing fairness audits, and it supposedly retains it indefinitely for the possibility of any future audits.
+
+However, this practice introduces security concerns. It creates a vulnerability to data security threats. A breach at the auditor's end could result in compromises of individuals' privacy.
+
+Moreover, the storage of the datasets also raises privacy concerns.
+Holding large amounts of sensitive data for an extended period opens the door to the risk of misuse.
+The auditor may misuse the data for unauthorized purposes.
+
+Thus, we introduce a new framework where the auditor generates synthetic data based on real data upon retrieval of the real data, and then holds onto the synthetic data and discards the real data, preventing further privacy breaches.
+
+\subsection{Methodology}
+
+We employed the tools of the winner of the 2018 NIST Differential Privacy Synthetic Data Challenge competition\cite{NIST2018} by Ryan McKenna\cite{Ullman2022,McKenna2022,McKenna_privatePGM,mckenna2021winning,mckenna2019graphical} and the fairness checker tool from our previous research\cite{yuan2024ensuring}.
+
+% This research is implemented in Python Jupyter notebooks and is publicly available.
+
+The synthesis framework is three-fold; namely, select-measure-generate\cite{McKenna2022}.
+We first select the important marginals to preserve, measure them by adding differentially private noise, and then generate synthetic data.
+
+Underneath the hood, the tool employs a Markov random field (MRF) and the select step corresponds to marking cliques in an MRF.
+By default, all $1$-way marginals are selected to preserve the quantity of each attribute element.
+
+We can further preserve correlations by adding $n$-way marginals. For example, if we want to preserve the relationship between sex and race, we may add the clique containing sex and race.
+
+In a perfect world where all correlation information is to be preserved, we may wish to make a completely connected graph.
+However, this was found to be intractable as the complexity of the problem would skyrocket.
+
+To circumvent the complexity explosion, instead, Ryan McKenna devised a technique where the mutual information(MI) of the all database attribute pairs are calculated and then a maximum spanning tree(MST) algorithm was run with edge weights being the MIs to obtain a skeleton MST MRF.
+
+For the competition, Ryan McKenna further manually added certain cliques based on his investigation of the competition dataset.
+
+For the select step, we followed the techniques used by . We further added edges according to a fraction of the upper bounds of each MI by calculating the Shannon entropies.
 

### 2024-11-26 paper/paper.tex
Added data synthesis

@@
 
-\subsection{Methodology}
+\section{Methodology}
 
@@
 
-% This research is implemented in Python Jupyter notebooks and is publicly available.
+This research is implemented in Python Jupyter notebooks and is publicly available.
+
+\subsection{Data Synthesis}
 
@@
 
-Underneath the hood, the tool employs a Markov random field (MRF) and the select step corresponds to marking cliques in an MRF.
+Underneath the hood, the tool employs a Markov random field (MRF). The select step corresponds to marking cliques in an MRF, and the generate step corresponds to sampling from the fitted MRF.
+
 By default, all $1$-way marginals are selected to preserve the quantity of each attribute element.
-
-We can further preserve correlations by adding $n$-way marginals. For example, if we want to preserve the relationship between sex and race, we may add the clique containing sex and race.
+We can further preserve correlations by adding $n$-way marginals.
+For example, if we want to preserve the relationship between sex and race, we may add the clique (sex,race).
 
@@
 For the competition, Ryan McKenna further manually added certain cliques based on his investigation of the competition dataset.
+For example, he manually added the clique (sex,city,income).
+In addition, he would add some edges based on some heuristics tailored to that particular dataset.
 
-For the select step, we followed the techniques used by . We further added edges according to a fraction of the upper bounds of each MI by calculating the Shannon entropies.
+We came up with an alternative heuristic for a general purpose workflow.
+Since MIs are bounded by the minimum of the pair's respective Shannon entropies, we add additional edges according to a fraction of this upper bounds.
 
-For the measure and generate step, we simply followed the examples provided in the tool's repository.
-We added Gaussian noise to the marginals.
-we spent half of the privacy budget $\epsilon = 1$ on all 1-way marginals and the other on the MRF cliques.
-And then we generate synthetic data of size similar to the original database.
+For the measure step, we followed the examples provided in the tool's repository.
+Gaussian noises are added to the selected marginals.
+Half of the privacy budget are spent on all 1-way marginals and the other half on the selected cliques.
+These marginals are then fed to the tool to fit the MRF.
 By \cite{mckenna2021winning}, this procedure satisfies $(\alpha,\frac{\alpha}{2 \sigma^2})$-RDP for all $\alpha \geq 1$.
 
-\subsection{Fairness Checker}
+\subsection{Fairness Checking}
 
-We used the fairness checker from \cite{yuan2024ensuring}.
+% We used the fairness checker from \cite{yuan2024ensuring}.
 We set the privileged predicate $\priv$ to male and the positive predicate $\pos$ to the positive prediction of each of the corresponding dataset.
@@
 
-We extracted various models from Kaggle.
+% We extracted various models from Kaggle.
 They are finetuned to perform well on the original dataset.

### 2024-11-26 paper/paper.tex
grammar

@@
 
-The synthesis framework is three-fold; namely, select-measure-generate\cite{McKenna2022}.
+The synthesis framework is three-fold, namely, select-measure-generate\cite{McKenna2022}.
 We first select the important marginals to preserve, measure them by adding differentially private noise, and then generate synthetic data.
@@
 
-To circumvent the complexity explosion, instead, Ryan McKenna devised a technique where the mutual information(MI) of the all database attribute pairs are calculated and then a maximum spanning tree(MST) algorithm was run with edge weights being the MIs to obtain a skeleton MST MRF.
+To circumvent the complexity explosion, instead, Ryan McKenna devised a technique where the mutual information(MI) of all the database attribute pairs is calculated, and then a maximum spanning tree(MST) algorithm was run with edge weights being the MIs to obtain a skeleton MST MRF.
 
@@
 
-We came up with an alternative heuristic for a general purpose workflow.
-Since MIs are bounded by the minimum of the pair's respective Shannon entropies, we add additional edges according to a fraction of this upper bounds.
+We developed an alternative heuristic for a general-purpose workflow.
+Since MIs are bounded by the minimum of the pair's respective Shannon entropies, we add additional edges according to a fraction of these upper bounds.
 
@@
 Gaussian noises are added to the selected marginals.
-Half of the privacy budget are spent on all 1-way marginals and the other half on the selected cliques.
+Half of the privacy budget is spent on all 1-way marginals and the other half on the selected cliques.
 These marginals are then fed to the tool to fit the MRF.

### 2024-11-26 paper/paper.tex
some progress

@@
 
-Underneath the hood, the tool employs a Markov random field (MRF). The select step corresponds to marking cliques in an MRF, and the generate step corresponds to sampling from the fitted MRF.
+Underneath the hood, the tool employs a Markov random field.
+The select step corresponds to marking cliques in a Markov random field, and the generate step corresponds to sampling from the fitted Markov random field.
 
@@
 
-To circumvent the complexity explosion, instead, Ryan McKenna devised a technique where the mutual information(MI) of all the database attribute pairs is calculated, and then a maximum spanning tree(MST) algorithm was run with edge weights being the MIs to obtain a skeleton MST MRF.
+To circumvent the complexity explosion, instead, Ryan McKenna devised a technique where the mutual information of all the database attribute pairs is calculated, and then a maximum spanning tree algorithm was run with edge weights being the mutual information to obtain a skeleton spanning-tree-shaped Markov random field.
 
@@
 We developed an alternative heuristic for a general-purpose workflow.
-Since MIs are bounded by the minimum of the pair's respective Shannon entropies, we add additional edges according to a fraction of these upper bounds.
+From the definition of mutual information, we can obtain that they are bounded by the pair's respective Shannon entropy.
+Using this property, we add additional edges with weights exceeding a fraction of the minimum of these upper bounds.
+As a rule of thumb, we have found setting the fraction to be $0.1$ to be effective.
 
@@
 Half of the privacy budget is spent on all 1-way marginals and the other half on the selected cliques.
-These marginals are then fed to the tool to fit the MRF.
+These marginals are then fed to the tool to fit the Markov random field.
 By \cite{mckenna2021winning}, this procedure satisfies $(\alpha,\frac{\alpha}{2 \sigma^2})$-RDP for all $\alpha \geq 1$.
@@
 
-% We used the fairness checker from \cite{yuan2024ensuring}.
-We set the privileged predicate $\priv$ to male and the positive predicate $\pos$ to the positive prediction of each of the corresponding dataset.
+After synthesizing datasets, we used the fairness checker from \cite{yuan2024ensuring} to compute their fairness measures.
+To test the viability of our method, we compare the metrics computed from the synthetic dataset against those of the original dataset.
 

### 2024-11-26 paper/paper.tex
some progress

@@
 For example, he manually added the clique (sex,city,income).
-In addition, he would add some edges based on some heuristics tailored to that particular dataset.
+In addition, he would add some edges based on some sophisticated heuristics tailored to that particular dataset.
 
@@
 To test the viability of our method, we compare the metrics computed from the synthetic dataset against those of the original dataset.
+We used various datasets with fairness concerns mentioned in \cite{pessach2022review}.
 
-\subsection{Test Models}
+The fairness checker evaluates datasets based on multiple fairness metrics, such as demographic parity and equalized odds.
+These metrics are computed on some sensitive attributes, predicted outcomes, and ground truths.
+Examples of sensitive attributes are race and sex.
+Examples of predicted outcomes and ground truths are loan approval and criminal recidivism.
 
-% We extracted various models from Kaggle.
+By comparing these measures between the synthetic and original datasets, we aim to ensure that the synthetic data preserves the fairness properties of the original data.
+The comparison process is three-fold.
+It goes as follows.
+
+The dataset is first processed so it can be fed into the synthetic data generator.
+Some marginals are selected as described in the previous section, and the synthetic data generator model is fitted to the original data according to the marginals.
+Then the generator is run multiple times to obtain multiple sets of synthetic data.
+
+Next, AI models are extracted from various real life authors from Kaggle.
 They are finetuned to perform well on the original dataset.
@@
 For another, a logistic regression model is finetuned by performing principal component analysis\cite{Prashant1112023}.
+
+AI models and both the original dataset and the synthetic datasets are fed to the fairness checker.
+Sensitive attributes are identified based on manual examination with common sense or by referring to \cite{pessach2022review}.
+Then, all applicable fairness measures are computed using the checker for both the original dataset and the rounds of synthetic datasets.
+
+Finally, we analyze the discrepancies between the fairness properties of the original and the synthetic by calculating the difference and the ratio of their perspective fairness measure values.
+The sum of the difference and the average of the ratio serve as a summary of the analysis.
 

### 2024-11-26 paper/paper.tex
some progress

@@
 
-Next, AI models are extracted from various real life authors from Kaggle.
+Next, several AI models are extracted from various real life authors from Kaggle.
 They are finetuned to perform well on the original dataset.
@@
 
-AI models and both the original dataset and the synthetic datasets are fed to the fairness checker.
+Several AI models and both the original dataset and the rounds of synthetic datasets are fed to the fairness checker.
 Sensitive attributes are identified based on manual examination with common sense or by referring to \cite{pessach2022review}.
-Then, all applicable fairness measures are computed using the checker for both the original dataset and the rounds of synthetic datasets.
+Then, all applicable fairness measures are computed using the checker for both the original and the synthetic.
 
@@
 
+\begin{figure}[h]
+\centering
+\includegraphics[width=\linewidth]{adult_mst}
+\caption{Markov random field for marginals of the adult dataset.}
+\Description{Markov random field for marginals of the adult dataset.}
+\end{figure}
+
+\begin{table}[h]
+\caption{Fairness measures experiment results.}
+\label{tab:categories}
+\begin{tabular}{p{0.3\linewidth}cccc}
+\toprule
+\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} & \textbf{Ratio} \\
+\midrule
+Demographic Parity  & 0.172 & 0.104 & 0.067 & 1.651 \\
+Accuracy Eqaulity   & 0.047 & 0.117 & 0.069 & 0.404 \\
+Equalized Odds 1    & 0.057 & 0.079 & 0.021 & 0.723 \\
+Equalized Odds 2    & 0.166 & 0.122 & 0.044 & 1.365 \\
+Accuracy Equality 1 & 0.100 & 0.132 & 0.031 & 0.759 \\
+Accuracy Equality 2 & 0.119 & 0.146 & 0.027 & 0.814 \\
+\bottomrule
+\end{tabular}
+\end{table}
+
 \subsection{COMPAS Dataset}
 
-\subsection{One More Dataset}
+\begin{figure}[h]
+\centering
+\includegraphics[width=\linewidth]{compas_mst}
+\caption{Markov random field for marginals of the COMPAS dataset.}
+\Description{Markov random field for marginals of the COMPAS dataset.}
+\end{figure}
+
+\begin{table}[h]
+\caption{Fairness measures experiment results.}
+\label{tab:categories}
+\begin{tabular}{p{0.3\linewidth}cccc}
+\toprule
+\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} & \textbf{Ratio} \\
+\midrule
+Demographic Parity     & 0.131 & 0.098 & 0.032 & 1.329 \\
+Accuracy Eqaulity      & 0.007 & 0.013 & 0.005 & 0.575 \\
+Equalized Odds 1       & 0.024 & 0.099 & 0.074 & 0.249 \\
+Equalized Odds 2       & 0.017 & 0.097 & 0.079 & 0.182 \\
+Accuracy Equality 1 & 0.170 & 0.082 & 0.088 & 2.082 \\
+Accuracy Equality 2 & 0.169 & 0.027 & 0.141 & 6.058 \\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\subsection{Diabetes Dataset}
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=\linewidth]{diabetes_mst}
+\caption{Markov random field for marginals of the diabetes dataset.}
+\Description{Markov random field for marginals of the COMPAS dataset.}
+\end{figure}
+
+\begin{table}[h]
+\caption{Fairness measures experiment results.}
+\label{tab:categories}
+\begin{tabular}{p{0.3\linewidth}cccc}
+\toprule
+\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} & \textbf{Ratio} \\
+\midrule
+Demographic Parity  & 0.013 & 0.015 & 0.002 & 0.867 \\
+Accuracy Eqaulity   & 0.007 & 0.009 & 0.002 & 0.782 \\
+Equalized Odds 1    & 0.000 & 0.003 & 0.003 & 0.000 \\
+Equalized Odds 2    & 0.008 & 0.106 & 0.097 & 0.081 \\
+Accuracy Equality 1 & 0.013 & 0.097 & 0.084 & 0.136 \\
+Accuracy Equality 2 & 0.021 & 0.020 & 0.001 & 1.068 \\
+\bottomrule
+\end{tabular}
+\end{table}
 
@@
 \section{Conclusion}
-
-% \begin{table}
-%   \caption{Frequency of Special Characters}
-%   \label{tab:freq}
-%   \begin{tabular}{ccl}
-%     \toprule
-%     Non-English or Math&Frequency&Comments\\
-%     \midrule
-%     \O & 1 in 1,000& For Swedish names\\
-%     $\pi$ & 1 in 5& Common in math\\
-%     \$ & 4 in 5 & Used in business\\
-%     $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-%   \bottomrule
-% \end{tabular}
-% \end{table}
-
-% \begin{table*}
-%   \caption{Some Typical Commands}
-%   \label{tab:commands}
-%   \begin{tabular}{ccl}
-%     \toprule
-%     Command &A Number & Comments\\
-%     \midrule
-%     \texttt{{\char'134}author} & 100& Author \\
-%     \texttt{{\char'134}table}& 300 & For tables\\
-%     \texttt{{\char'134}table*}& 400& For wider tables\\
-%     \bottomrule
-%   \end{tabular}
-% \end{table*}
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=\linewidth]{compas_mst}
-  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
-    Ewing, Inc. [Public domain], via Wikimedia
-    Commons. (\url{https://goo.gl/VLCRBB}).}
-  \Description{A woman and a girl in white dresses sit in an open car.}
-\end{figure}
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=\linewidth]{adult_mst}
-  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
-    Ewing, Inc. [Public domain], via Wikimedia
-    Commons. (\url{https://goo.gl/VLCRBB}).}
-  \Description{A woman and a girl in white dresses sit in an open car.}
-\end{figure}
 

### 2024-11-27 paper/paper.tex
some progress

@@
 %%
-% \documentclass[manuscript,screen,review]{acmart}
+% \documentclass[manuscript,screen,review,anonymous]{acmart}
 \documentclass[acmsmall,sigconf]{acmart}
@@
 
+We looked at several publicly available datasets, such as adult\cite{adult_2,Kaggle_Adult_Census_Income}, COMPAS\cite{larson2016propublica,Kaggle_COMPAS_Dataset}, and diabetes\cite{diabetes_34,Kaggle_Diabetes_Prediction}.
+The adult dataset comes from the 1994 census in the United States.
+The COMPAS dataset comes from an investigative report by ProPublica of the COMPAS criminal recidivism assessment system.
+The diabetes dataset comes from the hospital readmission data published in the 1994 AI in Medicine journal.
+
 \subsection{Adult Income Dataset}
+
+For the adult income dataset, the shape of the maximum spanning tree is very shallow, almost resembling a star; it has one internal node and all but one of the leaves have a depth of one.
+After introducing edges according to our heuristic, we observed an increase in the pairwise edges of the leaves, forming many 3-cliques and two 4-cliques.
+The resulting graph is shown in Figure~\ref{fig:adult_mst}.
+
+Marginals based on this graph are then passed to the synthetic data generator for model fitting.
 
@@
 \caption{Markov random field for marginals of the adult dataset.}
+\label{fig:adult_mst}
 \Description{Markov random field for marginals of the adult dataset.}
@@
 
+After generating ten rounds of synthetic data and passing them to the checker, their fairness measure values are averaged.
+Then, we compare them against the values of the original data.
+The results are shown in Table~\ref{tab:adult_score}.
+
+We observed that across all examined fairness measures, their difference all fall below 0.1.
+The sum of their differences is 0.259 and the average of their ratios is 0.952, which we consider quite satisfactory.
+
 \begin{table}[h]
-\caption{Fairness measures experiment results.}
-\label{tab:categories}
-\begin{tabular}{p{0.3\linewidth}cccc}
+\caption{Fairness measures experiment results of the adult dataset. Sum of differences is 0.259. Average of ratios is 0.952.}
+\label{tab:adult_score}
+\begin{tabular}{ccccc}
 \toprule
-\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} & \textbf{Ratio} \\
+\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Diff} & \textbf{Ratio} \\
 \midrule
@@
 
+For the COMPAS dataset, the initial spanning tree has a long tail, which is not surprising because, upon closer inspection, they all are related to the original COMPAS risk scores.
+The heuristic edge addition did not change the graph significantly.
+It only introduced one 3-clique triangle.
+The resulting graph is shown in Figure~\ref{fig:compas_mst}.
+
+Marginals of this graph are then too passed to the synthetic data generator for fitting.
+
 \begin{figure}[h]
@@
 \caption{Markov random field for marginals of the COMPAS dataset.}
+\label{fig:compas_mst}
 \Description{Markov random field for marginals of the COMPAS dataset.}
@@
 
+We ran the same workflow as adult dataset for the COMPAS dataset. The comparison results are shown in Table~\ref{tab:compas_score}.
+
+The results showed an increase in error on the sufficiency measure values.
+In particular, one of the measures has an error ratio as high as 6.
+The sum of their differences is 0.419, and the average of their ratios is 1.745, which is worse than the adult dataset.
+
 \begin{table}[h]
-\caption{Fairness measures experiment results.}
-\label{tab:categories}
-\begin{tabular}{p{0.3\linewidth}cccc}
+\caption{Fairness measures experiment results of the COMPAS dataset. Sum of differences is 0.419. Average of ratios is 1.745.}
+\label{tab:compas_score}
+\begin{tabular}{ccccc}
 \toprule
-\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} & \textbf{Ratio} \\
+\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Diff} & \textbf{Ratio} \\
 \midrule
@@
 
+The tree grown from the diabetes dataset did not appear to have any particular characteristics.
+The root of the tree is placed in the BMI value, which reasonably captures most information.
+The heuristic edge addition process introduced some 3-clique triangles.
+The resulting graph is shown in Figure~\ref{fig:diabetes_mst}.
+
+The same process is conducted to fit the synthetic data generator model.
+
 \begin{figure}[h]
@@
 \caption{Markov random field for marginals of the diabetes dataset.}
+\label{fig:diabetes_mst}
 \Description{Markov random field for marginals of the COMPAS dataset.}
@@
 
+The same workflow was done as on previous datasets. The comparison results are shown in Table~\ref{tab:diabetes_score}.
+
+There was also an increase of error on some sufficiency measure values.
+The sum of their differences is 0.189 and the average of their ratios is 0.489.
+However, this comparison may be skewed because one of the fairness measures in the original data was calculated to be zero, thus making the average ratio seem lower than otherwise.
+
 \begin{table}[h]
-\caption{Fairness measures experiment results.}
-\label{tab:categories}
-\begin{tabular}{p{0.3\linewidth}cccc}
+\caption{Fairness measures experiment results of the COMPAS dataset. Sum of differences is 0.189. Average of ratios is 0.489.}
+\label{tab:diabetes_score}
+\begin{tabular}{ccccc}
 \toprule
-\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} & \textbf{Ratio} \\
+\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Diff} & \textbf{Ratio} \\
 \midrule

### 2024-11-27 paper/paper.tex
changed title
Added some refs

@@
 %% allowing the author to define a "short title" to be used in page headers.
-\title{The Name of the Title Is Hope}
+\title{Quantitative Auditing of Fairness Measures with Differentially Private Synthetic Data}
 
@@
 
-\received{20 February 2007}
-\received[revised]{12 March 2009}
-\received[accepted]{5 June 2009}
+% \received{20 February 2007}
+% \received[revised]{12 March 2009}
+% \received[accepted]{5 June 2009}
 
@@
 
-The task of differentially private synthetic data is, given a database $\db$, adding some noise such that it satisfies differential privacy guarantee and outputting another database $\db'$, such that the $L_1$ errors between some selected marginals $C_1,C_2,...$ of $\db$ and $\db'$ is small; that is, their marginals $(M_{C_1}(\db),M_{C_1}(\db')),(M_{C_2}(\db),M_{C_2}(\db')),...$ are similar.
+The task of differentially private synthetic data\cite{NIST_Differentially_Private_Synthetic_Data,YouTube_Differentially_Private_Synthetic_Data} is, given a database $\db$, adding some noise such that it satisfies differential privacy guarantee and outputting another database $\db'$, such that the $L_1$ errors between some selected marginals $C_1,C_2,...$ of $\db$ and $\db'$ is small; that is, their marginals $(M_{C_1}(\db),M_{C_1}(\db')),(M_{C_2}(\db),M_{C_2}(\db')),...$ are similar.
 

### 2024-11-28 paper/paper.tex
Added todos

@@
 %%
-% \documentclass[manuscript,screen,review,anonymous]{acmart}
-\documentclass[acmsmall,sigconf]{acmart}
+\documentclass[manuscript,screen,review,anonymous]{acmart}
+% \documentclass[acmsmall,sigconf]{acmart}
 
@@
 % \acmConference[Conference acronym 'XX]{Make sure to enter the correct
-%   conference title from your rights confirmation emai}{June 03--05,
+%   conference title from your rights confirmation emai}{June 0--05,
 %   2018}{Woodstock, NY}
@@
 
+TODO: cart prod, shannon, mi, mrf definition
+
 \subsection{Fairness Measures}
@@
 Fairness measures can be broadly categorized into independence, separation, and sufficiency, which are defined by conditional independence in Table~\ref{tab:categories}.
+
+TODO: bot is independence
 
@@
 
-\subsection{Differential Privacy}
+\subsection{R\'enyi Differential Privacy}
 
@@
 where $D_\alpha$ is the R\'enyi divergence\cite{van2014renyi} of order $\alpha$.
+
+TODO: formula def
+
 \end{definition}
@@
 The Gaussian Mechanism satisfies $(\alpha, \alpha \frac{\Delta^2_f}{2 \sigma^2})$-RDP.
+
+TODO: sensitivity
 \end{theorem}
@@
 
+% TODO: x_c def
+
 Let $M_C(\db)$ be the function that computes the marginal of $C$ on $\db$, i.e., $\mu = M_C(\db)$. We call marginals of $|C| = n$ attributes $n$-way marginals.
@@
 The task of differentially private synthetic data\cite{NIST_Differentially_Private_Synthetic_Data,YouTube_Differentially_Private_Synthetic_Data} is, given a database $\db$, adding some noise such that it satisfies differential privacy guarantee and outputting another database $\db'$, such that the $L_1$ errors between some selected marginals $C_1,C_2,...$ of $\db$ and $\db'$ is small; that is, their marginals $(M_{C_1}(\db),M_{C_1}(\db')),(M_{C_2}(\db),M_{C_2}(\db')),...$ are similar.
+
+TODO: add noise to marginal not database
 
@@
 
-\section{Auditing Framework}
+\section{Motivation}
 
@@
 
-The third-party auditor acts as an evaluator, using our framework to audit the AI models for fairness issues by combining both the datasets and the models.
+The third-party auditor acts as an evaluator, using our tool to audit the AI models for fairness issues by combining both the datasets and the models.
 These may be investigative journalists or regulatory bodies.
@@
 However, this practice introduces security concerns. It creates a vulnerability to data security threats. A breach at the auditor's end could result in compromises of individuals' privacy.
+
+TODO:
+security => unauthorized access. bulwark database
+privacy => authorized access, no info leak
 
@@
 \section{Methodology}
+
+TODO: remove all names of ryan meckenna. use references
 
@@
 In addition, he would add some edges based on some sophisticated heuristics tailored to that particular dataset.
+
+TODO: spell it out that his methods is not general purposes
 
@@
 
+TODO: section experiment vs Methodology. move results to experiment
+
 Next, several AI models are extracted from various real life authors from Kaggle.
@@
 \section{Results}
+
+TODO: dataset sizes
 
@@
 
-\section{Discussion}
+TODO: only compare diff. remove ratios. use avg of diff.
+
+\section{Evaluation}
 

### 2024-11-29 paper/paper.tex
mi def

@@
 \newcommand{\prob}[1]{\text{Pr}[#1]}
+\newcommand{\mi}[2]{I(#1;#2)}
+\newcommand{\entropy}[1]{H(#1)}
 
@@
 
+Let $\prod_i x_i$ denotes the Cartesian product of $x_i$s.
+
 A \emph{row} $r_i$ is a lookup table or dictionary.
@@
 
-TODO: cart prod, shannon, mi, mrf definition
+Let $X \in \mathcal{X}$ be a discrete random variable and $p(x) := \prob{X = x}$.
+Its \emph{marginal Shannon entropy} is $\entropy{X} := -\sum_{x \in \mathcal{X}} p(x) \text{log} p(x)$.
+It quantifies the level of uncertainty of $X$.
+Let $Y \in \mathcal{Y}$ be another discrete random variable.
+Their \emph{joint Shannon entropy} is $\entropy{X,Y} := -\sum_{x \in \mathcal{X}} \sum_{y \in \mathcal{Y}} p(x, y) \text{log} p(x, y)$.
+
+Let $X,Y$ be discrete random variables.
+Their \emph{mutual information} is $\mi{X}{Y} := \entropy{X} + \entropy{Y} - \entropy{X,Y}$.
+It quantifies the level of dependence between $X$ and $Y$.
+By definition, the joint entropy is greater than the marginal entropies $\entropy{X,Y} \geq \text{max}(\entropy{X},\entropy{Y})$.
+Hence, we have an upper bound of mutual information $\mi{X}{Y} \leq \text{min}(\entropy{X}, \entropy{Y})$.
+
+TODO: mrf definition
 
@@
 Let $C \subseteq \mathcal{A}$ be a subset of attributes.
-Let $\Omega_C = \Pi_{i \in C} \Omega_i$.
+Let $\Omega_C = \prod_{i \in C} \Omega_i$.
 A \emph{marginal}\cite{barak2007privacy,mckenna2021winning} of $C$ is a vector $\mu \in \mathbb{R}^{\abs{\Omega_C}}$, indexed by domain element $t \in \Omega_C$, such that each entry is a count $\mu_t = \Sigma_{x \in \db} \vmathbb{1} [x_C = t]$ where $\vmathbb{1}$ is the indicator function; that is, it is the vector of the count of each possible element.
@@
 
-The task of differentially private synthetic data\cite{NIST_Differentially_Private_Synthetic_Data,YouTube_Differentially_Private_Synthetic_Data} is, given a database $\db$, adding some noise such that it satisfies differential privacy guarantee and outputting another database $\db'$, such that the $L_1$ errors between some selected marginals $C_1,C_2,...$ of $\db$ and $\db'$ is small; that is, their marginals $(M_{C_1}(\db),M_{C_1}(\db')),(M_{C_2}(\db),M_{C_2}(\db')),...$ are similar.
+The task of differentially private synthetic data\cite{Ullman2022,McKenna2022,NIST_Differentially_Private_Synthetic_Data,YouTube_Differentially_Private_Synthetic_Data} is, given a database $\db$, adding some noise such that it satisfies differential privacy guarantee and outputting another database $\db'$, such that the $L_1$ errors between some selected marginals $C_1,C_2,...$ of $\db$ and $\db'$ is small; that is, their marginals $(M_{C_1}(\db),M_{C_1}(\db')),(M_{C_2}(\db),M_{C_2}(\db')),...$ are similar.
 
@@
 Thus, we introduce a new framework where the auditor generates synthetic data based on real data upon retrieval of the real data, and then holds onto the synthetic data and discards the real data, preventing further privacy breaches.
+The third-party thus retains the ability to audit all incoming future models as needed.
 
@@
 
-We employed the tools of the winner of the 2018 NIST Differential Privacy Synthetic Data Challenge competition\cite{NIST2018} by Ryan McKenna\cite{Ullman2022,McKenna2022,McKenna_privatePGM,mckenna2021winning,mckenna2019graphical} and the fairness checker tool from our previous research\cite{yuan2024ensuring}.
+We employed the tools of the winner of the 2018 NIST Differential Privacy Synthetic Data Challenge competition\cite{NIST2018} by \cite{McKenna_privatePGM,mckenna2021winning,mckenna2019graphical} and the fairness checker tool from our previous research\cite{yuan2024ensuring}.
 
@@
 
-To circumvent the complexity explosion, instead, Ryan McKenna devised a technique where the mutual information of all the database attribute pairs is calculated, and then a maximum spanning tree algorithm was run with edge weights being the mutual information to obtain a skeleton spanning-tree-shaped Markov random field.
+To circumvent the complexity explosion, instead, \cite{McKenna_privatePGM,mckenna2021winning} devised a technique where the mutual information of all the database attribute pairs is calculated, and then a maximum spanning tree algorithm was run with edge weights being the mutual information to obtain a skeleton spanning-tree-shaped Markov random field.
 
-For the competition, Ryan McKenna further manually added certain cliques based on his investigation of the competition dataset.
+For the competition, \cite{McKenna_privatePGM,mckenna2021winning} further manually added certain cliques based on his investigation of the competition dataset.
 For example, he manually added the clique (sex,city,income).
 In addition, he would add some edges based on some sophisticated heuristics tailored to that particular dataset.
+Meanwhile, his other apporach where the auditor does access the real dataset does not fit our framework.
 
-TODO: spell it out that his methods is not general purposes
-
-We developed an alternative heuristic for a general-purpose workflow.
+We hence developed an alternative heuristic for the general-purpose workflow.
 From the definition of mutual information, we can obtain that they are bounded by the pair's respective Shannon entropy.

### 2024-11-29 paper/paper.tex
changed refs

@@
 
-TODO: remove all names of ryan meckenna. use references
-
 We employed the tools of the winner of the 2018 NIST Differential Privacy Synthetic Data Challenge competition\cite{NIST2018} by \cite{McKenna_privatePGM,mckenna2021winning,mckenna2019graphical} and the fairness checker tool from our previous research\cite{yuan2024ensuring}.
@@
 For the competition, \cite{McKenna_privatePGM,mckenna2021winning} further manually added certain cliques based on his investigation of the competition dataset.
-For example, he manually added the clique (sex,city,income).
-In addition, he would add some edges based on some sophisticated heuristics tailored to that particular dataset.
+For example, they manually added the clique (sex,city,income).
+In addition, they would add some edges based on some sophisticated heuristics tailored to that particular dataset.
 Meanwhile, his other apporach where the auditor does access the real dataset does not fit our framework.

### 2024-11-29 paper/paper.tex
chagned stuff

@@
 \section{Preliminaries}
+\label{sec:prelim}
 
@@
 It quantifies the level of dependence between $X$ and $Y$.
-By definition, the joint entropy is greater than the marginal entropies $\entropy{X,Y} \geq \text{max}(\entropy{X},\entropy{Y})$.
+By definition\cite{entropy_lecture_notes}, the joint entropy is greater than the marginal entropies $\entropy{X,Y} \geq \text{max}(\entropy{X},\entropy{Y})$.
 Hence, we have an upper bound of mutual information $\mi{X}{Y} \leq \text{min}(\entropy{X}, \entropy{Y})$.
@@
 Fairness measures can be broadly categorized into independence, separation, and sufficiency, which are defined by conditional independence in Table~\ref{tab:categories}.
-
-TODO: bot is independence
+$X \bot Y | Z$ denotes the conditional independence between $X$ and $Y$ conditioning on $Z$.
 
@@
 
-This research is implemented in Python Jupyter notebooks and is publicly available.
+This research is conducted in Python Jupyter notebooks and is publicly available.
 
@@
 We hence developed an alternative heuristic for the general-purpose workflow.
-From the definition of mutual information, we can obtain that they are bounded by the pair's respective Shannon entropy.
+As mentioned in Section~\ref{sec:prelim}, the mutual information of two random variables is bounded by the pair's respective Shannon entropy.
 Using this property, we add additional edges with weights exceeding a fraction of the minimum of these upper bounds.
@@
 
-\section{Results}
+\section{Experiments}
 

### 2024-11-29 paper/paper.tex
some progress

@@
 \]
-where $D_\alpha$ is the R\'enyi divergence\cite{van2014renyi} of order $\alpha$.
-
-TODO: formula def
-
+where $D_\alpha(P \Vert Q)$ is the R\'enyi divergence\cite{van2014renyi,van2010renyi,li2016renyi} of order $\alpha$ between discrete probability distributions $P$ and $Q$, defined on $\mathcal{X}$:
+\[
+D_\alpha(P \Vert Q) := \frac{1}{\alpha - 1} \text{log} \sum_{x \in \mathcal{X}} {P(x)}^\alpha {Q(x)}^{1-\alpha}
+\]
 \end{definition}
@@
 \begin{theorem}[RDP of the Gaussian Mechanism\cite{feldman2018privacy,mironov2017renyi}]
-The Gaussian Mechanism satisfies $(\alpha, \alpha \frac{\Delta^2_f}{2 \sigma^2})$-RDP.
+The Gaussian Mechanism satisfies $(\alpha, \alpha \frac{\Delta^2_f}{2 \sigma^2})$-RDP, where $\Delta_f$ denotes the sensitivity\cite{dwork2014algorithmic} of $f$.
 
-TODO: sensitivity
+TODO: define sensitivity?
+
 \end{theorem}
@@
 \subsection{Differentially Private Synthetic Data}
+
+TODO: indicator thing
 
@@
 
-The task of differentially private synthetic data\cite{Ullman2022,McKenna2022,NIST_Differentially_Private_Synthetic_Data,YouTube_Differentially_Private_Synthetic_Data} is, given a database $\db$, adding some noise such that it satisfies differential privacy guarantee and outputting another database $\db'$, such that the $L_1$ errors between some selected marginals $C_1,C_2,...$ of $\db$ and $\db'$ is small; that is, their marginals $(M_{C_1}(\db),M_{C_1}(\db')),(M_{C_2}(\db),M_{C_2}(\db')),...$ are similar.
-
-TODO: add noise to marginal not database
+The task of differentially private synthetic data\cite{Ullman2022,McKenna2022,NIST_Differentially_Private_Synthetic_Data,YouTube_Differentially_Private_Synthetic_Data} is, given a database $\db$, adding some noise to some marginals of $\db$ such that it satisfies some differential privacy guarantees and outputting another database $\db'$, such that the $L_1$ errors between some marginals $C_i$s of $\db$ and $\db'$ is small; that is, their marginals $M_{C_i}(\db),M_{C_i}(\db')$ are similar.
 

### 2024-11-30 paper/paper.tex
some progress

@@
 
-% \begin{definition}[Sensitivity\cite{dwork2014algorithmic}]\label{def:sensitivity}
-% Let $f$ be a function that takes a database $\db$ and outputs a vector $\mathbb{R}^p$. The $L_2$ sensitivity of $f$ is for all databases $\db_1,\db_2$ that differ in exactly one row:
-% \[
-% \Delta^2_f = max_{\db_1,\db_2} \Vert f(\db_1) - f(\db_2) \Vert_p
-% \]
-% \end{definition}
-
 % \begin{definition}[Differential Privacy (DP) \cite{dwork2006calibrating,dwork2014algorithmic,mckenna2021winning}]\label{def:rdp}
@@
 
+Let $\db_1,\db_2$ be two databases. They are \emph{neighbors}, denoted $\db_1 \sim \db_2$, if they differ in exactly one row.
+
 \begin{definition}[Gaussian Mechanism\cite{dwork2014algorithmic}]\label{def:gm}
-Let $f : \dbs \implies \mathbb{R}^p$ be a function that takes a database and outputs a vector. The Gaussian Mechanism $M$ adds i.i.d. Gaussian noise with scale $\sigma$ to each of the $p$ outputs:
+Let $f : \dbs \implies \mathbb{R}^p$ be a function that takes a database and outputs a vector. The Gaussian Mechanism $M$ adds i.i.d. Gaussian noise with scale $\sigma$ to each of the $p$ outputs
 \[
@@
 \begin{definition}[R\'enyi Differential Privacy (RDP)]\label{def:rdp}
-A randomized mechanism $M$ satisfies $(\alpha,\gamma)$-RDP for $\alpha \geq 1$ and $\gamma \geq 1$ if, for all databases $\db_1,\db_2$ that differ in exactly one row, we have
+A randomized mechanism $M$ satisfies $(\alpha,\gamma)$-RDP for $\alpha \geq 1$ and $\gamma \geq 1$ if, for all databases $\db_1 \sim \db_2$, we have
 \[
@@
 \begin{theorem}[RDP of the Gaussian Mechanism\cite{feldman2018privacy,mironov2017renyi}]
-The Gaussian Mechanism satisfies $(\alpha, \alpha \frac{\Delta^2_f}{2 \sigma^2})$-RDP, where $\Delta_f$ denotes the sensitivity\cite{dwork2014algorithmic} of $f$.
-
-TODO: define sensitivity?
-
+The Gaussian Mechanism satisfies $(\alpha, \alpha \frac{\Delta^2_f}{2 \sigma^2})$-RDP, where $\Delta_f$ denotes the sensitivity\cite{dwork2014algorithmic} of $f$, which is defined as the maximum $L^2$-norm difference in the output of $f$
+\[
+\Delta_f := \text{max}_{\db_1 \sim \db_2} \Vert f(\db_1) - f(\db_2) \Vert_2
+\]
 \end{theorem}
@@
 
-TODO: indicator thing
-
 Let $C \subseteq \mathcal{A}$ be a subset of attributes.
 Let $\Omega_C = \prod_{i \in C} \Omega_i$.
-A \emph{marginal}\cite{barak2007privacy,mckenna2021winning} of $C$ is a vector $\mu \in \mathbb{R}^{\abs{\Omega_C}}$, indexed by domain element $t \in \Omega_C$, such that each entry is a count $\mu_t = \Sigma_{x \in \db} \vmathbb{1} [x_C = t]$ where $\vmathbb{1}$ is the indicator function; that is, it is the vector of the count of each possible element.
+Let $x$ be a row and $x_C$ denote the restriction of $x$ to $C$.
+A \emph{marginal}\cite{barak2007privacy,mckenna2021winning} of $C$ on database $\db$ is a lookup table $\mu_{\db} : \Omega_C \implies \mathbb{N}_0$ such that each entry is a count $\mu_{\db}(t) = \Sigma_{x \in \db} \delta_{t,{x_C}}$ where $\delta$ is the Kronecker function; that is, it is the vector of the counts of each possible domain element.
+We call marginals of $|C| = n$ attributes $n$-way marginals.
 
-% TODO: x_c def
-
-Let $M_C(\db)$ be the function that computes the marginal of $C$ on $\db$, i.e., $\mu = M_C(\db)$. We call marginals of $|C| = n$ attributes $n$-way marginals.
-
-The task of differentially private synthetic data\cite{Ullman2022,McKenna2022,NIST_Differentially_Private_Synthetic_Data,YouTube_Differentially_Private_Synthetic_Data} is, given a database $\db$, adding some noise to some marginals of $\db$ such that it satisfies some differential privacy guarantees and outputting another database $\db'$, such that the $L_1$ errors between some marginals $C_i$s of $\db$ and $\db'$ is small; that is, their marginals $M_{C_i}(\db),M_{C_i}(\db')$ are similar.
+The task of differentially private synthetic data\cite{Ullman2022,McKenna2022,NIST_Differentially_Private_Synthetic_Data,YouTube_Differentially_Private_Synthetic_Data} is, given a database $\db$, adding some noise to marginals of $\db$ such that it satisfies some differential privacy guarantees and outputting another database $\db'$, such that the $L^1$-norm errors between marginals of $\db$ and $\db'$ is small; that is, their marginals $\mu_{\db},\mu_{\db'}$ are similar.
 

### 2024-11-30 paper/paper.tex
removed ratios

@@
 
-Finally, we analyze the discrepancies between the fairness properties of the original and the synthetic by calculating the difference and the ratio of their perspective fairness measure values.
-The sum of the difference and the average of the ratio serve as a summary of the analysis.
+Finally, we analyze the discrepancies between the fairness properties of the original and the synthetic by calculating the difference of their perspective fairness measure values.
+The average of the differences serves as a summary of the analysis.
 
@@
 
-TODO: dataset sizes
-
 We looked at several publicly available datasets, such as adult\cite{adult_2,Kaggle_Adult_Census_Income}, COMPAS\cite{larson2016propublica,Kaggle_COMPAS_Dataset}, and diabetes\cite{diabetes_34,Kaggle_Diabetes_Prediction}.
-The adult dataset comes from the 1994 census in the United States.
-The COMPAS dataset comes from an investigative report by ProPublica of the COMPAS criminal recidivism assessment system.
-The diabetes dataset comes from the hospital readmission data published in the 1994 AI in Medicine journal.
+The adult dataset comes from the 1994 census in the United States and contains about 30000 individuals.
+The COMPAS dataset comes from an investigative report by ProPublica of the COMPAS criminal recidivism assessment system and contains about 7000 individuals.
+The diabetes dataset comes from the hospital readmission data published in the 1994 AI in Medicine journal and contains about 100000 individuals.
 
@@
 
-We observed that across all examined fairness measures, their difference all fall below 0.1.
-The sum of their differences is 0.259 and the average of their ratios is 0.952, which we consider quite satisfactory.
+We observed that across all examined fairness measures, their difference all fall below 0.1. The average of their differences is 0.0431, which we consider quite satisfactory.
 
 \begin{table}[h]
-\caption{Fairness measures experiment results of the adult dataset. Sum of differences is 0.259. Average of ratios is 0.952.}
+\caption{Fairness measures experiment results of the adult dataset. Average of differences is 0.0431.}
 \label{tab:adult_score}
@@
 \toprule
-\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Diff} & \textbf{Ratio} \\
+\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} \\
 \midrule
-Demographic Parity  & 0.172 & 0.104 & 0.067 & 1.651 \\
-Accuracy Eqaulity   & 0.047 & 0.117 & 0.069 & 0.404 \\
-Equalized Odds 1    & 0.057 & 0.079 & 0.021 & 0.723 \\
-Equalized Odds 2    & 0.166 & 0.122 & 0.044 & 1.365 \\
-Accuracy Equality 1 & 0.100 & 0.132 & 0.031 & 0.759 \\
-Accuracy Equality 2 & 0.119 & 0.146 & 0.027 & 0.814 \\
+Demographic Parity  & 0.172 & 0.104 & 0.067 \\
+Accuracy Eqaulity   & 0.047 & 0.117 & 0.069 \\
+Equalized Odds 1    & 0.057 & 0.079 & 0.021 \\
+Equalized Odds 2    & 0.166 & 0.122 & 0.044 \\
+Accuracy Equality 1 & 0.100 & 0.132 & 0.031 \\
+Accuracy Equality 2 & 0.119 & 0.146 & 0.027 \\
 \bottomrule
@@
 The results showed an increase in error on the sufficiency measure values.
-In particular, one of the measures has an error ratio as high as 6.
-The sum of their differences is 0.419, and the average of their ratios is 1.745, which is worse than the adult dataset.
+In particular, one of the measures has an error difference as high as 0.141.
+The average of their differences is 0.069, which is worse than the adult dataset.
 
 \begin{table}[h]
-\caption{Fairness measures experiment results of the COMPAS dataset. Sum of differences is 0.419. Average of ratios is 1.745.}
+\caption{Fairness measures experiment results of the COMPAS dataset. Average of differences is 0.069.}
 \label{tab:compas_score}
-\begin{tabular}{ccccc}
+\begin{tabular}{cccc}
 \toprule
-\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Diff} & \textbf{Ratio} \\
+\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} \\
 \midrule
-Demographic Parity     & 0.131 & 0.098 & 0.032 & 1.329 \\
-Accuracy Eqaulity      & 0.007 & 0.013 & 0.005 & 0.575 \\
-Equalized Odds 1       & 0.024 & 0.099 & 0.074 & 0.249 \\
-Equalized Odds 2       & 0.017 & 0.097 & 0.079 & 0.182 \\
-Accuracy Equality 1    & 0.170 & 0.082 & 0.088 & 2.082 \\
-Accuracy Equality 2    & 0.169 & 0.027 & 0.141 & 6.058 \\
+Demographic Parity     & 0.131 & 0.098 & 0.032 \\
+Accuracy Eqaulity      & 0.007 & 0.013 & 0.005 \\
+Equalized Odds 1       & 0.024 & 0.099 & 0.074 \\
+Equalized Odds 2       & 0.017 & 0.097 & 0.079 \\
+Accuracy Equality 1    & 0.170 & 0.082 & 0.088 \\
+Accuracy Equality 2    & 0.169 & 0.027 & 0.141 \\
 \bottomrule
@@
 
-There was also an increase of error on some sufficiency measure values.
-The sum of their differences is 0.189 and the average of their ratios is 0.489.
-However, this comparison may be skewed because one of the fairness measures in the original data was calculated to be zero, thus making the average ratio seem lower than otherwise.
+There was also an increase of error on some sufficiency measure values. The average of their differences is 0.031.
 
 \begin{table}[h]
-\caption{Fairness measures experiment results of the COMPAS dataset. Sum of differences is 0.189. Average of ratios is 0.489.}
+\caption{Fairness measures experiment results of the COMPAS dataset. Average of differences is 0.031.}
 \label{tab:diabetes_score}
-\begin{tabular}{ccccc}
+\begin{tabular}{cccc}
 \toprule
-\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Diff} & \textbf{Ratio} \\
+\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} \\
 \midrule
-Demographic Parity  & 0.013 & 0.015 & 0.002 & 0.867 \\
-Accuracy Eqaulity   & 0.007 & 0.009 & 0.002 & 0.782 \\
-Equalized Odds 1    & 0.000 & 0.003 & 0.003 & 0.000 \\
-Equalized Odds 2    & 0.008 & 0.106 & 0.097 & 0.081 \\
-Accuracy Equality 1 & 0.013 & 0.097 & 0.084 & 0.136 \\
-Accuracy Equality 2 & 0.021 & 0.020 & 0.001 & 1.068 \\
+Demographic Parity  & 0.013 & 0.015 & 0.002 \\
+Accuracy Eqaulity   & 0.007 & 0.009 & 0.002 \\
+Equalized Odds 1    & 0.000 & 0.003 & 0.003 \\
+Equalized Odds 2    & 0.008 & 0.106 & 0.097 \\
+Accuracy Equality 1 & 0.013 & 0.097 & 0.084 \\
+Accuracy Equality 2 & 0.021 & 0.020 & 0.001 \\
 \bottomrule
@@
 \end{table}
-
-TODO: only compare diff. remove ratios. use avg of diff.
 

### 2024-12-01 paper/paper.tex
some progress

@@
 
-TODO: mrf definition
+Let $\set{X_i}$ be a set of discrete random variables indexed by a graph $G = (V,E)$, where $V$ represents the random variables $X_i$s and $E$ represents dependencies between these random variables.
+A \emph{Markov random field} is a probability distribution over $X_i$s, such that each random variable $X_i$, given its neighborhood in $G$, is conditionally independent of all other variables.
+Since edges represent dependencies, cliques in a Markov random field represent groups of variables that are all mutually dependent.
+As a machine learning model, there has been much development in the fitting and inference of Markov random fields\cite{murphy2023probabilistic}.
 
@@
 
-For fairness measures\cite{yuan2024ensuring,pessach2022review}, let $Y$ to denote the ground truth of an outcome, let $\hat{Y}$ to denote the predicated result of an outcome, let $S$ denote the protected attribute, and let $\epsilon$ denote some threshold.
+For fairness measures\cite{yuan2024ensuring,pessach2022review}, let $Y$ denote the ground truth of an outcome, let $\hat{Y}$ denote the predicated result of an outcome, let $S$ denote the protected attribute, and let $\epsilon$ denote some threshold.
 For non-binary prediction, such as a score, we use $\hat{V}$.
@@
 We consider in this work various fairness measures listed in Table~\ref{tab:measures}.
-
-% \begin{definition}[Independence\cite{barocas2023fairness}]\label{def:independence}
-% $(S, \hat{Y})$ satisfy independence if and only if $S \bot \hat{Y}$; that is
-% \[
-% P[\hat{Y} = 1 | S = 1] = P[\hat{Y} = 1 | S \neq 1]
-% \]
-% A relaxation of independence on a threshold is
-% \[
-% \abs{P[\hat{Y} = 1 | S = 1] - P[\hat{Y} = 1 | S \neq 1]} \leq \epsilon
-% \]
-% \end{definition}
-
-% \begin{definition}[Separation\cite{barocas2023fairness}]\label{def:separation}
-% $(S, Y, \hat{Y})$ satisfy separation if and only if $S \bot \hat{Y} | Y$; that is
-% \begin{align*}
-% P[\hat{Y} = 1 | S = 1, Y = 1] & = P[\hat{Y} = 1 | S \neq 1, Y = 1] \\
-% P[\hat{Y} = 1 | S = 1, Y = 0] & = P[\hat{Y} = 1 | S \neq 1, Y = 0]
-% \end{align*}
-% A relaxation of independence on a threshold is
-% \begin{align*}
-% \abs{P[\hat{Y} = 1 | S = 1, Y = 1] - P[\hat{Y} = 1 | S \neq 1, Y = 1]} & \leq \epsilon \\
-% \abs{P[\hat{Y} = 1 | S = 1, Y = 0] - P[\hat{Y} = 1 | S \neq 1, Y = 0]} & \leq \epsilon
-% \end{align*}
-% \end{definition}
-
-% \begin{definition}[Sufficiency\cite{barocas2023fairness}]\label{def:separation}
-% $(S, Y, \hat{Y})$ satisfy sufficiency if and only if $S \bot Y | \hat{Y}$; that is
-% \begin{align*}
-% P[Y = 1 | S = 1, \hat{Y} = 1] & = P[Y = 1 | S \neq 1, \hat{Y} = 1] \\
-% P[Y = 1 | S = 1, \hat{Y} = 0] & = P[Y = 1 | S \neq 1, \hat{Y} = 0]
-% \end{align*}
-% A relaxation of independence on a threshold is
-% \begin{align*}
-% \abs{P[Y = 1 | S = 1, \hat{Y} = 1] - P[Y = 1 | S \neq 1, \hat{Y} = 1]} & \leq \epsilon \\
-% \abs{P[Y = 1 | S = 1, \hat{Y} = 0] - P[Y = 1 | S \neq 1, \hat{Y} = 0]} & \leq \epsilon
-% \end{align*}
-% \end{definition}
-
-% The $p$-norm is denoted by $L_p$ and the $p$-norm of a vector $x$ is denoted by $\Vert x \Vert_p$.
-
-% The normal distribution or Gaussian distribution with mean $\mu$ and standard deviation $\sigma$ is denoted by $\mathcal{N}(\mu, \sigma^2)$.
 
@@
 Underneath the hood, the tool employs a Markov random field.
-The select step corresponds to marking cliques in a Markov random field, and the generate step corresponds to sampling from the fitted Markov random field.
+The select step corresponds to marking cliques in a Markov random field, and the generate step corresponds to inference from the fitted Markov random field.
 

### 2024-12-01 paper/paper.tex
security vs privacy

@@
 In the framework of our previous work\cite{yuan2024ensuring}, after obtaining real data from the data provider, the 3rd party auditor holds onto the real data for performing fairness audits, and it supposedly retains it indefinitely for the possibility of any future audits.
+However, this practice raises both security and privacy concerns.
 
-However, this practice introduces security concerns. It creates a vulnerability to data security threats. A breach at the auditor's end could result in compromises of individuals' privacy.
+For security, it creates a point of vulnerability of unauthorized access, and the auditor is now a target of data security attacks.
+The auditor may not have the necessary resources to defend against these threats.
+A breach at the auditor's end could result in compromises of individuals' sensitive information.
 
-TODO:
-security => unauthorized access. bulwark database
-privacy => authorized access, no info leak
+As for privacy, on the other hand, it introduces risks of information leakage.
+Storage of real data may inadvertently reveal sensitive information by data inference attacks.
+Indefinite retention exacerbates this issue because the longer the data is stored, the higher the chance of unwanted information disclosure.
 
-Moreover, the storage of the datasets also raises privacy concerns.
-Holding large amounts of sensitive data for an extended period opens the door to the risk of misuse.
-The auditor may misuse the data for unauthorized purposes.
-
-Thus, we introduce a new framework where the auditor generates synthetic data based on real data upon retrieval of the real data, and then holds onto the synthetic data and discards the real data, preventing further privacy breaches.
-The third-party thus retains the ability to audit all incoming future models as needed.
+Thus, we introduce a new framework where the auditor generates synthetic data based on real data upon retrieval of the real data, and then holds onto the synthetic data and discards the real data, preventing all further data breaches.
+The third-party retains the ability to audit all incoming future models as needed.
 

### 2024-12-01 paper/paper.tex
reorg

@@
 
-After synthesizing datasets, we used the fairness checker from \cite{yuan2024ensuring} to compute their fairness measures.
+After synthesizing the dataset, we used the fairness checker from \cite{yuan2024ensuring} to compute the fairness measures of any incoming AI model.
+
+The fairness checker is an open-sourced public domain Python package that computes various fairness measures, such as those mentioned in Table~\ref{measures}.
+
+The checker is designed to be user-friendly and agnostic to the underlying AI model. It is also designed to be easily extensible to accommodate new fairness measures.
+
+The checker simply iterates through the given database $\db$ and computes the results based on some given predicates on the rows $r_i$s, and finally outputs the fairness measure values.
+
+Protected groups $S$, predicted outcomes $\hat{Y}$, and ground truths $Y$ are all formulated as these predicates.
+These are straightforward logical boolean expressions.
+Specifically, they are given as Python functions that output boolean values.
+
+For example, if the sensitive attribute is sex and the protected group is female, the protected group predicate would be $S := r_i(\text{``sex''}) = \text{``Female''}$.
+This can be easily implemented in Python as a comparison function.
+
+The interpretation of the resulting fairness measure values is dependent on the third-party auditors.
+The auditors may have different thresholds $\epsilon$ for different fairness measures or different AI models.
+
+\section{Experiments}
+
 To test the viability of our method, we compare the metrics computed from the synthetic dataset against those of the original dataset.
 We used various datasets with fairness concerns mentioned in \cite{pessach2022review}.
+
+We looked at several publicly available datasets, such as adult\cite{adult_2,Kaggle_Adult_Census_Income}, COMPAS\cite{larson2016propublica,Kaggle_COMPAS_Dataset}, and diabetes\cite{diabetes_34,Kaggle_Diabetes_Prediction}.
+The adult dataset comes from the 1994 census in the United States and contains about 30000 individuals.
+The COMPAS dataset comes from an investigative report by ProPublica of the COMPAS criminal recidivism assessment system and contains about 7000 individuals.
+The diabetes dataset comes from the hospital readmission data published in the 1994 AI in Medicine journal and contains about 100000 individuals.
 
@@
 
-TODO: section experiment vs Methodology. move results to experiment
-
-Next, several AI models are extracted from various real life authors from Kaggle.
+Next, several AI models are extracted from various real-life authors from Kaggle.
 They are finetuned to perform well on the original dataset.
@@
 The average of the differences serves as a summary of the analysis.
-
-\section{Experiments}
-
-We looked at several publicly available datasets, such as adult\cite{adult_2,Kaggle_Adult_Census_Income}, COMPAS\cite{larson2016propublica,Kaggle_COMPAS_Dataset}, and diabetes\cite{diabetes_34,Kaggle_Diabetes_Prediction}.
-The adult dataset comes from the 1994 census in the United States and contains about 30000 individuals.
-The COMPAS dataset comes from an investigative report by ProPublica of the COMPAS criminal recidivism assessment system and contains about 7000 individuals.
-The diabetes dataset comes from the hospital readmission data published in the 1994 AI in Medicine journal and contains about 100000 individuals.
 

### 2024-12-01 paper/paper.tex
Grouped figs togther

@@
 \section{Methodology}
+\label{sec:method}
 
@@
 The dataset is first processed so it can be fed into the synthetic data generator.
-Some marginals are selected as described in the previous section, and the synthetic data generator model is fitted to the original data according to the marginals.
+Some marginals are selected as described in the Section~\ref{sec:method}, and the synthetic data generator model is fitted to the original data according to the marginals.
 Then the generator is run multiple times to obtain multiple sets of synthetic data.
@@
 
+% \begin{figure}[h]
+%   \centering
+%   \includegraphics[width=\linewidth]{adult_mst}
+%   \caption{Markov random field for marginals of the adult dataset.}
+%   \label{fig:adult_mst}
+%   \Description{Markov random field for marginals of the adult dataset.}
+% \end{figure}
+
+% \begin{figure}[h]
+%   \centering
+%   \includegraphics[width=\linewidth]{compas_mst}
+%   \caption{Markov random field for marginals of the COMPAS dataset.}
+%   \label{fig:compas_mst}
+%   \Description{Markov random field for marginals of the COMPAS dataset.}
+% \end{figure}
+
+% \begin{figure}[h]
+%   \centering
+%   \includegraphics[width=\linewidth]{diabetes_mst}
+%   \caption{Markov random field for marginals of the diabetes dataset.}
+%   \label{fig:diabetes_mst}
+%   \Description{Markov random field for marginals of the COMPAS dataset.}
+% \end{figure}
+
+\begin{figure}
+  \centering
+  \begin{subfigure}[b]{0.3\textwidth}
+      \centering
+      \includegraphics[width=\textwidth]{adult_mst}
+      \caption{Markov random field for marginals of the adult dataset.}
+      \label{fig:adult_mst}
+      \Description{Markov random field for marginals of the adult dataset.}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[b]{0.3\textwidth}
+      \centering
+      \includegraphics[width=\textwidth]{compas_mst}
+      \caption{Markov random field for marginals of the COMPAS dataset.}
+      \label{fig:compas_mst}
+      \Description{Markov random field for marginals of the COMPAS dataset.}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[b]{0.3\textwidth}
+      \centering
+      \includegraphics[width=\textwidth]{diabetes_mst}
+      \caption{Markov random field for marginals of the diabetes dataset.}
+      \label{fig:diabetes_mst}
+      \Description{Markov random field for marginals of the COMPAS dataset.}
+  \end{subfigure}
+      \caption{Markov random field for marginals of the experimented datasets.}
+      \label{fig:msts}
+\end{figure}
+
 \subsection{Adult Income Dataset}
@@
 Marginals based on this graph are then passed to the synthetic data generator for model fitting.
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=\linewidth]{adult_mst}
-\caption{Markov random field for marginals of the adult dataset.}
-\label{fig:adult_mst}
-\Description{Markov random field for marginals of the adult dataset.}
-\end{figure}
 
@@
 
-\begin{figure}[h]
-\centering
-\includegraphics[width=\linewidth]{compas_mst}
-\caption{Markov random field for marginals of the COMPAS dataset.}
-\label{fig:compas_mst}
-\Description{Markov random field for marginals of the COMPAS dataset.}
-\end{figure}
-
 We ran the same workflow as adult dataset for the COMPAS dataset. The comparison results are shown in Table~\ref{tab:compas_score}.
@@
 The same process is conducted to fit the synthetic data generator model.
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=\linewidth]{diabetes_mst}
-\caption{Markov random field for marginals of the diabetes dataset.}
-\label{fig:diabetes_mst}
-\Description{Markov random field for marginals of the COMPAS dataset.}
-\end{figure}
 

### 2024-12-01 paper/paper.tex
subtable will overflow
some progress

@@
 \end{subtable}
-\hspace{0.05\linewidth}
 \begin{subtable}[t]{0.45\linewidth}
@@
 
+% \begin{table}[h]
+% \caption{Example marginals.}
+% \label{tab:marginal-example}
+% \centering
+% \begin{subtable}[t]{0.3\linewidth}
+%   \caption{Fairness measures experiment results of the adult dataset. Average of differences is 0.0431.}
+%   \label{tab:adult_score}
+%   \begin{tabular}{ccccc}
+%   \toprule
+%   \textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} \\
+%   \midrule
+%   Demographic Parity  & 0.172 & 0.104 & 0.067 \\
+%   Accuracy Eqaulity   & 0.047 & 0.117 & 0.069 \\
+%   Equalized Odds 1    & 0.057 & 0.079 & 0.021 \\
+%   Equalized Odds 2    & 0.166 & 0.122 & 0.044 \\
+%   Accuracy Equality 1 & 0.100 & 0.132 & 0.031 \\
+%   Accuracy Equality 2 & 0.119 & 0.146 & 0.027 \\
+%   \bottomrule
+%   \end{tabular}
+% \end{subtable}
+% \begin{subtable}[t]{0.3\linewidth}
+%   \centering
+%   \caption{Fairness measures experiment results of the COMPAS dataset. Average of differences is 0.031.}
+%   \label{tab:diabetes_score}
+%   \begin{tabular}{cccc}
+%   \toprule
+%   \textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} \\
+%   \midrule
+%   Demographic Parity  & 0.013 & 0.015 & 0.002 \\
+%   Accuracy Eqaulity   & 0.007 & 0.009 & 0.002 \\
+%   Equalized Odds 1    & 0.000 & 0.003 & 0.003 \\
+%   Equalized Odds 2    & 0.008 & 0.106 & 0.097 \\
+%   Accuracy Equality 1 & 0.013 & 0.097 & 0.084 \\
+%   Accuracy Equality 2 & 0.021 & 0.020 & 0.001 \\
+%   \bottomrule
+%   \end{tabular}
+% \end{subtable}
+% \end{table}
+
 \subsection{Adult Income Dataset}
@@
 \begin{table}[h]
-\caption{Fairness measures experiment results of the COMPAS dataset. Average of differences is 0.031.}
+\caption{Fairness measures experiment results of the diabetes dataset. Average of differences is 0.031.}
 \label{tab:diabetes_score}
@@
 
+Our experiments showed that synthetic data generally preserves the fairness properties with a reasonable degree of accuracy.
+The average of the differences between the fairness measure values of the original and synthetic datasets is below 0.1 for all datasets.
+This indicates that synthetic data is a good approximation of the original data in terms of fairness.
+
+In particular, for the adult dataset, the average difference was 0.0431, suggesting a close match between the synthetic and the original data in terms of fairness measures.
+For the diabetes dataset, the average difference was 0.031, which is even lower.
+Even in the case of the COMPAS dataset, which had a higher value, it was still within an acceptable range at 0.069.
+
+This demonstrated that synthetic data can accurately reflect the fairness properties of the original data.
+Therefore, fairness analyses performed on synthetic data will yield results consistent with those on the original data.
+
 \subsection{Impossibility}
+
+Let the standalone symbols denote the case of being equal to one and the overlined symbols denote the case of being equal to zero.
+For example, $S$ denotes the case of $S = 1$ and $\overline{S}$ denotes the case of $S = 0$.
+
+independence
+\[
+P[\hat{Y} | S] - P[\hat{Y} | \overline{S}]
+= \frac{P[\hat{Y} \cap S]}{P[\overline{S}]} - \frac{P[\hat{Y} \cap \overline{S}]}{P[\overline{S}]}
+\]
+
+separation
+\[
+P[\hat{Y} | S, Y] - P[\hat{Y} | \overline{S}, Y]
+= \frac{P[\hat{Y} \cap S \cap Y]}{P[\overline{S} \cap Y]} - \frac{P[\hat{Y} \cap \overline{S} \cap Y]}{P[\overline{S} \cap Y]}
+\]
+
+sufficiency
+\[
+P[Y | S, \hat{Y}] - P[Y | \overline{S}, \hat{Y}]
+= \frac{P[Y \cap S \cap \hat{Y}]}{P[\overline{S} \cap \hat{Y}]} - \frac{P[Y \cap \overline{S} \cap \hat{Y}]}{P[\overline{S} \cap \hat{Y}]}
+\]
 

### 2024-12-01 paper/paper.tex
wrong
impossibility

@@
 
-There was also an increase of error on some sufficiency measure values. The average of their differences is 0.031.
+The differences are all pretty low, no more than $0.01$ this time, across all measures, except for one separation measure and one sufficiency measure. The average of their differences is 0.031.
 
@@
 
-Let the standalone symbols denote the case of being equal to one and the overlined symbols denote the case of being equal to zero.
-For example, $S$ denotes the case of $S = 1$ and $\overline{S}$ denotes the case of $S = 0$.
+The experiments also revealed some limitations of this approach.
+In particular, the sufficiency measure showed higher errors compared to other measures.
+For example, in the COMPAS dataset, the sufficiency measure had an error difference as high as 0.141, while other measures had errors below 0.1.
 
-independence
-\[
-P[\hat{Y} | S] - P[\hat{Y} | \overline{S}]
-= \frac{P[\hat{Y} \cap S]}{P[\overline{S}]} - \frac{P[\hat{Y} \cap \overline{S}]}{P[\overline{S}]}
-\]
+By close examination of our scenario, we can observe the following: of the three variables, $(\hat{Y},Y,S)$, two of them, namely $(Y,S)$, are both readily available in the original data.
+In contrast, $\hat{Y}$ is only available in the output of the given AI model, which cannot be captured by the synthetic data at the time of generation.
 
-separation
-\[
-P[\hat{Y} | S, Y] - P[\hat{Y} | \overline{S}, Y]
-= \frac{P[\hat{Y} \cap S \cap Y]}{P[\overline{S} \cap Y]} - \frac{P[\hat{Y} \cap \overline{S} \cap Y]}{P[\overline{S} \cap Y]}
-\]
+Referring back to the definition of the fairness measures, we can see the following: separation is concerned with the form $P[\hat{Y} | S, Y] = \frac{P[\hat{Y} \cap S \cap Y]}{P[{S} \cap Y]}$, and sufficiency is concerned with the form $P[Y | S, \hat{Y}] = \frac{P[Y \cap S \cap \hat{Y}]}{P[{S} \cap \hat{Y}]}$.
 
-sufficiency
-\[
-P[Y | S, \hat{Y}] - P[Y | \overline{S}, \hat{Y}]
-= \frac{P[Y \cap S \cap \hat{Y}]}{P[\overline{S} \cap \hat{Y}]} - \frac{P[Y \cap \overline{S} \cap \hat{Y}]}{P[\overline{S} \cap \hat{Y}]}
-\]
+This explains why sufficiency measures could have higher errors compared to separation because synthetic data have less information about them.
+While only one variable is missing in the numerator for separation, one more variable is missing in the denominator for sufficiency.
+
+Therefore, it is harder to approximate sufficiency measures on synthetic data.
+This is a fundamental limitation of this approach, and it is important to be aware of this when interpreting the results of fairness analyses.
+
+% independence
+% \[
+% P[\hat{Y} | S] - P[\hat{Y} | \overline{S}]
+% = \frac{P[\hat{Y} \cap S]}{P[{S}]} - \frac{P[\hat{Y} \cap \overline{S}]}{P[\overline{S}]}
+% \]
+
+% separation
+% \[
+% P[\hat{Y} | S, Y] - P[\hat{Y} | \overline{S}, Y]
+% = \frac{P[\hat{Y} \cap S \cap Y]}{P[{S} \cap Y]} - \frac{P[\hat{Y} \cap \overline{S} \cap Y]}{P[\overline{S} \cap Y]}
+% \]
+
+% sufficiency
+% \[
+% P[Y | S, \hat{Y}] - P[Y | \overline{S}, \hat{Y}]
+% = \frac{P[Y \cap S \cap \hat{Y}]}{P[{S} \cap \hat{Y}]} - \frac{P[Y \cap \overline{S} \cap \hat{Y}]}{P[\overline{S} \cap \hat{Y}]}
+% \]
 

### 2024-12-01 paper/paper.tex
concepts

@@
 % %% Please copy and paste the code instead of the example below.
+\begin{CCSXML}
+  <ccs2012>
+     <concept>
+         <concept_id>10002944.10011123.10011124</concept_id>
+         <concept_desc>General and reference~Metrics</concept_desc>
+         <concept_significance>500</concept_significance>
+         </concept>
+     <concept>
+         <concept_id>10002978.10003029.10011703</concept_id>
+         <concept_desc>Security and privacy~Usability in security and privacy</concept_desc>
+         <concept_significance>500</concept_significance>
+         </concept>
+     <concept>
+         <concept_id>10002951.10003227.10003351</concept_id>
+         <concept_desc>Information systems~Data mining</concept_desc>
+         <concept_significance>300</concept_significance>
+         </concept>
+     <concept>
+         <concept_id>10010147.10010257</concept_id>
+         <concept_desc>Computing methodologies~Machine learning</concept_desc>
+         <concept_significance>300</concept_significance>
+         </concept>
+     <concept>
+         <concept_id>10010147.10010178</concept_id>
+         <concept_desc>Computing methodologies~Artificial intelligence</concept_desc>
+         <concept_significance>300</concept_significance>
+         </concept>
+     <concept>
+         <concept_id>10002978.10002991.10002995</concept_id>
+         <concept_desc>Security and privacy~Privacy-preserving protocols</concept_desc>
+         <concept_significance>300</concept_significance>
+         </concept>
+     <concept>
+         <concept_id>10002951.10003227</concept_id>
+         <concept_desc>Information systems~Information systems applications</concept_desc>
+         <concept_significance>300</concept_significance>
+         </concept>
+     <concept>
+         <concept_id>10002950.10003648.10003688.10003690</concept_id>
+         <concept_desc>Mathematics of computing~Contingency table analysis</concept_desc>
+         <concept_significance>300</concept_significance>
+         </concept>
+   </ccs2012>
+\end{CCSXML}
+
+\ccsdesc[500]{General and reference~Metrics}
+\ccsdesc[500]{Security and privacy~Usability in security and privacy}
+\ccsdesc[300]{Information systems~Data mining}
+\ccsdesc[300]{Computing methodologies~Machine learning}
+\ccsdesc[300]{Computing methodologies~Artificial intelligence}
+\ccsdesc[300]{Security and privacy~Privacy-preserving protocols}
+\ccsdesc[300]{Information systems~Information systems applications}
+\ccsdesc[300]{Mathematics of computing~Contingency table analysis}
 % %%

### 2024-12-01 paper/paper.tex
alot of progress

@@
 
-\clearpage
+Fairness in machine learning has become a crucial area of research\cite{barocas2023fairness}.
+Various fairness measures have been proposed to quantify the fairness of AI models\cite{pessach2022review,corbett2017algorithmic,vzliobaite2017measuring,hardt2016equality,corbett2017algorithmic,berk2021fairness,chouldechova2017fair,kleinberg2016inherent}.
+
+The auditing of AI models is an important step in ensuring that these models are fair\cite{ferrara2023fairness}.
+Different tools have been developed to check the fairness of AI models\cite{yuan2024ensuring,saleiro2018aequitas,bellamy2019ai,bird2020fairlearn}.
+
+% differential privacy
+
+Differential Privacy has risen to become the standard of privacy protection in many data analyses\cite{jiang2021applications}.
+It offers a formal framework for quantifying privacy guarantees when releasing information derived from sensitive data\cite{dwork2006calibrating,dwork2014algorithmic}.
+
+Different flavors of Differential Privacy have been proposed over the years\cite{desfontaines2019sok}, such as Gaussian Differential Privacy\cite{dong2022gaussian}, Pufferfish Differential Privacy\cite{kifer2012rigorous}, Bayesian Differential Privacy\cite{triastcyn2020bayesian}, and R\'enyi Differential Privacy\cite{mironov2017renyi}.
+
+% synthetic data
+
+The generation of synthetic data under differential privacy constraints allows for data sharing without compromising privacy\cite{tao2021benchmarking}.
+There have been several techniques developed for Differentially Private synthetic data generation\cite{rosenblatt2020differentially,fan2020relational,bowen2019comparative,bowen2020comparative,arnold2020really,xu2019modeling} in recent years.
+
+While useful, there are some ethical concerns with the generation of synthetic data ...
+
+% TODO: cite
 
@@
 For non-binary prediction, such as a score, we use $\hat{V}$.
+
+% TODO: should we exclude nonbinary prediction?
 
@@
 Let $x$ be a row and $x_C$ denote the restriction of $x$ to $C$.
-A \emph{marginal}\cite{barak2007privacy,mckenna2021winning} of $C$ on database $\db$ is a lookup table $\mu_{\db} : \Omega_C \implies \mathbb{N}_0$ such that each entry is a count $\mu_{\db}(t) = \Sigma_{x \in \db} \delta_{t,{x_C}}$ where $\delta$ is the Kronecker function; that is, it is the vector of the counts of each possible domain element.
+A \emph{marginal}\cite{barak2007privacy,mckenna2021winning} of $C$ on database $\db$ is a lookup table $\mu_{\db} : \Omega_C \implies \mathbb{N}_0$ such that each entry is a count $\mu_{\db}(t) = \Sigma_{x \in \db} \delta_{t,{x_C}}$ where $\delta$ is the Kronecker function; that is, it is a table of the counts of each possible combination of domain elements.
 We call marginals of $|C| = n$ attributes $n$-way marginals.
 
-The task of differentially private synthetic data\cite{Ullman2022,McKenna2022,NIST_Differentially_Private_Synthetic_Data,YouTube_Differentially_Private_Synthetic_Data} is, given a database $\db$, adding some noise to marginals of $\db$ such that it satisfies some differential privacy guarantees and outputting another database $\db'$, such that the $L^1$-norm errors between marginals of $\db$ and $\db'$ is small; that is, their marginals $\mu_{\db},\mu_{\db'}$ are similar.
+The task of differentially private synthetic data\cite{Ullman2022,McKenna2022,NIST_Differentially_Private_Synthetic_Data,YouTube_Differentially_Private_Synthetic_Data} is, given a database $\db$, adding some noise to marginals of $\db$ such that it satisfies some Differential Privacy guarantees and outputting another database $\db'$, such that the $L^1$-norm errors between marginals of $\db$ and $\db'$ is small; that is, their marginals $\mu_{\db},\mu_{\db'}$ are similar.
 
@@
 The synthesis framework is three-fold, namely, select-measure-generate\cite{McKenna2022}.
-We first select the important marginals to preserve, measure them by adding differentially private noise, and then generate synthetic data.
+We first select the important marginals to preserve, measure them by adding Differential Privacy noise, and then generate synthetic data.
 
@@
 
-The fairness checker is an open-sourced public domain Python package that computes various fairness measures, such as those mentioned in Table~\ref{measures}.
+The fairness checker is an open-sourced public domain Python package that computes various fairness measures, such as those mentioned in Table~\ref{tab:measures}.
 

### 2024-12-02 paper/paper.tex
some progress

@@
 Fairness in machine learning has become a crucial area of research\cite{barocas2023fairness}.
-Various fairness measures have been proposed to quantify the fairness of AI models\cite{pessach2022review,corbett2017algorithmic,vzliobaite2017measuring,hardt2016equality,corbett2017algorithmic,berk2021fairness,chouldechova2017fair,kleinberg2016inherent}.
+Various fairness measures have been proposed to quantify\cite{yeh2024analyzing} the fairness of AI models\cite{pessach2022review,corbett2017algorithmic,vzliobaite2017measuring,hardt2016equality,corbett2017algorithmic,berk2021fairness,chouldechova2017fair,kleinberg2016inherent}.
 
@@
 
-The generation of synthetic data under differential privacy constraints allows for data sharing without compromising privacy\cite{tao2021benchmarking}.
+The generation of synthetic data\cite{raghunathan2021synthetic,lu2023machine} under Differential Privacy constraints allows for data sharing without compromising privacy\cite{tao2021benchmarking}.
 There have been several techniques developed for Differentially Private synthetic data generation\cite{rosenblatt2020differentially,fan2020relational,bowen2019comparative,bowen2020comparative,arnold2020really,xu2019modeling} in recent years.
 
-While useful, there are some ethical concerns with the generation of synthetic data ...
+There are also works that aim to introduce bias to synthetic data\cite{jiang2024synthetic,baumann2023bias}.
 
-% TODO: cite
+While helpful, there are some technical limitations\cite{stadler2022synthetic,cheng2021can,ganev2022robin,wyllie2024fairness} and ethical concerns\cite{whitney2024real} with the use of synthetic data.
 
@@
 
-Let $\prod_i x_i$ denotes the Cartesian product of $x_i$s.
+Let $\prod_i x_i$ denote the Cartesian product of $x_i$s.
 
@@
 
-The task of differentially private synthetic data\cite{Ullman2022,McKenna2022,NIST_Differentially_Private_Synthetic_Data,YouTube_Differentially_Private_Synthetic_Data} is, given a database $\db$, adding some noise to marginals of $\db$ such that it satisfies some Differential Privacy guarantees and outputting another database $\db'$, such that the $L^1$-norm errors between marginals of $\db$ and $\db'$ is small; that is, their marginals $\mu_{\db},\mu_{\db'}$ are similar.
+The task of Differentially Private synthetic data\cite{Ullman2022,McKenna2022,NIST_Differentially_Private_Synthetic_Data,YouTube_Differentially_Private_Synthetic_Data} is, given a database $\db$, adding some noise to marginals of $\db$ such that it satisfies some Differential Privacy guarantees and outputting another database $\db'$, such that the $L^1$-norm errors between marginals of $\db$ and $\db'$ is small; that is, their marginals $\mu_{\db},\mu_{\db'}$ are similar.
 

### 2024-12-02 paper/paper.tex
minor changes

@@
 
-The auditing of AI models is an important step in ensuring that these models are fair\cite{ferrara2023fairness}.
+Auditing of AI models is an important step in ensuring that these models are fair\cite{ferrara2023fairness}.
 Different tools have been developed to check the fairness of AI models\cite{yuan2024ensuring,saleiro2018aequitas,bellamy2019ai,bird2020fairlearn}.
@@
 Storage of real data may inadvertently reveal sensitive information by data inference attacks.
-Indefinite retention exacerbates this issue because the longer the data is stored, the higher the chance of unwanted information disclosure.
+Indefinite retention also exacerbates this issue because the longer the data is stored, the higher the chance of unwanted information disclosure.
 
@@
 
-The synthesis framework is three-fold, namely, select-measure-generate\cite{McKenna2022}.
+The synthesis framework is three-fold, namely, select-measure-generate\cite{McKenna2022,YouTube_Differentially_Private_Synthetic_Data}.
 We first select the important marginals to preserve, measure them by adding Differential Privacy noise, and then generate synthetic data.
@@
 
-To circumvent the complexity explosion, instead, \cite{McKenna_privatePGM,mckenna2021winning} devised a technique where the mutual information of all the database attribute pairs is calculated, and then a maximum spanning tree algorithm was run with edge weights being the mutual information to obtain a skeleton spanning-tree-shaped Markov random field.
+To circumvent the complexity explosion, instead, \cite{mckenna2021winning} devised a technique where the mutual information of all the database attribute pairs is calculated, and then a maximum spanning tree algorithm was run with edge weights being the mutual information to obtain a skeleton spanning-tree-shaped Markov random field.
 
-For the competition, \cite{McKenna_privatePGM,mckenna2021winning} further manually added certain cliques based on his investigation of the competition dataset.
+For the competition, \cite{mckenna2021winning} further manually added certain cliques based on his investigation of the competition dataset.
 For example, they manually added the clique (sex,city,income).
@@
 
+% TODO: mention model fit time?
+
 \subsection{Accuracy}

### 2024-12-03 paper/paper.tex
Added loans experiment
Added TODOs

@@
 
+TODO: add more connections to our work
+
 Fairness in machine learning has become a crucial area of research\cite{barocas2023fairness}.
@@
 
+TODO: some works aim to change properties of og data. we want to preserve. so we dont consider this case
+
 There are also works that aim to introduce bias to synthetic data\cite{jiang2024synthetic,baumann2023bias}.
@@
 
-A \emph{row} $r_i$ is a lookup table or dictionary.
+TODO: Let $r_i$ denote a \emph{row} $r_i$ is a function.
 A \emph{database} $\db = \set{r_1, r_2, ...}$ is a collection of rows.
@@
 Their \emph{joint Shannon entropy} is $\entropy{X,Y} := -\sum_{x \in \mathcal{X}} \sum_{y \in \mathcal{Y}} p(x, y) \text{log} p(x, y)$.
+
+TODO: cite elements of info theory
 
@@
 
+TODO: let Y be binary
+
 For fairness measures\cite{yuan2024ensuring,pessach2022review}, let $Y$ denote the ground truth of an outcome, let $\hat{Y}$ denote the predicated result of an outcome, let $S$ denote the protected attribute, and let $\epsilon$ denote some threshold.
 For non-binary prediction, such as a score, we use $\hat{V}$.
+
+TODO: mention in results we only tested binary predictions
 
@@
 
+TODO: N is multivariate normal distribution and sigma and identity function. I sub p
+
+TODO: Da needs to take distributions. change symbols. lowercase phi
+
 \begin{theorem}[RDP of the Gaussian Mechanism\cite{feldman2018privacy,mironov2017renyi}]
@@
 
-As for privacy, on the other hand, it introduces risks of information leakage.
-Storage of real data may inadvertently reveal sensitive information by data inference attacks.
+As for privacy, on the other hand, it introduces risks of information leakage. Releasings of real data may inadvertently reveal sensitive information by data inference attacks.
+
+TODO: ppl may infer info from auditors analyses Releasings. repeated queries
+
 Indefinite retention also exacerbates this issue because the longer the data is stored, the higher the chance of unwanted information disclosure.
@@
 Underneath the hood, the tool employs a Markov random field.
-The select step corresponds to marking cliques in a Markov random field, and the generate step corresponds to inference from the fitted Markov random field.
+The select step corresponds to marking cliques in a Markov random field, and the generate step corresponds to sampling by inference from the fitted Markov random field.
 
@@
 
+TODO: mst was obtained. delete the word algorithm
+
 For the competition, \cite{mckenna2021winning} further manually added certain cliques based on his investigation of the competition dataset.
@@
 As a rule of thumb, we have found setting the fraction to be $0.1$ to be effective.
+
+TODO: use latex algorithm. pseudo code
 
@@
 
-% TODO: mention model fit time?
+% TODO: mention model fit time? yes. do experiments!
 
-\subsection{Accuracy}
+TODO: \subsection{Positive Results}
 
@@
 
-\subsection{Impossibility}
+TODO: \subsection{Negative Results}
 
@@
 Referring back to the definition of the fairness measures, we can see the following: separation is concerned with the form $P[\hat{Y} | S, Y] = \frac{P[\hat{Y} \cap S \cap Y]}{P[{S} \cap Y]}$, and sufficiency is concerned with the form $P[Y | S, \hat{Y}] = \frac{P[Y \cap S \cap \hat{Y}]}{P[{S} \cap \hat{Y}]}$.
+
+TODO: expand all defs and count the nums of avail vars
 

### 2024-12-04 paper/paper.tex
major progress

@@
 
-TODO: Let $r_i$ denote a \emph{row} $r_i$ is a function.
-A \emph{database} $\db = \set{r_1, r_2, ...}$ is a collection of rows.
-The set of all databases is denoted $\dbs$.
-The attributes of a $\db$ is $\mathcal{A} = \set{A_1, A_2, ...}$.
-The domain of $A_i$ is $\Omega_i$.
+An \emph{attribute} is a symbol $A$.
+The set of all attributes is $\mathcal{A}$.
+An \emph{attribute value} is a symbol $a$.
+The set of all attribute values is $\Omega$.
+An \emph{attribute value space} is a function $\sigma : \mathcal{A} \implies 2^{\Omega}$
+specifying the set of valid values that attributes can take on.
+A \emph{row} with respect to $\sigma$
+is a function $r : \mathcal{A} \implies \Omega$
+where $r(A) \in \sigma(A)$.
+The set of all rows is $\mathcal{R}$.
+A \emph{database} is a tuple $\db =
+\tuple{
+    \mathcal{A}_{\db},
+    \Omega_{\db},
+    \sigma_{\db},
+    \mathcal{R}_{\db}
+}$
+where
+$\mathcal{A}_{\db} \subseteq \mathcal{A}$
+is the set of attributes in $\db$,
+$\Omega_{\db} \subseteq \Omega$
+is the set of attribute values in $\db$,
+$\sigma_{\db} : \mathcal{A}_{\db} \implies 2^{\Omega_{\db}}$
+is the function specifying the valid values that each attribute can take on in $\db$,
+and $\mathcal{R}_{\db} \subseteq \mathcal{R}$
+is the set of rows in $\db$
+with $r_\db : \mathcal{A}_\db \implies \Omega_\db$
+for all $r_\db \in \mathcal{R}_\db$
+and $r_\db(A) \in \sigma_\db(A)$
+for all $A \in \mathcal{A}_\db$.
+The set of all databases is $\dbs$.
 
@@
 
-TODO: cite elements of info theory
-
 Let $X,Y$ be discrete random variables.
@@
 It quantifies the level of dependence between $X$ and $Y$.
-By definition\cite{entropy_lecture_notes}, the joint entropy is greater than the marginal entropies $\entropy{X,Y} \geq \text{max}(\entropy{X},\entropy{Y})$.
+By definition\cite{427884}, the joint entropy is greater than or equal to the marginal entropies $\entropy{X,Y} \geq \text{max}(\entropy{X},\entropy{Y})$.
 Hence, we have an upper bound of mutual information $\mi{X}{Y} \leq \text{min}(\entropy{X}, \entropy{Y})$.
@@
 Since edges represent dependencies, cliques in a Markov random field represent groups of variables that are all mutually dependent.
-As a machine learning model, there has been much development in the fitting and inference of Markov random fields\cite{murphy2023probabilistic}.
+As a machine learning model, there has been much development in the fitting and inference of Markov random fields\cite{koller2009probabilistic,murphy2023probabilistic}.
 
@@
 
-TODO: let Y be binary
-
 For fairness measures\cite{yuan2024ensuring,pessach2022review}, let $Y$ denote the ground truth of an outcome, let $\hat{Y}$ denote the predicated result of an outcome, let $S$ denote the protected attribute, and let $\epsilon$ denote some threshold.
+$Y, \hat{Y}, S$ are binary.
 For non-binary prediction, such as a score, we use $\hat{V}$.
-
-TODO: mention in results we only tested binary predictions
-
-% TODO: should we exclude nonbinary prediction?
 
@@
 
-A \emph{randomized mechanism} is a randomized algorithm $M : \dbs \implies R$ that takes a database and, after introducing noise, outputs some results.
+A \emph{randomized mechanism} is a randomized algorithm $M : \dbs \implies \mathbb{R}^p$ that takes a database and, after introducing noise, outputs some results.
 
-Let $\db_1,\db_2$ be two databases. They are \emph{neighbors}, denoted $\db_1 \sim \db_2$, if they differ in exactly one row.
+Let $\db_1,\db_2$ be two databases.
+They are \emph{neighbors}, denoted $\db_1 \sim \db_2$, if $\abs{\mathcal{R}_{\db_1} \Delta \mathcal{R}_{\db_2}} \in \set{1,2}$ where $\Delta$ denotes symmetric difference; that is, either one database contains an extra row, or both databases have all but one row in common.
+In other words, they differ in exactly one row.
 
 \begin{definition}[Gaussian Mechanism\cite{dwork2014algorithmic}]\label{def:gm}
-Let $f : \dbs \implies \mathbb{R}^p$ be a function that takes a database and outputs a vector. The Gaussian Mechanism $M$ adds i.i.d. Gaussian noise with scale $\sigma$ to each of the $p$ outputs
+Let $f : \dbs \implies \mathbb{R}^p$ be a function.
+The Gaussian Mechanism $M$ adds independent and identically distributed Gaussian noise with mean $0$ and standard deviation $\sigma$ to each component of the $p$-dimensional vector output of $f(\db)$
 \[
-M(\db) = f(\db) + \mathcal{N}(0, \sigma^2 \mathbb{I})
+M(\db) = f(\db) + \mathcal{N}(0_p, \sigma^2 \mathbb{I}_p)
 \]
+where $\mathcal{N}$ is a multivariate normal distribution with mean vector $0_p$ and covariance matrix $\sigma^2 \mathbb{I}_p$ where $\mathbb{I}_p$ is the identity matrix.
 \end{definition}
@@
 \begin{definition}[R\'enyi Differential Privacy (RDP)]\label{def:rdp}
+Let $P_{\mathbf{X}}$ denote the probability distribution induced by the random vector $\mathbf{X}$.
 A randomized mechanism $M$ satisfies $(\alpha,\gamma)$-RDP for $\alpha \geq 1$ and $\gamma \geq 1$ if, for all databases $\db_1 \sim \db_2$, we have
 \[
-D_\alpha(M(\db_1) \Vert M(\db_2)) \leq \gamma
+D_\alpha(P_{M(\db_1)} \Vert P_{M(\db_2)}) \leq \gamma
 \]
-where $D_\alpha(P \Vert Q)$ is the R\'enyi divergence\cite{van2014renyi,van2010renyi,li2016renyi} of order $\alpha$ between discrete probability distributions $P$ and $Q$, defined on $\mathcal{X}$:
+where $D_\alpha(P_1 \Vert P_2)$ is the R\'enyi divergence\cite{van2014renyi,van2010renyi,li2016renyi} of order $\alpha$ between probability distributions $P_1,P_2$ over $x$:
 \[
-D_\alpha(P \Vert Q) := \frac{1}{\alpha - 1} \text{log} \sum_{x \in \mathcal{X}} {P(x)}^\alpha {Q(x)}^{1-\alpha}
+D_\alpha(P_1 \Vert P_2) := \frac{1}{\alpha - 1} \text{log} \int {P_1(x)}^\alpha {P_2(x)}^{1-\alpha} \text{d}x
 \]
 \end{definition}
-
-TODO: N is multivariate normal distribution and sigma and identity function. I sub p
-
-TODO: Da needs to take distributions. change symbols. lowercase phi
 
@@
 Let $x$ be a row and $x_C$ denote the restriction of $x$ to $C$.
-A \emph{marginal}\cite{barak2007privacy,mckenna2021winning} of $C$ on database $\db$ is a lookup table $\mu_{\db} : \Omega_C \implies \mathbb{N}_0$ such that each entry is a count $\mu_{\db}(t) = \Sigma_{x \in \db} \delta_{t,{x_C}}$ where $\delta$ is the Kronecker function; that is, it is a table of the counts of each possible combination of domain elements.
+A \emph{marginal}\cite{barak2007privacy,mckenna2021winning} of $C$ on database $\db$ is a function $\mu_{\db} : \Omega_C \implies \mathbb{N}_0$ such that $\mu_{\db}(t) = \Sigma_{x \in \mathcal{\db}} \delta_{t,{x_C}}$ where $\delta$ is the Kronecker function; that is, it is a lookup table of the counts of each possible combination of attribute values.
 We call marginals of $|C| = n$ attributes $n$-way marginals.
@@
 
-We employed the tools of the winner of the 2018 NIST Differential Privacy Synthetic Data Challenge competition\cite{NIST2018} by \cite{McKenna_privatePGM,mckenna2021winning,mckenna2019graphical} and the fairness checker tool from our previous research\cite{yuan2024ensuring}.
+We employed the tools of the winner of the 2018 NIST Differential Privacy Synthetic Data Challenge competition\cite{NIST2018} by \cite{McKenna_Private-PGM_2021,mckenna2021winning,mckenna2019graphical} and the fairness checker tool from our previous research\cite{yuan2024ensuring}.
 
@@
 
-For example, if the sensitive attribute is sex and the protected group is female, the protected group predicate would be $S := r_i(\text{``sex''}) = \text{``Female''}$.
+For example, if the sensitive attribute is sex and the protected group is female, the protected group predicate would be $S := r(sex) = Female$.
 This can be easily implemented in Python as a comparison function.
@@
 The diabetes dataset comes from the hospital readmission data published in the 1994 AI in Medicine journal and contains about 100000 individuals.
+Since these datasets all have binary outcomes, we did not consider the case of non-binary outcomes in the experiments.
 
@@
 
+% this experiment is complete
+
+With heuristic it is 27m33s. The fit time is 33s without heuristic.
+
+The average of their differences is $0.0787$. Without heuristic it is $0.0775$.
+
 The results showed an increase in error on the sufficiency measure values.
@@
 \begin{table}[h]
-\caption{Fairness measures experiment results of the COMPAS dataset. Average of differences is 0.069.}
+\caption{Fairness measures experiment results of the COMPAS dataset. Average of differences is 0.0787.}
 \label{tab:compas_score}
@@
 \midrule
-Demographic Parity     & 0.131 & 0.098 & 0.032 \\
-Accuracy Eqaulity      & 0.007 & 0.013 & 0.005 \\
-Equalized Odds 1       & 0.024 & 0.099 & 0.074 \\
-Equalized Odds 2       & 0.017 & 0.097 & 0.079 \\
-Accuracy Equality 1    & 0.170 & 0.082 & 0.088 \\
-Accuracy Equality 2    & 0.169 & 0.027 & 0.141 \\
+Demographic Parity  & 0.1310 & 0.0980 & 0.0330 \\
+Mean Difference     & 0.3282 & 0.2274 & 0.1007 \\
+Accuracy Eqaulity   & 0.0079 & 0.0129 & 0.0050 \\
+Equalized Odds 1    & 0.0249 & 0.0936 & 0.0687 \\
+Equalized Odds 2    & 0.0177 & 0.1016 & 0.0838 \\
+Accuracy Equality 1 & 0.1709 & 0.0505 & 0.1203 \\
+Accuracy Equality 2 & 0.1695 & 0.0303 & 0.1392 \\
 \bottomrule
@@
 
-The differences are all pretty low, no more than $0.01$ this time, across all measures, except for one separation measure and one sufficiency measure. The average of their differences is 0.031.
+% run this with 100 iter
+
+The fit time is 1m24s without heuristic. With heuristic it is 1m44s.
+
+The average of their differences is $0.0069$. Without heuristic it is $0.0083$.
+
+% The results showed that the synthetic data generally preserves the fairness properties of the original data.
+
+% The average of the differences between the fairness measure values of the original and synthetic datasets is below 0.1 for all datasets.
+The average of the differences is 0.0431 for the adult dataset, 0.069 for the COMPAS dataset, and 0.031 for the diabetes dataset.
 
 \begin{table}[h]
-\caption{Fairness measures experiment results of the diabetes dataset. Average of differences is 0.031.}
+\caption{Fairness measures experiment results of the diabetes dataset. Average of differences is 0.0069.}
 \label{tab:diabetes_score}
@@
 \midrule
-Demographic Parity  & 0.013 & 0.015 & 0.002 \\
-Accuracy Eqaulity   & 0.007 & 0.009 & 0.002 \\
-Equalized Odds 1    & 0.000 & 0.003 & 0.003 \\
-Equalized Odds 2    & 0.008 & 0.106 & 0.097 \\
-Accuracy Equality 1 & 0.013 & 0.097 & 0.084 \\
-Accuracy Equality 2 & 0.021 & 0.020 & 0.001 \\
+Demographic Parity  & 0.0135 & 0.0032 & 0.0102 \\
+Mean Difference     & 0.0035 & 0.0119 & 0.0083 \\
+Accuracy Eqaulity   & 0.0077 & 0.0009 & 0.0067 \\
+Equalized Odds 1    & 0.0000 & 0.0003 & 0.0003 \\
+Equalized Odds 2    & 0.0086 & 0.0104 & 0.0017 \\
+Accuracy Equality 1 & 0.0133 & 0.0095 & 0.0038 \\
+Accuracy Equality 2 & 0.0216 & 0.0039 & 0.0177 \\
 \bottomrule
@@
 
-TODO: \subsection{Positive Results}
+\subsection{Positive Results}
+
+%  TODO: rewrite this
 
@@
 
-In particular, for the adult dataset, the average difference was 0.0431, suggesting a close match between the synthetic and the original data in terms of fairness measures.
+For the adult dataset, the average difference was 0.0431, suggesting a close match between the synthetic and the original data in terms of fairness measures.
 For the diabetes dataset, the average difference was 0.031, which is even lower.
 Even in the case of the COMPAS dataset, which had a higher value, it was still within an acceptable range at 0.069.
+
+In particular, both the independence and separation measures showed low errors across all datasets, with the differences of all of them below 0.1.
+On the other hand, results of accuracy equality also showed low errors, with the differences of one of them as low as 0.005.
 
@@
 
-TODO: \subsection{Negative Results}
+\subsection{Negative Results}
+
+%  TODO: rewrite this
 

### 2024-12-04 paper/paper.tex
reference

@@
 For one, a random forest model is finetuned by searching hyperparameters settings\cite{Ipbyrne2023}.
-For another, a logistic regression model is finetuned by performing principal component analysis\cite{Prashant1112023}.
+Another random forest model is finetuned with over-sampling methods\cite{Jawat2024}.
+Also, a logistic regression model is finetuned by performing principal component analysis\cite{Prashant1112023}.
 
@@
 
+% this 100 experiment is not run yet
+
+With heuristic it is 924m15s. The fit time is 17m1s without heuristic.
+
+The average of their differences is $0.0787$. Without heuristic it is $0.0775$.
+
 We observed that across all examined fairness measures, their difference all fall below 0.1. The average of their differences is 0.0431, which we consider quite satisfactory.
@@
 Demographic Parity  & 0.1310 & 0.0980 & 0.0330 \\
-Mean Difference     & 0.3282 & 0.2274 & 0.1007 \\
 Accuracy Eqaulity   & 0.0079 & 0.0129 & 0.0050 \\
@@
 
-% run this with 100 iter
+% this is running with 100 iter
 

### 2024-12-04 paper/paper.tex
experimenting...

@@
 and $\mathcal{R}_{\db} \subseteq \mathcal{R}$
-is the set of rows in $\db$
+is the set of rows with respect to $\sigma_{\db}$ in $\db$
 with $r_\db : \mathcal{A}_\db \implies \Omega_\db$
@@
 
-As for privacy, on the other hand, it introduces risks of information leakage. Releasings of real data may inadvertently reveal sensitive information by data inference attacks.
-
-TODO: ppl may infer info from auditors analyses Releasings. repeated queries
-
-Indefinite retention also exacerbates this issue because the longer the data is stored, the higher the chance of unwanted information disclosure.
+As for privacy, on the other hand, it introduces risks of information leakage.
+Releasings of analyses on real data may inadvertently reveal sensitive information by data inference attacks.
+Attackers can exploit patterns in data outputs or combine outputs with external data to infer sensitive information.
 
@@
 
-% this 100 experiment is not run yet
+% this 100 experiment is running
 
-With heuristic it is 924m15s. The fit time is 17m1s without heuristic.
+The fit time is 17m1s without heuristic. With heuristic it is 924m15s.
 
@@
 
-With heuristic it is 27m33s. The fit time is 33s without heuristic.
+The fit time is 33s without heuristic. With heuristic it is 27m33s.
 
-The average of their differences is $0.0787$. Without heuristic it is $0.0775$.
+The average of their differences is $0.0750$. Without heuristic it is $0.0727$.
 
@@
 \begin{table}[h]
-\caption{Fairness measures experiment results of the COMPAS dataset. Average of differences is 0.0787.}
+\caption{Fairness measures experiment results of the COMPAS dataset. Average of differences is $0.0750$. Average of differences without heuristic is $0.0727$}
 \label{tab:compas_score}
-\begin{tabular}{cccc}
+\begin{tabular}{cccccc}
 \toprule
-\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} \\
+\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} & \textbf{Synthetic(No Heuristic)} & \textbf{Difference(No Heuristic)} \\
 \midrule
-Demographic Parity  & 0.1310 & 0.0980 & 0.0330 \\
-Accuracy Eqaulity   & 0.0079 & 0.0129 & 0.0050 \\
-Equalized Odds 1    & 0.0249 & 0.0936 & 0.0687 \\
-Equalized Odds 2    & 0.0177 & 0.1016 & 0.0838 \\
-Accuracy Equality 1 & 0.1709 & 0.0505 & 0.1203 \\
-Accuracy Equality 2 & 0.1695 & 0.0303 & 0.1392 \\
+Demographic Parity  & 0.1310 & 0.0980 & 0.0330 & 0.0809 & 0.0501 \\
+Accuracy Eqaulity   & 0.0079 & 0.0129 & 0.0050 & 0.0146 & 0.0067 \\
+Equalized Odds 1    & 0.0249 & 0.0936 & 0.0687 & 0.0802 & 0.0553 \\
+Equalized Odds 2    & 0.0177 & 0.1016 & 0.0838 & 0.0825 & 0.0648 \\
+Accuracy Equality 1 & 0.1709 & 0.0505 & 0.1203 & 0.0551 & 0.1157 \\
+Accuracy Equality 2 & 0.1695 & 0.0303 & 0.1392 & 0.0256 & 0.1439 \\
 \bottomrule
@@
 
-% this is running with 100 iter
+% this experiment is complete
 
@@
 
-The average of their differences is $0.0069$. Without heuristic it is $0.0083$.
+The average of their differences is $0.0067$. Without heuristic it is $0.0078$.
 
@@
 \begin{table}[h]
-\caption{Fairness measures experiment results of the diabetes dataset. Average of differences is 0.0069.}
+\caption{Fairness measures experiment results of the diabetes dataset. Average of differences is $0.0067$. Average of differences without heuristic is $0.0078$}
 \label{tab:diabetes_score}
-\begin{tabular}{cccc}
+\begin{tabular}{cccccc}
 \toprule
-\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} \\
+\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} & \textbf{Synthetic(No Heuristic)} & \textbf{Difference(No Heuristic)} \\
 \midrule
-Demographic Parity  & 0.0135 & 0.0032 & 0.0102 \\
-Mean Difference     & 0.0035 & 0.0119 & 0.0083 \\
-Accuracy Eqaulity   & 0.0077 & 0.0009 & 0.0067 \\
-Equalized Odds 1    & 0.0000 & 0.0003 & 0.0003 \\
-Equalized Odds 2    & 0.0086 & 0.0104 & 0.0017 \\
-Accuracy Equality 1 & 0.0133 & 0.0095 & 0.0038 \\
-Accuracy Equality 2 & 0.0216 & 0.0039 & 0.0177 \\
+Demographic Parity  & 0.0135 & 0.0038 & 0.0096 & 0.0015 & 0.0119 \\
+Accuracy Eqaulity   & 0.0077 & 0.0011 & 0.0065 & 0.0011 & 0.0065 \\
+Equalized Odds 1    & 0.0000 & 0.0006 & 0.0006 & 0.0010 & 0.0010 \\
+Equalized Odds 2    & 0.0086 & 0.0106 & 0.0020 & 0.0094 & 0.0008 \\
+Accuracy Equality 1 & 0.0133 & 0.0090 & 0.0042 & 0.0059 & 0.0074 \\
+Accuracy Equality 2 & 0.0216 & 0.0041 & 0.0175 & 0.0019 & 0.0197 \\
 \bottomrule

### 2024-12-04 paper/paper.tex
experiments

@@
 \usepackage{subcaption}
+\usepackage{algorithm}
+\usepackage{algorithmic}
 
@@
 
-To circumvent the complexity explosion, instead, \cite{mckenna2021winning} devised a technique where the mutual information of all the database attribute pairs is calculated, and then a maximum spanning tree algorithm was run with edge weights being the mutual information to obtain a skeleton spanning-tree-shaped Markov random field.
-
-TODO: mst was obtained. delete the word algorithm
+To circumvent the complexity explosion, instead, \cite{mckenna2021winning} devised a technique where the mutual information of all the database attribute pairs is calculated, and then a maximum spanning tree is obtained with edge weights being the mutual information to form a skeleton tree-shaped Markov random field.
 
@@
 
-TODO: use latex algorithm. pseudo code
+\begin{algorithm}
+\caption{something something}
+\label{alg:heuristic}
+\begin{algorithmic}[1]
+\STATE Initialize $x \gets 0$
+\STATE Initialize $y \gets 1$
+\FOR{$i \gets 1$ to $n$}
+    \IF{$i$ is even}
+        \STATE $x \gets x + i$
+    \ELSE
+        \STATE $y \gets y \times i$
+    \ENDIF
+\ENDFOR
+\RETURN $x + y$
+\end{algorithmic}
+\end{algorithm}
 
@@
 
-% this 100 experiment is running
-
-The fit time is 17m1s without heuristic. With heuristic it is 924m15s.
-
-The average of their differences is $0.0787$. Without heuristic it is $0.0775$.
-
-We observed that across all examined fairness measures, their difference all fall below 0.1. The average of their differences is 0.0431, which we consider quite satisfactory.
+% We observed that across all examined fairness measures, their difference all fall below 0.1. The average of their differences is 0.0431, which we consider quite satisfactory.
 
 \begin{table}[h]
-\caption{Fairness measures experiment results of the adult dataset. Average of differences is 0.0431.}
+\caption{
+    Fairness measures experiment results of the adult dataset.
+    With heuristic, average difference is $0.0787$, and fit time is 924m15s.
+    Without heuristic, average difference is $0.0775$, and fit time is 17m1s.
+}
 \label{tab:adult_score}
-\begin{tabular}{ccccc}
+\begin{tabular}{ccccccc}
 \toprule
-\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} \\
+\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} & \textbf{Synthetic(No Heuristic)} & \textbf{Difference(No Heuristic)} \\
 \midrule
-Demographic Parity  & 0.172 & 0.104 & 0.067 \\
-Accuracy Eqaulity   & 0.047 & 0.117 & 0.069 \\
-Equalized Odds 1    & 0.057 & 0.079 & 0.021 \\
-Equalized Odds 2    & 0.166 & 0.122 & 0.044 \\
-Accuracy Equality 1 & 0.100 & 0.132 & 0.031 \\
-Accuracy Equality 2 & 0.119 & 0.146 & 0.027 \\
+Demographic Parity  & 0.1933 & 0.1079 & 0.0853 & 0.0114 & 0.1818 \\
+Accuracy Eqaulity   & 0.0250 & 0.1399 & 0.1149 & 0.0169 & 0.0080 \\
+Equalized Odds 1    & 0.0175 & 0.0870 & 0.0695 & 0.0060 & 0.0115 \\
+Equalized Odds 2    & 0.0114 & 0.0622 & 0.0508 & 0.0303 & 0.0189 \\
+Accuracy Equality 1 & 0.1941 & 0.1466 & 0.0474 & 0.0315 & 0.1626 \\
+Accuracy Equality 2 & 0.1102 & 0.1450 & 0.0348 & 0.0299 & 0.0803 \\
 \bottomrule
@@
 
-For the COMPAS dataset, the initial spanning tree has a long tail, which is not surprising because, upon closer inspection, they all are related to the original COMPAS risk scores.
+% For the COMPAS dataset, the initial spanning tree has a long tail, which is not surprising because, upon closer inspection, they all are related to the original COMPAS risk scores.
 The heuristic edge addition did not change the graph significantly.
@@
 
-Marginals of this graph are then too passed to the synthetic data generator for fitting.
+% Marginals of this graph are then too passed to the synthetic data generator for fitting.
 
-We ran the same workflow as adult dataset for the COMPAS dataset. The comparison results are shown in Table~\ref{tab:compas_score}.
+% We ran the same workflow as adult dataset for the COMPAS dataset. The comparison results are shown in Table~\ref{tab:compas_score}.
 
-% this experiment is complete
-
-The fit time is 33s without heuristic. With heuristic it is 27m33s.
-
-The average of their differences is $0.0750$. Without heuristic it is $0.0727$.
-
-The results showed an increase in error on the sufficiency measure values.
+% The results showed an increase in error on the sufficiency measure values.
 In particular, one of the measures has an error difference as high as 0.141.
@@
 \begin{table}[h]
-\caption{Fairness measures experiment results of the COMPAS dataset. Average of differences is $0.0750$. Average of differences without heuristic is $0.0727$}
+\caption{
+    Fairness measures experiment results of the COMPAS dataset.
+    With heuristic, average difference is $0.0750$, and fit time is 27m33s.
+    Without heuristic, average difference is $0.0727$, and fit time is 33s.
+}
 \label{tab:compas_score}
@@
 
-The tree grown from the diabetes dataset did not appear to have any particular characteristics.
+% The tree grown from the diabetes dataset did not appear to have any particular characteristics.
 The root of the tree is placed in the BMI value, which reasonably captures most information.
@@
 
-The same process is conducted to fit the synthetic data generator model.
+% The same process is conducted to fit the synthetic data generator model.
 
-The same workflow was done as on previous datasets. The comparison results are shown in Table~\ref{tab:diabetes_score}.
-
-% this experiment is complete
-
-The fit time is 1m24s without heuristic. With heuristic it is 1m44s.
-
-The average of their differences is $0.0067$. Without heuristic it is $0.0078$.
+% The same workflow was done as on previous datasets. The comparison results are shown in Table~\ref{tab:diabetes_score}.
 
@@
 \begin{table}[h]
-\caption{Fairness measures experiment results of the diabetes dataset. Average of differences is $0.0067$. Average of differences without heuristic is $0.0078$}
+\caption{
+    Fairness measures experiment results of the diabetes dataset.
+    With heuristic, average difference is $0.0067$, and fit time is 1m44s.
+    Without heuristic, average difference is $0.0078$, and fit time is 1m24s.
+}
 \label{tab:diabetes_score}
@@
 
-%  TODO: rewrite this
+% %  TODO: rewrite this
 
-Our experiments showed that synthetic data generally preserves the fairness properties with a reasonable degree of accuracy.
+% Our experiments showed that synthetic data generally preserves the fairness properties with a reasonable degree of accuracy.
 The average of the differences between the fairness measure values of the original and synthetic datasets is below 0.1 for all datasets.
@@
 
-For the adult dataset, the average difference was 0.0431, suggesting a close match between the synthetic and the original data in terms of fairness measures.
+% For the adult dataset, the average difference was 0.0431, suggesting a close match between the synthetic and the original data in terms of fairness measures.
 For the diabetes dataset, the average difference was 0.031, which is even lower.
@@
 
-In particular, both the independence and separation measures showed low errors across all datasets, with the differences of all of them below 0.1.
+% In particular, both the independence and separation measures showed low errors across all datasets, with the differences of all of them below 0.1.
 On the other hand, results of accuracy equality also showed low errors, with the differences of one of them as low as 0.005.
 
-This demonstrated that synthetic data can accurately reflect the fairness properties of the original data.
+% This demonstrated that synthetic data can accurately reflect the fairness properties of the original data.
 Therefore, fairness analyses performed on synthetic data will yield results consistent with those on the original data.
@@
 
-The experiments also revealed some limitations of this approach.
+% The experiments also revealed some limitations of this approach.
 In particular, the sufficiency measure showed higher errors compared to other measures.
@@
 
-By close examination of our scenario, we can observe the following: of the three variables, $(\hat{Y},Y,S)$, two of them, namely $(Y,S)$, are both readily available in the original data.
+% By close examination of our scenario, we can observe the following: of the three variables, $(\hat{Y},Y,S)$, two of them, namely $(Y,S)$, are both readily available in the original data.
 In contrast, $\hat{Y}$ is only available in the output of the given AI model, which cannot be captured by the synthetic data at the time of generation.
 
-Referring back to the definition of the fairness measures, we can see the following: separation is concerned with the form $P[\hat{Y} | S, Y] = \frac{P[\hat{Y} \cap S \cap Y]}{P[{S} \cap Y]}$, and sufficiency is concerned with the form $P[Y | S, \hat{Y}] = \frac{P[Y \cap S \cap \hat{Y}]}{P[{S} \cap \hat{Y}]}$.
+% Referring back to the definition of the fairness measures, we can see the following: separation is concerned with the form $P[\hat{Y} | S, Y] = \frac{P[\hat{Y} \cap S \cap Y]}{P[{S} \cap Y]}$, and sufficiency is concerned with the form $P[Y | S, \hat{Y}] = \frac{P[Y \cap S \cap \hat{Y}]}{P[{S} \cap \hat{Y}]}$.
 
-TODO: expand all defs and count the nums of avail vars
+% TODO: expand all defs and count the nums of avail vars
 
-This explains why sufficiency measures could have higher errors compared to separation because synthetic data have less information about them.
+% This explains why sufficiency measures could have higher errors compared to separation because synthetic data have less information about them.
 While only one variable is missing in the numerator for separation, one more variable is missing in the denominator for sufficiency.
 
-Therefore, it is harder to approximate sufficiency measures on synthetic data.
+% Therefore, it is harder to approximate sufficiency measures on synthetic data.
 This is a fundamental limitation of this approach, and it is important to be aware of this when interpreting the results of fairness analyses.

### 2024-12-05 paper/paper.tex
sophisticated

@@
 Since edges represent dependencies, cliques in a Markov random field represent groups of variables that are all mutually dependent.
-As a machine learning model, there has been much development in the fitting and inference of Markov random fields\cite{koller2009probabilistic,murphy2023probabilistic}.
+As a machine learning model, there has been much development in the estimation and inference of Markov random fields\cite{koller2009probabilistic,murphy2023probabilistic}.
 
@@
 Releasings of analyses on real data may inadvertently reveal sensitive information by data inference attacks.
-Attackers can exploit patterns in data outputs or combine outputs with external data to infer sensitive information.
+Attackers can exploit data patterns in outputs or combine outputs with external data to infer sensitive information.
 
-Thus, we introduce a new framework where the auditor generates synthetic data based on real data upon retrieval of the real data, and then holds onto the synthetic data and discards the real data, preventing all further data breaches.
-The third-party retains the ability to audit all incoming future models as needed.
+Thus, we introduce a new framework where the auditor generates synthetic data based on real data upon retrieval of the real data, and then holds onto the synthetic data and discards the real data, preventing all further security and privacy violations.
+The third-party still retains the ability to audit all incoming future models as needed.
 
@@
 
-We employed the tools of the winner of the 2018 NIST Differential Privacy Synthetic Data Challenge competition\cite{NIST2018} by \cite{McKenna_Private-PGM_2021,mckenna2021winning,mckenna2019graphical} and the fairness checker tool from our previous research\cite{yuan2024ensuring}.
+We employed the tools of the winner of the 2018 NIST Differential Privacy Synthetic Data Challenge competition\cite{NIST2018} by \cite{nist_ryan_2018,McKenna_Private-PGM_2021,mckenna2021winning,mckenna2019graphical} and the fairness checker tool from our previous research\cite{yuan2024ensuring}.
 
@@
 Underneath the hood, the tool employs a Markov random field.
-The select step corresponds to marking cliques in a Markov random field, and the generate step corresponds to sampling by inference from the fitted Markov random field.
+The select step corresponds to marking cliques in a Markov random field, and the generate step corresponds to sampling from the fitted Markov random field.
 
@@
 In a perfect world where all correlation information is to be preserved, we may wish to make a completely connected graph.
-However, this was found to be intractable as the complexity of the problem would skyrocket.
+However, this is intractable as the complexity of the problem would skyrocket.
+Furthermore, algorithms for Markov random field favor graphs with specific shapes, such as trees.
 
-To circumvent the complexity explosion, instead, \cite{mckenna2021winning} devised a technique where the mutual information of all the database attribute pairs is calculated, and then a maximum spanning tree is obtained with edge weights being the mutual information to form a skeleton tree-shaped Markov random field.
+To circumvent this complexity explosion, instead, \cite{mckenna2021winning} devised a technique where the mutual information of all the database attribute pairs is calculated, and then a maximum spanning tree is identified with edge weights being the mutual information to obtain a skeleton tree-shaped Markov random field.
 

### 2024-12-05 paper/paper.tex
related work

@@
 
-TODO: add more connections to our work
+% fairness
 
@@
 Various fairness measures have been proposed to quantify\cite{yeh2024analyzing} the fairness of AI models\cite{pessach2022review,corbett2017algorithmic,vzliobaite2017measuring,hardt2016equality,corbett2017algorithmic,berk2021fairness,chouldechova2017fair,kleinberg2016inherent}.
+We consider these fairness measures in this work.
 
 Auditing of AI models is an important step in ensuring that these models are fair\cite{ferrara2023fairness}.
-Different tools have been developed to check the fairness of AI models\cite{yuan2024ensuring,saleiro2018aequitas,bellamy2019ai,bird2020fairlearn}.
+Different tools have been developed to check the fairness of AI models\cite{saleiro2018aequitas,bellamy2019ai,bird2020fairlearn}.
+We use a tool produced from our previous work\cite{yuan2024ensuring}.
 
@@
 It offers a formal framework for quantifying privacy guarantees when releasing information derived from sensitive data\cite{dwork2006calibrating,dwork2014algorithmic}.
+We use Differential Privacy in this work to protect the privacy of individuals in the data in our auditing framework.
 
 Different flavors of Differential Privacy have been proposed over the years\cite{desfontaines2019sok}, such as Gaussian Differential Privacy\cite{dong2022gaussian}, Pufferfish Differential Privacy\cite{kifer2012rigorous}, Bayesian Differential Privacy\cite{triastcyn2020bayesian}, and R\'enyi Differential Privacy\cite{mironov2017renyi}.
+We consider R\'enyi Differential Privacy specifically in this work.
 
@@
 There have been several techniques developed for Differentially Private synthetic data generation\cite{rosenblatt2020differentially,fan2020relational,bowen2019comparative,bowen2020comparative,arnold2020really,xu2019modeling} in recent years.
+We use the technique that won the 2018 NIST Differential Privacy Synthetic Data Challenge competition\cite{mckenna2021winning}.
 
-TODO: some works aim to change properties of og data. we want to preserve. so we dont consider this case
-
-There are also works that aim to introduce bias to synthetic data\cite{jiang2024synthetic,baumann2023bias}.
+There have also been some works that aim to alter the properties of synthetic data, such as introducing bias to them\cite{jiang2024synthetic,baumann2023bias}.
+In this work, we aim to preserve the properties of the original data.
+Thus, we do not consider these works.
 
 While helpful, there are some technical limitations\cite{stadler2022synthetic,cheng2021can,ganev2022robin,wyllie2024fairness} and ethical concerns\cite{whitney2024real} with the use of synthetic data.
+Synthetic data may not always preserve properties of real data.
+This may cause inaccuracies in downstream tasks such as fairness evaluation.
+Our work examines these limitations.
 
@@
 
-% \begin{table}[h]
-% \caption{Example marginals.}
-% \label{tab:marginal-example}
-% \centering
-% \begin{subtable}[t]{0.3\linewidth}
-%   \caption{Fairness measures experiment results of the adult dataset. Average of differences is 0.0431.}
-%   \label{tab:adult_score}
-%   \begin{tabular}{ccccc}
-%   \toprule
-%   \textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} \\
-%   \midrule
-%   Demographic Parity  & 0.172 & 0.104 & 0.067 \\
-%   Accuracy Eqaulity   & 0.047 & 0.117 & 0.069 \\
-%   Equalized Odds 1    & 0.057 & 0.079 & 0.021 \\
-%   Equalized Odds 2    & 0.166 & 0.122 & 0.044 \\
-%   Accuracy Equality 1 & 0.100 & 0.132 & 0.031 \\
-%   Accuracy Equality 2 & 0.119 & 0.146 & 0.027 \\
-%   \bottomrule
-%   \end{tabular}
-% \end{subtable}
-% \begin{subtable}[t]{0.3\linewidth}
-%   \centering
-%   \caption{Fairness measures experiment results of the COMPAS dataset. Average of differences is 0.031.}
-%   \label{tab:diabetes_score}
-%   \begin{tabular}{cccc}
-%   \toprule
-%   \textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} \\
-%   \midrule
-%   Demographic Parity  & 0.013 & 0.015 & 0.002 \\
-%   Accuracy Eqaulity   & 0.007 & 0.009 & 0.002 \\
-%   Equalized Odds 1    & 0.000 & 0.003 & 0.003 \\
-%   Equalized Odds 2    & 0.008 & 0.106 & 0.097 \\
-%   Accuracy Equality 1 & 0.013 & 0.097 & 0.084 \\
-%   Accuracy Equality 2 & 0.021 & 0.020 & 0.001 \\
-%   \bottomrule
-%   \end{tabular}
-% \end{subtable}
-% \end{table}
-
 \subsection{Adult Income Dataset}
@@
 
-% TODO: mention model fit time? yes. do experiments!
-
 \subsection{Positive Results}
-
-% %  TODO: rewrite this
 
@@
 
-%  TODO: rewrite this
-
 % The experiments also revealed some limitations of this approach.
@@
 
-% TODO: expand all defs and count the nums of avail vars
+% expand all defs and count the nums of avail vars
 

### 2024-12-05 paper/paper.tex
intro draft
intro

@@
 \section{Introduction}
+
+Fairness in machine learning has become an important topic as AI systems become widely used.
+Biased AI systems could result in amplified unfairness.
+Ensuring fairness in AI systems is crucial to prevent these biases from being exacerbated by AI systems.
+One approach is to audit the fairness of existing AI systems.
+Quantitative fairness auditing is a process of evaluating the fairness of AI systems with a range of fairness metrics.
+Many metrics have been proposed to help evaluate the fairness of AI systems.
+
+% data privacy
+
+To conduct audits, auditors may rely on access to real datasets containing sensitive information, raising significant security and privacy concerns.
+This reliance invites data security attacks on auditors, making them targets of unauthorized access.
+Analysis on real data runs the risk of data inference attacks, where confidential information may be deduced from seemingly harmless or aggregated data.
+Various technologies have been developed to mitigate these risks, such as Differential Privacy, where the idea is that whether or not any individual is in a dataset has a limited impact.
+
+% differentially private synthetic data for fairness auditing
+
+We propose a novel auditing framework that leverages Differentially Private synthetic data to evaluate the fairness of AI systems.
+Our framework lets the auditors assess the fairness of AI systems without exposing sensitive information.
+Differentially Private synthetic data is a technique that generates synthetic data from real data that preserves some statistical properties of the real data while ensuring Differential Privacy.
+This technology enables auditing without exposing sensitive information.
+However, synthetic data also introduces new challenges.
+Whether or not it accurately preserves the fairness properties of the real data is a critical question.
+
+% contribution
+
+Our work examines the capabilities of existing Differentially Private synthetic data generation technologies in preserving fairness properties.
+Through empirical experiments on multiple real datasets, we aim to determine the effectiveness of Differentially Private synthetic data in this respect.
 

### 2024-12-05 paper/paper.tex
title
abstract wip

@@
-%%
-%% This is file `sample-manuscript.tex',
-%% generated with the docstrip utility.
-%%
-%% The original source files were:
-%%
-%% samples.dtx  (with options: `all,proceedings,bibtex,manuscript')
-%%
-%% IMPORTANT NOTICE:
-%%
-%% For the copyright see the source file.
-%%
-%% Any modified versions of this file must be renamed
-%% with new filenames distinct from sample-manuscript.tex.
-%%
-%% For distribution of the original source see the terms
-%% for copying and modification in the file samples.dtx.
-%%
-%% This generated file may be distributed as long as the
-%% original source files, as listed above, are part of the
-%% same distribution. (The sources need not necessarily be
-%% in the same archive or directory.)
-%%
-%%
-%% Commands for TeXCount
-%TC:macro \cite [option:text,text]
-%TC:macro \citep [option:text,text]
-%TC:macro \citet [option:text,text]
-%TC:envir table 0 1
-%TC:envir table* 0 1
-%TC:envir tabular [ignore] word
-%TC:envir displaymath 0 word
-%TC:envir math 0 word
-%TC:envir comment 0 0
-%%
-%%
-%% The first command in your LaTeX source must be the \documentclass
-%% command.
-%%
-%% For submission and review of your manuscript please change the
-%% command to \documentclass[manuscript, screen, review]{acmart}.
-%%
-%% When submitting camera ready or to TAPS, please change the command
-%% to \documentclass[sigconf]{acmart} or whichever template is required
-%% for your publication.
-%%
-%%
 \documentclass[manuscript,screen,review,anonymous]{acmart}
 % \documentclass[acmsmall,sigconf]{acmart}
-
-%%
-%% \BibTeX command to typeset BibTeX logo in the docs
-\AtBeginDocument{%
-  \providecommand\BibTeX{{%
-    Bib\TeX}}}
 
@@
 % \acmISBN{978-1-4503-XXXX-X/18/06}
-
-%%
-%% Submission ID.
-%% Use this when submitting an article to a sponsored event. You'll
-%% receive a unique submission ID from the organizers
-%% of the event, and this ID should be used as the parameter to this command.
-%%\acmSubmissionID{123-A56-BU3}
-
-%%
-%% For managing citations, it is recommended to use bibliography
-%% files in BibTeX format.
-%%
-%% You can then either use BibTeX with the ACM-Reference-Format style,
-%% or BibLaTeX with the acmnumeric or acmauthoryear sytles, that include
-%% support for advanced citation of software artefact from the
-%% biblatex-software package, also separately available on CTAN.
-%%
-%% Look at the sample-*-biblatex.tex files for templates showcasing
-%% the biblatex styles.
-%%
-
-%%
-%% The majority of ACM publications use numbered citations and
-%% references.  The command \citestyle{authoryear} switches to the
-%% "author year" style.
-%%
-%% If you are preparing content for an event
-%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
-%% citations and references.
-%% Uncommenting
-%% the next command will enable that style.
-%%\citestyle{acmauthoryear}
 
@@
 %% allowing the author to define a "short title" to be used in page headers.
-\title{Quantitative Auditing of Fairness Measures with Differentially Private Synthetic Data}
+\title{Quantitative Auditing of AI Fairness with Differentially Private Synthetic Data}
 
@@
 \begin{abstract}
-  abstract
+Ensuring fairness in AI systems is crucial, but auditing these systems often requires sensitive data, which raises security and privacy concerns.
+To address this, we introduce a framework that utilizes Differentially Private synthetic data for fairness evaluations.
+This approach allows auditors to assess AI systems without exposing sensitive information.
+Through experiments on datasets like Adult, COMPAS, and Diabetes, we compare fairness metrics of synthetic and real data.
+Our results ...
 \end{abstract}
@@
 \ccsdesc[300]{Mathematics of computing~Contingency table analysis}
-% %%
-% \begin{CCSXML}
-% <ccs2012>
-%  <concept>
-%   <concept_id>00000000.0000000.0000000</concept_id>
-%   <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
-%   <concept_significance>500</concept_significance>
-%  </concept>
-%  <concept>
-%   <concept_id>00000000.00000000.00000000</concept_id>
-%   <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
-%   <concept_significance>300</concept_significance>
-%  </concept>
-%  <concept>
-%   <concept_id>00000000.00000000.00000000</concept_id>
-%   <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
-%   <concept_significance>100</concept_significance>
-%  </concept>
-%  <concept>
-%   <concept_id>00000000.00000000.00000000</concept_id>
-%   <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
-%   <concept_significance>100</concept_significance>
-%  </concept>
-% </ccs2012>
-% \end{CCSXML}
 
-% \ccsdesc[500]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
-% \ccsdesc[300]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
-% \ccsdesc{Do Not Use This Code~Generate the Correct Terms for Your Paper}
-% \ccsdesc[100]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
-
-% %%
-% %% Keywords. The author(s) should pick words that accurately describe
-% %% the work being presented. Separate the keywords with commas.
-% \keywords{Do, Not, Us, This, Code, Put, the, Correct, Terms, for,
-%   Your, Paper}
+\keywords{AI, fairness, auditing, differential privacy, synthetic data}
 
@@
 
-%%
-%% This command processes the author and affiliation and title
-%% information and builds the first part of the formatted document.
 \maketitle
@@
 
-We looked at several publicly available datasets, such as adult\cite{adult_2,Kaggle_Adult_Census_Income}, COMPAS\cite{larson2016propublica,Kaggle_COMPAS_Dataset}, and diabetes\cite{diabetes_34,Kaggle_Diabetes_Prediction}.
-The adult dataset comes from the 1994 census in the United States and contains about 30000 individuals.
+We looked at several publicly available datasets, such as Adult\cite{adult_2,Kaggle_Adult_Census_Income}, COMPAS\cite{larson2016propublica,Kaggle_COMPAS_Dataset}, and Diabetes\cite{diabetes_34,Kaggle_Diabetes_Prediction}.
+The Adult dataset comes from the 1994 census in the United States and contains about 30000 individuals.
 The COMPAS dataset comes from an investigative report by ProPublica of the COMPAS criminal recidivism assessment system and contains about 7000 individuals.
-The diabetes dataset comes from the hospital readmission data published in the 1994 AI in Medicine journal and contains about 100000 individuals.
+The Diabetes dataset comes from the hospital readmission data published in the 1994 AI in Medicine journal and contains about 100000 individuals.
 Since these datasets all have binary outcomes, we did not consider the case of non-binary outcomes in the experiments.
@@
       \includegraphics[width=\textwidth]{adult_mst}
-      \caption{Markov random field for marginals of the adult dataset.}
+      \caption{Markov random field for marginals of the Adult dataset.}
       \label{fig:adult_mst}
-      \Description{Markov random field for marginals of the adult dataset.}
+      \Description{Markov random field for marginals of the Adult dataset.}
   \end{subfigure}
@@
       \includegraphics[width=\textwidth]{diabetes_mst}
-      \caption{Markov random field for marginals of the diabetes dataset.}
+      \caption{Markov random field for marginals of the Diabetes dataset.}
       \label{fig:diabetes_mst}
@@
 
-For the adult income dataset, the shape of the maximum spanning tree is very shallow, almost resembling a star; it has one internal node and all but one of the leaves have a depth of one.
+For the Adult income dataset, the shape of the maximum spanning tree is very shallow, almost resembling a star; it has one internal node and all but one of the leaves have a depth of one.
 After introducing edges according to our heuristic, we observed an increase in the pairwise edges of the leaves, forming many 3-cliques and two 4-cliques.
@@
 \caption{
-    Fairness measures experiment results of the adult dataset.
+    Fairness measures experiment results of the Adult dataset.
     With heuristic, average difference is $0.0787$, and fit time is 924m15s.
@@
 \caption{
-    Fairness measures experiment results of the diabetes dataset.
+    Fairness measures experiment results of the Diabetes dataset.
     With heuristic, average difference is $0.0067$, and fit time is 1m44s.

### 2024-12-06 paper/paper.tex
minor

@@
 Our results ...
+(to be continued)
 \end{abstract}
@@
 \]
-where $D_\alpha(P_1 \Vert P_2)$ is the R\'enyi divergence\cite{van2014renyi,van2010renyi,li2016renyi} of order $\alpha$ between probability distributions $P_1,P_2$ over $x$:
+where $D_\alpha(P_1 \Vert P_2)$ is the R\'enyi divergence\cite{van2014renyi,van2010renyi,li2016renyi} of order $\alpha$ between probability distributions $P_1,P_2$ over $x$
 \[
@@
 
-In a perfect world where all correlation information is to be preserved, we may wish to make a completely connected graph.
+In a perfect world where all correlation information is to be preserved, we may wish to make a complete graph.
 However, this is intractable as the complexity of the problem would skyrocket.
@@
 
-\begin{algorithm}
-\caption{something something}
-\label{alg:heuristic}
-\begin{algorithmic}[1]
-\STATE Initialize $x \gets 0$
-\STATE Initialize $y \gets 1$
-\FOR{$i \gets 1$ to $n$}
-    \IF{$i$ is even}
-        \STATE $x \gets x + i$
-    \ELSE
-        \STATE $y \gets y \times i$
-    \ENDIF
-\ENDFOR
-\RETURN $x + y$
-\end{algorithmic}
-\end{algorithm}
+% \begin{algorithm}
+% \caption{something something}
+% \label{alg:heuristic}
+% \begin{algorithmic}[1]
+% \STATE Initialize $x \gets 0$
+% \STATE Initialize $y \gets 1$
+% \FOR{$i \gets 1$ to $n$}
+%     \IF{$i$ is even}
+%         \STATE $x \gets x + i$
+%     \ELSE
+%         \STATE $y \gets y \times i$
+%     \ENDIF
+% \ENDFOR
+% \RETURN $x + y$
+% \end{algorithmic}
+% \end{algorithm}
 

### 2024-12-09 paper/paper.tex
colors

@@
 \documentclass[manuscript,screen,review,anonymous]{acmart}
+\usepackage{xcolor}
+\usepackage{mathtools}
 % \documentclass[acmsmall,sigconf]{acmart}
@@
 & Equal Calibration & $\abs{P[Y = 1 | S = 1, \hat{V} = v] - P[Y = 1 | S \neq 1, \hat{V} = v]} \leq \epsilon$ \\
-\multirow{3}{*}{N/A} & Overall Accuracy Equality & $\abs{P[Y = \hat{Y} | S = 1] - P[Y = \hat{Y} | S \neq 1]} \leq \epsilon$ \\
+\multirow{3}{*}{N/A} & Accuracy Equality & $\abs{P[Y = \hat{Y} | S = 1] - P[Y = \hat{Y} | S \neq 1]} \leq \epsilon$ \\
 & Positive Balance & $\abs{E[\hat{V} | Y = 1, S = 1] - E[\hat{V} | Y = 1, S \neq 1]} \leq \epsilon$ \\
@@
 
-% independence
-% \[
-% P[\hat{Y} | S] - P[\hat{Y} | \overline{S}]
-% = \frac{P[\hat{Y} \cap S]}{P[{S}]} - \frac{P[\hat{Y} \cap \overline{S}]}{P[\overline{S}]}
-% \]
+\definecolor{lightgreen}{rgb}{0.6, 1.0, 0.6}
+\definecolor{lightred}{rgb}{1.0, 0.6, 0.6}
+\newcommand{\mathhighlight}[2]{\colorbox{#1}{$\displaystyle #2$}}
+\newcommand{\y}[1]{\mathhighlight{lightgreen}{#1}}
+\newcommand{\n}[1]{\mathhighlight{lightred}{#1}}
 
-% separation
-% \[
-% P[\hat{Y} | S, Y] - P[\hat{Y} | \overline{S}, Y]
-% = \frac{P[\hat{Y} \cap S \cap Y]}{P[{S} \cap Y]} - \frac{P[\hat{Y} \cap \overline{S} \cap Y]}{P[\overline{S} \cap Y]}
-% \]
+independence
+\[
+P[\hat{Y} | S] - P[\hat{Y} | \overline{S}]
+= \frac{P[\n{\hat{Y}} \cap \y{S}]}{P[\y{S}]} - \frac{P[\n{\hat{Y}} \cap \y{\overline{S}}]}{P[\y{\overline{S}}]}
+\]
 
-% sufficiency
-% \[
-% P[Y | S, \hat{Y}] - P[Y | \overline{S}, \hat{Y}]
-% = \frac{P[Y \cap S \cap \hat{Y}]}{P[{S} \cap \hat{Y}]} - \frac{P[Y \cap \overline{S} \cap \hat{Y}]}{P[\overline{S} \cap \hat{Y}]}
-% \]
+separation
+\[
+P[\hat{Y} | S, Y] - P[\hat{Y} | \overline{S}, Y]
+= \frac{P[\n{\hat{Y}} \cap \y{S} \cap \y{Y}]}{P[\y{S} \cap \y{Y}]} - \frac{P[\n{\hat{Y}} \cap \y{\overline{S}} \cap \y{Y}]}{P[\y{\overline{S}} \cap \y{Y}]}
+\]
+
+sufficiency
+\[
+P[Y | S, \hat{Y}] - P[Y | \overline{S}, \hat{Y}]
+= \frac{P[\y{Y} \cap \y{S} \cap \n{\hat{Y}}]}{P[\y{S} \cap \n{\hat{Y}}]} - \frac{P[\y{Y} \cap \y{\overline{S}} \cap \n{\hat{Y}}]}{P[\y{\overline{S}} \cap \n{\hat{Y}}]}
+\]
+
+accuracy equality
+\[
+P[Y = \hat{Y} | {S} ] - P[Y = \hat{Y} | \overline{S}]
+= \frac{P[\y{Y} = \n{\hat{Y}} \cap \y{S}]}{P[\y{S}]} - \frac{P[\y{Y} = \n{\hat{Y}} \cap \y{\overline{S}}]}{P[\y{\overline{S}}]}
+\]
 

### 2024-12-10 paper/paper.tex
Added todos

@@
 
+% TODO: add more to intro
+
+% TODO: lowercase Diff
+
+% fairness
+
 Fairness in machine learning has become an important topic as AI systems become widely used.
@@
 
+% TODO: ai woulld be found to be unfair by 3rd party. example: compas
+
 % data privacy
@@
 Various technologies have been developed to mitigate these risks, such as Differential Privacy, where the idea is that whether or not any individual is in a dataset has a limited impact.
+
+% TODO: to mitigate use synthetic data. principals of this
 
@@
 
+% TODO: remove unconsidered
+
+% TODO: rename equalized odds 1,2
+
 \begin{table*}[h]
@@
 \midrule
-\multirow{4}{*}{Independence} & Disparate Impact & $\frac{P[\hat{Y} = 1 | S \neq 1]}{P[\hat{Y} = 1 | S = 1]} \geq 1 - \epsilon$ \\
+\multirow{1}{*}{Independence}
+% & Disparate Impact & $\frac{P[\hat{Y} = 1 | S \neq 1]}{P[\hat{Y} = 1 | S = 1]} \geq 1 - \epsilon$ \\
 & Demographic Parity & $\abs{P[\hat{Y} = 1 | S = 1] - P[\hat{Y} = 1 | S \neq 1]} \leq \epsilon$ \\
-& Conditional Statistical Parity & $\abs{P[\hat{Y} = 1 | S = 1, L = l] - P[\hat{Y} = 1 | S \neq 1, L = l]} \leq \epsilon$ \\
-& Mean Difference & $\abs{E[\hat{Y}|S = 1] - E[\hat{Y}|S \neq 1]} \leq \epsilon$ \\
-\multirow{4}{*}{Separation} & \multirow{2}{*}{Equalized Odds} & $\abs{P[\hat{Y} = 1 | S = 1, Y = 0] - P[\hat{Y} = 1 | S \neq 1, Y = 0]} \leq \epsilon$ \\
+% & Conditional Statistical Parity & $\abs{P[\hat{Y} = 1 | S = 1, L = l] - P[\hat{Y} = 1 | S \neq 1, L = l]} \leq \epsilon$ \\
+% & Mean Difference & $\abs{E[\hat{Y}|S = 1] - E[\hat{Y}|S \neq 1]} \leq \epsilon$ \\
+\multirow{2}{*}{Separation}
+& \multirow{2}{*}{Equalized Odds} & $\abs{P[\hat{Y} = 1 | S = 1, Y = 0] - P[\hat{Y} = 1 | S \neq 1, Y = 0]} \leq \epsilon$ \\
 & & $\abs{P[\hat{Y} = 1 | S = 1, Y = 1] - P[\hat{Y} = 1 | S \neq 1, Y = 1]} \leq \epsilon$ \\
-& Equal Opportunity & $\abs{P[\hat{Y} = 1 | S = 1, Y = 1] - P[\hat{Y} = 1 | S \neq 1, Y = 1]} \leq \epsilon$ \\
-& Predictive Equality & $\abs{P[\hat{Y} = 1 | S = 1, Y = 0] - P[\hat{Y} = 1 | S \neq 1, Y = 0]} \leq \epsilon$ \\
-\multirow{4}{*}{Sufficiency} & \multirow{2}{*}{Conditional Use Accuracy Equality} & $\abs{P[Y = 1 | S = 1, \hat{Y} = 1] - P[Y = 1 | S \neq 1, \hat{Y} = 1]} \leq \epsilon$ \\
+% & Equal Opportunity & $\abs{P[\hat{Y} = 1 | S = 1, Y = 1] - P[\hat{Y} = 1 | S \neq 1, Y = 1]} \leq \epsilon$ \\
+% & Predictive Equality & $\abs{P[\hat{Y} = 1 | S = 1, Y = 0] - P[\hat{Y} = 1 | S \neq 1, Y = 0]} \leq \epsilon$ \\
+\multirow{2}{*}{Sufficiency}
+& \multirow{2}{*}{Conditional Use Accuracy Equality} & $\abs{P[Y = 1 | S = 1, \hat{Y} = 1] - P[Y = 1 | S \neq 1, \hat{Y} = 1]} \leq \epsilon$ \\
 & & $\abs{P[Y = 0 | S = 1, \hat{Y} = 0] - P[Y = 0 | S \neq 1, \hat{Y} = 0]} \leq \epsilon$ \\
-& Predictive Parity & $\abs{P[Y = 1 | S = 1, \hat{Y} = 1] - P[Y = 1 | S \neq 1, \hat{Y} = 1]} \leq \epsilon$ \\
-& Equal Calibration & $\abs{P[Y = 1 | S = 1, \hat{V} = v] - P[Y = 1 | S \neq 1, \hat{V} = v]} \leq \epsilon$ \\
-\multirow{3}{*}{N/A} & Accuracy Equality & $\abs{P[Y = \hat{Y} | S = 1] - P[Y = \hat{Y} | S \neq 1]} \leq \epsilon$ \\
-& Positive Balance & $\abs{E[\hat{V} | Y = 1, S = 1] - E[\hat{V} | Y = 1, S \neq 1]} \leq \epsilon$ \\
-& Negative Balance & $\abs{E[\hat{V} | Y = 0, S = 1] - E[\hat{V} | Y = 0, S \neq 1]} \leq \epsilon$ \\
+% & Predictive Parity & $\abs{P[Y = 1 | S = 1, \hat{Y} = 1] - P[Y = 1 | S \neq 1, \hat{Y} = 1]} \leq \epsilon$ \\
+% & Equal Calibration & $\abs{P[Y = 1 | S = 1, \hat{V} = v] - P[Y = 1 | S \neq 1, \hat{V} = v]} \leq \epsilon$ \\
+\multirow{1}{*}{N/A}
+& Overall Accuracy Equality & $\abs{P[Y = \hat{Y} | S = 1] - P[Y = \hat{Y} | S \neq 1]} \leq \epsilon$ \\
+% & Positive Balance & $\abs{E[\hat{V} | Y = 1, S = 1] - E[\hat{V} | Y = 1, S \neq 1]} \leq \epsilon$ \\
+% & Negative Balance & $\abs{E[\hat{V} | Y = 0, S = 1] - E[\hat{V} | Y = 0, S \neq 1]} \leq \epsilon$ \\
 \bottomrule
@@
 \begin{definition}[R\'enyi Differential Privacy (RDP)]\label{def:rdp}
-Let $P_{\mathbf{X}}$ denote the probability distribution induced by the random vector $\mathbf{X}$.
+Let $P_{\mathbf{X}}$ denote the probability distribution associated with the random vector $\mathbf{X}$.
 A randomized mechanism $M$ satisfies $(\alpha,\gamma)$-RDP for $\alpha \geq 1$ and $\gamma \geq 1$ if, for all databases $\db_1 \sim \db_2$, we have
@@
 
+% TODO: reiterate intro
+
+% TODO: goal of this framework
+
 Our auditing framework is tripartite. It consists of three parties: the data provider, the model maker, and the third-party auditor.
+
+% TODO: write more about these paragraphs
 
@@
 \label{sec:method}
+
+% TODO: add a overarching example for methodologies
 
@@
 
-We hence developed an alternative heuristic for the general-purpose workflow.
+% We hence developed an alternative heuristic for the general-purpose workflow.
 As mentioned in Section~\ref{sec:prelim}, the mutual information of two random variables is bounded by the pair's respective Shannon entropy.
@@
 
-% \begin{algorithm}
-% \caption{something something}
-% \label{alg:heuristic}
-% \begin{algorithmic}[1]
-% \STATE Initialize $x \gets 0$
-% \STATE Initialize $y \gets 1$
-% \FOR{$i \gets 1$ to $n$}
-%     \IF{$i$ is even}
-%         \STATE $x \gets x + i$
-%     \ELSE
-%         \STATE $y \gets y \times i$
-%     \ENDIF
-% \ENDFOR
-% \RETURN $x + y$
-% \end{algorithmic}
-% \end{algorithm}
+% TODO:
+% for synth to good : depend on domain knowledge, tractibility
+% synth algos use dependencies
+% we DO NOT use this. we do vanilla
+% experiment didnt developed heuristics:
+% 1. lack of domain knowledge
+% 2. different prediction target. cannot tailor a priori
 
@@
 We used various datasets with fairness concerns mentioned in \cite{pessach2022review}.
+
+% TODO: move this to their respective subsection
+
+% TODO: reiterate methodologies
 
@@
 
-\begin{figure}
-  \centering
-  \begin{subfigure}[b]{0.3\textwidth}
-      \centering
-      \includegraphics[width=\textwidth]{adult_mst}
-      \caption{Markov random field for marginals of the Adult dataset.}
-      \label{fig:adult_mst}
-      \Description{Markov random field for marginals of the Adult dataset.}
-  \end{subfigure}
-  \hfill
-  \begin{subfigure}[b]{0.3\textwidth}
-      \centering
-      \includegraphics[width=\textwidth]{compas_mst}
-      \caption{Markov random field for marginals of the COMPAS dataset.}
-      \label{fig:compas_mst}
-      \Description{Markov random field for marginals of the COMPAS dataset.}
-  \end{subfigure}
-  \hfill
-  \begin{subfigure}[b]{0.3\textwidth}
-      \centering
-      \includegraphics[width=\textwidth]{diabetes_mst}
-      \caption{Markov random field for marginals of the Diabetes dataset.}
-      \label{fig:diabetes_mst}
-      \Description{Markov random field for marginals of the COMPAS dataset.}
-  \end{subfigure}
-      \caption{Markov random field for marginals of the experimented datasets.}
-      \label{fig:msts}
-\end{figure}
+% \begin{figure}
+%   \centering
+%   \begin{subfigure}[b]{0.3\textwidth}
+%       \centering
+%       \includegraphics[width=\textwidth]{adult_mst}
+%       \caption{Markov random field for marginals of the Adult dataset.}
+%       \label{fig:adult_mst}
+%       \Description{Markov random field for marginals of the Adult dataset.}
+%   \end{subfigure}
+%   \hfill
+%   \begin{subfigure}[b]{0.3\textwidth}
+%       \centering
+%       \includegraphics[width=\textwidth]{compas_mst}
+%       \caption{Markov random field for marginals of the COMPAS dataset.}
+%       \label{fig:compas_mst}
+%       \Description{Markov random field for marginals of the COMPAS dataset.}
+%   \end{subfigure}
+%   \hfill
+%   \begin{subfigure}[b]{0.3\textwidth}
+%       \centering
+%       \includegraphics[width=\textwidth]{diabetes_mst}
+%       \caption{Markov random field for marginals of the Diabetes dataset.}
+%       \label{fig:diabetes_mst}
+%       \Description{Markov random field for marginals of the COMPAS dataset.}
+%   \end{subfigure}
+%       \caption{Markov random field for marginals of the experimented datasets.}
+%       \label{fig:msts}
+% \end{figure}
 
 \subsection{Adult Income Dataset}
+
+% TODO: dont mention shape of graph
 
@@
 
+% TODO:
+first list formulas
+
+count vars
+
+theyre not part of marginals
+
+they cant be computed
+
+we can say less about fairness with these with less info
+
+auditor need to know theyre aproxing scores
+
+auditor need to keep in mind that these scores are for datasets and we preserve these scores thats it. scores may not be accurate. it doesnt mean its less easy to test fairness
+
 \subsection{Positive Results}
+
+% TODO:
+it works!
 
@@
 This is a fundamental limitation of this approach, and it is important to be aware of this when interpreting the results of fairness analyses.
+
+% TODO: use = 1
 

### 2024-12-11 paper/paper.tex
progress

@@
 %% allowing the author to define a "short title" to be used in page headers.
-\title{Quantitative Auditing of AI Fairness with Differentially Private Synthetic Data}
+\title{Quantitative Auditing of AI Fairness with differentially private Synthetic Data}
 
@@
 Ensuring fairness in AI systems is crucial, but auditing these systems often requires sensitive data, which raises security and privacy concerns.
-To address this, we introduce a framework that utilizes Differentially Private synthetic data for fairness evaluations.
+To address this, we introduce a framework that utilizes differentially private synthetic data for fairness evaluations.
 This approach allows auditors to assess AI systems without exposing sensitive information.
@@
          <concept_id>10002978.10002991.10002995</concept_id>
-         <concept_desc>Security and privacy~Privacy-preserving protocols</concept_desc>
+         <concept_desc>Security and privacy~privacy-preserving protocols</concept_desc>
          <concept_significance>300</concept_significance>
@@
 \ccsdesc[300]{Computing methodologies~Artificial intelligence}
-\ccsdesc[300]{Security and privacy~Privacy-preserving protocols}
+\ccsdesc[300]{Security and privacy~privacy-preserving protocols}
 \ccsdesc[300]{Information systems~Information systems applications}
@@
 
-% TODO: lowercase Diff
-
 % fairness
@@
 
-% TODO: ai woulld be found to be unfair by 3rd party. example: compas
+Auditing can evaluate the fairness of AI systems, sometimes revealing cases of unfairness in them.
+For example, investigative journalists at ProPublica found that the COMPAS system, which is used to predict recidivism in the criminal justice system in the United States, is biased against certain demographic groups.
+This highlights the need for fairness auditing conducted by third parties.
 
@@
 Analysis on real data runs the risk of data inference attacks, where confidential information may be deduced from seemingly harmless or aggregated data.
-Various technologies have been developed to mitigate these risks, such as Differential Privacy, where the idea is that whether or not any individual is in a dataset has a limited impact.
+Various technologies have been developed to mitigate these risks, such as differential privacy, where the idea is that whether or not any individual is in a dataset has a limited impact.
 
-% TODO: to mitigate use synthetic data. principals of this
+To mitigate these risks, the use of synthetic data has been proposed.
+Synthetic data are fake data that is artificially generated from real data.
+The principle of this technology is to preserve some statistical properties of the real data while protecting the privacy of the individuals in the real data.
+Among the generation techniques, differentially private synthetic data offers a way to investigate the data properties under differential privacy guarantees.
 
@@
 
-We propose a novel auditing framework that leverages Differentially Private synthetic data to evaluate the fairness of AI systems.
+We propose a novel auditing framework that leverages differentially private synthetic data to evaluate the fairness of AI systems.
 Our framework lets the auditors assess the fairness of AI systems without exposing sensitive information.
-Differentially Private synthetic data is a technique that generates synthetic data from real data that preserves some statistical properties of the real data while ensuring Differential Privacy.
+Differentially private synthetic data is a technique that generates synthetic data from real data that preserves some statistical properties of the real data while ensuring differential privacy.
 This technology enables auditing without exposing sensitive information.
@@
 
-Our work examines the capabilities of existing Differentially Private synthetic data generation technologies in preserving fairness properties.
-Through empirical experiments on multiple real datasets, we aim to determine the effectiveness of Differentially Private synthetic data in this respect.
+Our work examines the capabilities of existing differentially private synthetic data generation technologies in preserving fairness properties.
+Through empirical experiments on multiple real datasets, we aim to determine the effectiveness of differentially private synthetic data in this respect.
 
@@
 
-Differential Privacy has risen to become the standard of privacy protection in many data analyses\cite{jiang2021applications}.
+Differential privacy has risen to become the standard of privacy protection in many data analyses\cite{jiang2021applications}.
 It offers a formal framework for quantifying privacy guarantees when releasing information derived from sensitive data\cite{dwork2006calibrating,dwork2014algorithmic}.
-We use Differential Privacy in this work to protect the privacy of individuals in the data in our auditing framework.
+We use differential privacy in this work to protect the privacy of individuals in the data in our auditing framework.
 
-Different flavors of Differential Privacy have been proposed over the years\cite{desfontaines2019sok}, such as Gaussian Differential Privacy\cite{dong2022gaussian}, Pufferfish Differential Privacy\cite{kifer2012rigorous}, Bayesian Differential Privacy\cite{triastcyn2020bayesian}, and R\'enyi Differential Privacy\cite{mironov2017renyi}.
-We consider R\'enyi Differential Privacy specifically in this work.
+Different flavors of differential privacy have been proposed over the years\cite{desfontaines2019sok}, such as Gaussian differential privacy\cite{dong2022gaussian}, Pufferfish differential privacy\cite{kifer2012rigorous}, Bayesian differential privacy\cite{triastcyn2020bayesian}, and R\'enyi differential privacy\cite{mironov2017renyi}.
+We consider R\'enyi differential privacy specifically in this work.
 
@@
 
-The generation of synthetic data\cite{raghunathan2021synthetic,lu2023machine} under Differential Privacy constraints allows for data sharing without compromising privacy\cite{tao2021benchmarking}.
-There have been several techniques developed for Differentially Private synthetic data generation\cite{rosenblatt2020differentially,fan2020relational,bowen2019comparative,bowen2020comparative,arnold2020really,xu2019modeling} in recent years.
-We use the technique that won the 2018 NIST Differential Privacy Synthetic Data Challenge competition\cite{mckenna2021winning}.
+The generation of synthetic data\cite{raghunathan2021synthetic,lu2023machine} under differential privacy constraints allows for data sharing without compromising privacy\cite{tao2021benchmarking}.
+There have been several techniques developed for differentially private synthetic data generation\cite{rosenblatt2020differentially,fan2020relational,bowen2019comparative,bowen2020comparative,arnold2020really,xu2019modeling} in recent years.
+We use the technique that won the 2018 NIST differential privacy Synthetic Data Challenge competition\cite{mckenna2021winning}.
 
@@
 
-Let $X,Y$ be discrete random variables.
-Their \emph{mutual information} is $\mi{X}{Y} := \entropy{X} + \entropy{Y} - \entropy{X,Y}$.
-It quantifies the level of dependence between $X$ and $Y$.
-By definition\cite{427884}, the joint entropy is greater than or equal to the marginal entropies $\entropy{X,Y} \geq \text{max}(\entropy{X},\entropy{Y})$.
+Let $X,Y$ be discrete random variables. Their \emph{mutual information} is $\mi{X}{Y} := \entropy{X} + \entropy{Y} - \entropy{X,Y}$. It quantifies the level of dependence between $X$ and $Y$.
+% By definition\cite{427884}, the joint entropy is greater than or equal to the marginal entropies $\entropy{X,Y} \geq \text{max}(\entropy{X},\entropy{Y})$.
 Hence, we have an upper bound of mutual information $\mi{X}{Y} \leq \text{min}(\entropy{X}, \entropy{Y})$.
@@
 $Y, \hat{Y}, S$ are binary.
-For non-binary prediction, such as a score, we use $\hat{V}$.
 
@@
 
-% TODO: remove unconsidered
-
-% TODO: rename equalized odds 1,2
-
 \begin{table*}[h]
@@
 \label{tab:measures}
-\begin{tabular}{llc}
+\begin{tabular}{lll}
 \toprule
@@
 % & Conditional Statistical Parity & $\abs{P[\hat{Y} = 1 | S = 1, L = l] - P[\hat{Y} = 1 | S \neq 1, L = l]} \leq \epsilon$ \\
-% & Mean Difference & $\abs{E[\hat{Y}|S = 1] - E[\hat{Y}|S \neq 1]} \leq \epsilon$ \\
+% & Mean difference & $\abs{E[\hat{Y}|S = 1] - E[\hat{Y}|S \neq 1]} \leq \epsilon$ \\
 \multirow{2}{*}{Separation}
-& \multirow{2}{*}{Equalized Odds} & $\abs{P[\hat{Y} = 1 | S = 1, Y = 0] - P[\hat{Y} = 1 | S \neq 1, Y = 0]} \leq \epsilon$ \\
-& & $\abs{P[\hat{Y} = 1 | S = 1, Y = 1] - P[\hat{Y} = 1 | S \neq 1, Y = 1]} \leq \epsilon$ \\
+& \multirow{1}{*}{Equalized Odds (False Positive)} & $\abs{P[\hat{Y} = 1 | S = 1, Y = 0] - P[\hat{Y} = 1 | S \neq 1, Y = 0]} \leq \epsilon$ \\
+& \multirow{1}{*}{Equalized Odds (True Positive)} & $\abs{P[\hat{Y} = 1 | S = 1, Y = 1] - P[\hat{Y} = 1 | S \neq 1, Y = 1]} \leq \epsilon$ \\
 % & Equal Opportunity & $\abs{P[\hat{Y} = 1 | S = 1, Y = 1] - P[\hat{Y} = 1 | S \neq 1, Y = 1]} \leq \epsilon$ \\
@@
 \multirow{2}{*}{Sufficiency}
-& \multirow{2}{*}{Conditional Use Accuracy Equality} & $\abs{P[Y = 1 | S = 1, \hat{Y} = 1] - P[Y = 1 | S \neq 1, \hat{Y} = 1]} \leq \epsilon$ \\
-& & $\abs{P[Y = 0 | S = 1, \hat{Y} = 0] - P[Y = 0 | S \neq 1, \hat{Y} = 0]} \leq \epsilon$ \\
+& \multirow{1}{*}{Conditional Use Accuracy Equality (True Positive)} & $\abs{P[Y = 1 | S = 1, \hat{Y} = 1] - P[Y = 1 | S \neq 1, \hat{Y} = 1]} \leq \epsilon$ \\
+& \multirow{1}{*}{Conditional Use Accuracy Equality (True Negative)} & $\abs{P[Y = 0 | S = 1, \hat{Y} = 0] - P[Y = 0 | S \neq 1, \hat{Y} = 0]} \leq \epsilon$ \\
 % & Predictive Parity & $\abs{P[Y = 1 | S = 1, \hat{Y} = 1] - P[Y = 1 | S \neq 1, \hat{Y} = 1]} \leq \epsilon$ \\
@@
 
-\subsection{R\'enyi Differential Privacy}
+\subsection{R\'enyi differential privacy}
 
-% \begin{definition}[Differential Privacy (DP) \cite{dwork2006calibrating,dwork2014algorithmic,mckenna2021winning}]\label{def:rdp}
+% \begin{definition}[differential privacy (DP) \cite{dwork2006calibrating,dwork2014algorithmic,mckenna2021winning}]\label{def:rdp}
 % A randomized mechanism $M$ satisfies $(\epsilon,\delta)$-DP if, for all databases $\db_1,\db_2$ that differ in exactly one row and for all subsets $S$ of $R$, we have
@@
 Let $\db_1,\db_2$ be two databases.
-They are \emph{neighbors}, denoted $\db_1 \sim \db_2$, if $\abs{\mathcal{R}_{\db_1} \Delta \mathcal{R}_{\db_2}} \in \set{1,2}$ where $\Delta$ denotes symmetric difference; that is, either one database contains an extra row, or both databases have all but one row in common.
+They are \emph{neighbors}, denoted $\db_1 \sim \db_2$, if $\abs{\mathcal{R}_{\db_1} \Delta \mathcal{R}_{\db_2}} = 1$ where $\Delta$ denotes symmetric difference; that is, one database contains an extra row than the other.
 In other words, they differ in exactly one row.
@@
 
-The task of Differentially Private synthetic data\cite{Ullman2022,McKenna2022,NIST_Differentially_Private_Synthetic_Data,YouTube_Differentially_Private_Synthetic_Data} is, given a database $\db$, adding some noise to marginals of $\db$ such that it satisfies some Differential Privacy guarantees and outputting another database $\db'$, such that the $L^1$-norm errors between marginals of $\db$ and $\db'$ is small; that is, their marginals $\mu_{\db},\mu_{\db'}$ are similar.
+The task of differentially private synthetic data\cite{Ullman2022,McKenna2022,NIST_Differentially_Private_Synthetic_Data,YouTube_Differentially_Private_Synthetic_Data} is, given a database $\db$, adding some noise to marginals of $\db$ such that it satisfies some differential privacy guarantees and outputting another database $\db'$, such that the $L^1$-norm errors between marginals of $\db$ and $\db'$ is small; that is, their marginals $\mu_{\db},\mu_{\db'}$ are similar.
 
@@
 \caption{Marginal of original data.}
-\begin{tabular}{cc}
+\begin{tabular}{lr}
 \toprule
@@
 \caption{Marginal of synthetic data.}
-\begin{tabular}{cc}
+\begin{tabular}{lr}
 \toprule
@@
 
-% TODO: add a overarching example for methodologies
-
-We employed the tools of the winner of the 2018 NIST Differential Privacy Synthetic Data Challenge competition\cite{NIST2018} by \cite{nist_ryan_2018,McKenna_Private-PGM_2021,mckenna2021winning,mckenna2019graphical} and the fairness checker tool from our previous research\cite{yuan2024ensuring}.
+We employed the tools of the winner of the 2018 NIST differential privacy Synthetic Data Challenge competition\cite{NIST2018} by \cite{nist_ryan_2018,McKenna_private-PGM_2021,mckenna2021winning,mckenna2019graphical} and the fairness checker tool from our previous research\cite{yuan2024ensuring}.
 
 This research is conducted in Python Jupyter notebooks and is publicly available.
+
+We shall illustrate the workflow of our methodology with an example of the COMPAS dataset, which contains attributes such as sex and race with the prediction target attribute being recidivism.
 
@@
 The synthesis framework is three-fold, namely, select-measure-generate\cite{McKenna2022,YouTube_Differentially_Private_Synthetic_Data}.
-We first select the important marginals to preserve, measure them by adding Differential Privacy noise, and then generate synthetic data.
+We first select the important marginals to preserve, measure them by adding differential privacy noise, and then generate synthetic data.
 
@@
 To circumvent this complexity explosion, instead, \cite{mckenna2021winning} devised a technique where the mutual information of all the database attribute pairs is calculated, and then a maximum spanning tree is identified with edge weights being the mutual information to obtain a skeleton tree-shaped Markov random field.
+The marginals are then selected based on the edges of this tree.
+
+In the COMPAS example, we may select the marginal (sex,race).
 
@@
 In addition, they would add some edges based on some sophisticated heuristics tailored to that particular dataset.
-Meanwhile, his other apporach where the auditor does access the real dataset does not fit our framework.
+
+We do not consider these additional heuristics for the generality of our approach. Meanwhile, his other apporach where the auditor does access the real dataset does not fit our framework.
+
+While synthetic data generation methods often leverage domain knowledge to improve accuracy, we chose to employ a vanilla approach with only the maximum spanning tree method without incorporating additional heuristics.
+This decision was made due to two main factors: first, the need for more specific domain knowledge about the dataset makes it difficult to identify meaningful dependencies; second, prediction targets may differ from dataset to dataset, which means that tailored heuristics could not be effectively generalized.
+By avoiding dataset-specific adjustments, our method remains general and applicable to a wide range of datasets.
+Furthermore, the bare tree structure makes the method more tractable and computationally efficient.
 
@@
 
-% TODO:
-% for synth to good : depend on domain knowledge, tractibility
-% synth algos use dependencies
-% we DO NOT use this. we do vanilla
-% experiment didnt developed heuristics:
-% 1. lack of domain knowledge
-% 2. different prediction target. cannot tailor a priori
-
 For the measure step, we followed the examples provided in the tool's repository.
 Gaussian noises are added to the selected marginals.
-Half of the privacy budget is spent on all 1-way marginals and the other half on the selected cliques.
+Half of the privacy budget $\epsilon = 1$ is spent on all 1-way marginals and the other half on the selected cliques.
 These marginals are then fed to the tool to fit the Markov random field.
 By \cite{mckenna2021winning}, this procedure satisfies $(\alpha,\frac{\alpha}{2 \sigma^2})$-RDP for all $\alpha \geq 1$.
+
+In the COMPAS example, the selected the marginals are perturbed by Gaussian noise, as shown in Table~\ref{tab:marginal-perturbed}.
+
+\begin{table}[h]
+\caption{Example marginals.}
+\label{tab:marginal-perturbed}
+\centering
+\begin{subtable}[t]{0.45\linewidth}
+\centering
+\caption{Original marginal.}
+\begin{tabular}{lr}
+\toprule
+Attributes & Count \\
+\midrule
+Female,African-American & 1537 \\
+Female,Asian & 8 \\
+Female,Caucasian & 1465 \\
+Female,Hispanic & 215 \\
+Female,Native American & 15 \\
+Female,Other & 143 \\
+Male,African-American & 8254 \\
+Male,Asian & 63 \\
+Male,Caucasian & 4621 \\
+Male,Hispanic & 1236 \\
+Male,Native American & 42 \\
+Male,Other & 717 \\
+\bottomrule
+\end{tabular}
+\end{subtable}
+\begin{subtable}[t]{0.45\linewidth}
+\centering
+\caption{Perturbed marginal.}
+\begin{tabular}{lr}
+\toprule
+Attributes & Count \\
+\midrule
+Female,African-American & 1545.7885 \\
+Female,Asian & 4.3236 \\
+Female,Caucasian & 1444.7303 \\
+Female,Hispanic & 208.2250 \\
+Female,Native American & 26.7479 \\
+Female,Other & 150.8175 \\
+Male,African-American & 8296.6274 \\
+Male,Asian & 92.1107 \\
+Male,Caucasian & 4643.0108 \\
+Male,Hispanic & 1274.0831 \\
+Male,Native American & 28.9542 \\
+Male,Other & 710.3473 \\
+\bottomrule
+\end{tabular}
+\end{subtable}
+\end{table}
 
@@
 
-For example, if the sensitive attribute is sex and the protected group is female, the protected group predicate would be $S := r(sex) = Female$.
+In the COMPAS example, if the sensitive attribute is sex and the protected group is female, the protected group predicate would be $S := r(sex) = Female$.
 This can be easily implemented in Python as a comparison function.
@@
 
-% TODO: move this to their respective subsection
-
-% TODO: reiterate methodologies
-
 We looked at several publicly available datasets, such as Adult\cite{adult_2,Kaggle_Adult_Census_Income}, COMPAS\cite{larson2016propublica,Kaggle_COMPAS_Dataset}, and Diabetes\cite{diabetes_34,Kaggle_Diabetes_Prediction}.
-The Adult dataset comes from the 1994 census in the United States and contains about 30000 individuals.
-The COMPAS dataset comes from an investigative report by ProPublica of the COMPAS criminal recidivism assessment system and contains about 7000 individuals.
-The Diabetes dataset comes from the hospital readmission data published in the 1994 AI in Medicine journal and contains about 100000 individuals.
-Since these datasets all have binary outcomes, we did not consider the case of non-binary outcomes in the experiments.
+These datasets are known to have fairness issues\cite{pessach2022review}.
 
 The fairness checker evaluates datasets based on multiple fairness metrics, such as demographic parity and equalized odds.
-These metrics are computed on some sensitive attributes, predicted outcomes, and ground truths.
-Examples of sensitive attributes are race and sex.
-Examples of predicted outcomes and ground truths are loan approval and criminal recidivism.
-
 By comparing these measures between the synthetic and original datasets, we aim to ensure that the synthetic data preserves the fairness properties of the original data.
@@
 The dataset is first processed so it can be fed into the synthetic data generator.
-Some marginals are selected as described in the Section~\ref{sec:method}, and the synthetic data generator model is fitted to the original data according to the marginals.
-Then the generator is run multiple times to obtain multiple sets of synthetic data.
+Some marginals are selected according to their mutual information, as described in the Section~\ref{sec:method}, and the synthetic data generator model is fitted to the original data according to the selected marginals.
+Then the generator is run 100 times to obtain 100 sets of synthetic data.
 
@@
 
-Several AI models and both the original dataset and the rounds of synthetic datasets are fed to the fairness checker.
+The AI models and both the original dataset and synthetic datasets are then fed to the fairness checker.
 Sensitive attributes are identified based on manual examination with common sense or by referring to \cite{pessach2022review}.
-Then, all applicable fairness measures are computed using the checker for both the original and the synthetic.
-
-Finally, we analyze the discrepancies between the fairness properties of the original and the synthetic by calculating the difference of their perspective fairness measure values.
-The average of the differences serves as a summary of the analysis.
+Then, applicable fairness measures are computed using the checker for both the original and the synthetic.
 
@@
 
-% TODO: dont mention shape of graph
+The Adult\cite{adult_2,Kaggle_Adult_Census_Income} dataset comes from the 1994 census in the United States and contains about 30000 individuals.
+The dataset has 14 attributes, such as sex, age, and education.
+The task is to predict whether an individual earns more than \$50,000 a year.
+We set the sensitive attribute as sex and the protected group as female.
+The results are shown in Table~\ref{tab:adult_score}.
 
-For the Adult income dataset, the shape of the maximum spanning tree is very shallow, almost resembling a star; it has one internal node and all but one of the leaves have a depth of one.
+% For the Adult income dataset, the shape of the maximum spanning tree is very shallow, almost resembling a star; it has one internal node and all but one of the leaves have a depth of one.
 After introducing edges according to our heuristic, we observed an increase in the pairwise edges of the leaves, forming many 3-cliques and two 4-cliques.
 The resulting graph is shown in Figure~\ref{fig:adult_mst}.
-
-Marginals based on this graph are then passed to the synthetic data generator for model fitting.
-
-After generating ten rounds of synthetic data and passing them to the checker, their fairness measure values are averaged.
-Then, we compare them against the values of the original data.
-The results are shown in Table~\ref{tab:adult_score}.
 
@@
     Fairness measures experiment results of the Adult dataset.
-    With heuristic, average difference is $0.0787$, and fit time is 924m15s.
-    Without heuristic, average difference is $0.0775$, and fit time is 17m1s.
+    % With heuristic, average difference is $0.0787$, and fit time is 924m15s.
+    Average difference is $0.0775$, and fit time is 17m1s.
 }
+% \label{tab:adult_score}
+% \begin{tabular}{ccccccc}
+% \toprule
+% \textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{difference} & \textbf{Synthetic(No Heuristic)} & \textbf{difference(No Heuristic)} \\
+% \midrule
+% Demographic Parity  & 0.1933 & 0.1079 & 0.0853 & 0.0114 & 0.1818 \\
+% Overall Accuracy Eqaulity   & 0.0250 & 0.1399 & 0.1149 & 0.0169 & 0.0080 \\
+% Equalized Odds (False Positive)    & 0.0175 & 0.0870 & 0.0695 & 0.0060 & 0.0115 \\
+% Equalized Odds (True Positive)    & 0.0114 & 0.0622 & 0.0508 & 0.0303 & 0.0189 \\
+% CU Accuracy Equality (True Positive) & 0.1941 & 0.1466 & 0.0474 & 0.0315 & 0.1626 \\
+% CU Accuracy Equality (True Negative) & 0.1102 & 0.1450 & 0.0348 & 0.0299 & 0.0803 \\
+% \bottomrule
+% \end{tabular}
+% \end{table}
+
 \label{tab:adult_score}
-\begin{tabular}{ccccccc}
+\begin{tabular}{llll}
 \toprule
-\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} & \textbf{Synthetic(No Heuristic)} & \textbf{Difference(No Heuristic)} \\
+\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} \\
 \midrule
-Demographic Parity  & 0.1933 & 0.1079 & 0.0853 & 0.0114 & 0.1818 \\
-Accuracy Eqaulity   & 0.0250 & 0.1399 & 0.1149 & 0.0169 & 0.0080 \\
-Equalized Odds 1    & 0.0175 & 0.0870 & 0.0695 & 0.0060 & 0.0115 \\
-Equalized Odds 2    & 0.0114 & 0.0622 & 0.0508 & 0.0303 & 0.0189 \\
-Accuracy Equality 1 & 0.1941 & 0.1466 & 0.0474 & 0.0315 & 0.1626 \\
-Accuracy Equality 2 & 0.1102 & 0.1450 & 0.0348 & 0.0299 & 0.0803 \\
+Demographic Parity  & 0.1933 & 0.0114 & 0.1818 \\
+Overall Accuracy Eqaulity   & 0.0250 & 0.0169 & 0.0080 \\
+Equalized Odds (False Positive)    & 0.0175 & 0.0060 & 0.0115 \\
+Equalized Odds (True Positive)    & 0.0114 & 0.0303 & 0.0189 \\
+Conditional Use Accuracy Equality (True Positive) & 0.1941 & 0.0315 & 0.1626 \\
+Conditional Use Accuracy Equality (True Negative) & 0.1102 & 0.0299 & 0.0803 \\
 \bottomrule
@@
 
+The COMPAS\cite{larson2016propublica,Kaggle_COMPAS_Dataset} dataset comes from an investigative report by ProPublica of the COMPAS criminal recidivism assessment system and contains about 7000 individuals.
+The dataset has 10 applicable attributes, such sex, age, and priors count.
+The task is to predict whether an individual will re-offend.
+We set the sensitive attribute as sex and the protected group as female.
+The results are shown in Table~\ref{tab:compas_score}.
+
 % For the COMPAS dataset, the initial spanning tree has a long tail, which is not surprising because, upon closer inspection, they all are related to the original COMPAS risk scores.
@@
 The resulting graph is shown in Figure~\ref{fig:compas_mst}.
-
-% Marginals of this graph are then too passed to the synthetic data generator for fitting.
-
-% We ran the same workflow as adult dataset for the COMPAS dataset. The comparison results are shown in Table~\ref{tab:compas_score}.
 
@@
     Fairness measures experiment results of the COMPAS dataset.
-    With heuristic, average difference is $0.0750$, and fit time is 27m33s.
-    Without heuristic, average difference is $0.0727$, and fit time is 33s.
+    % With heuristic, average difference is $0.0750$, and fit time is 27m33s.
+    Average difference is $0.0727$, and fit time is 33s.
 }
 \label{tab:compas_score}
-\begin{tabular}{cccccc}
+\begin{tabular}{llll}
 \toprule
-\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} & \textbf{Synthetic(No Heuristic)} & \textbf{Difference(No Heuristic)} \\
+\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} \\
 \midrule
-Demographic Parity  & 0.1310 & 0.0980 & 0.0330 & 0.0809 & 0.0501 \\
-Accuracy Eqaulity   & 0.0079 & 0.0129 & 0.0050 & 0.0146 & 0.0067 \\
-Equalized Odds 1    & 0.0249 & 0.0936 & 0.0687 & 0.0802 & 0.0553 \\
-Equalized Odds 2    & 0.0177 & 0.1016 & 0.0838 & 0.0825 & 0.0648 \\
-Accuracy Equality 1 & 0.1709 & 0.0505 & 0.1203 & 0.0551 & 0.1157 \\
-Accuracy Equality 2 & 0.1695 & 0.0303 & 0.1392 & 0.0256 & 0.1439 \\
+Demographic Parity  & 0.1310 & 0.0809 & 0.0501 \\
+Overall Accuracy Eqaulity   & 0.0079 & 0.0146 & 0.0067 \\
+Equalized Odds (False Positive)    & 0.0249 & 0.0802 & 0.0553 \\
+Equalized Odds (True Positive)    & 0.0177 & 0.0825 & 0.0648 \\
+Conditional Use Accuracy Equality (True Positive) & 0.1709 & 0.0551 & 0.1157 \\
+Conditional Use Accuracy Equality (True Negative) & 0.1695 & 0.0256 & 0.1439 \\
 \bottomrule
@@
 
+The Diabetes\cite{diabetes_34,Kaggle_Diabetes_Prediction} dataset comes from the hospital readmission data published in the 1994 AI in Medicine journal and contains about 100000 individuals.
+The dataset has 8 attributes, such as gender, age, and smoking history.
+The task is to predict whether an individual will be readmitted.
+We set the sensitive attribute as gender and the protected group as female.
+The results are shown in Table~\ref{tab:diabetes_score}.
+
 % The tree grown from the diabetes dataset did not appear to have any particular characteristics.
@@
 The resulting graph is shown in Figure~\ref{fig:diabetes_mst}.
-
-% The same process is conducted to fit the synthetic data generator model.
-
-% The same workflow was done as on previous datasets. The comparison results are shown in Table~\ref{tab:diabetes_score}.
 
@@
     Fairness measures experiment results of the Diabetes dataset.
-    With heuristic, average difference is $0.0067$, and fit time is 1m44s.
-    Without heuristic, average difference is $0.0078$, and fit time is 1m24s.
+    % With heuristic, average difference is $0.0067$, and fit time is 1m44s.
+    Average difference is $0.0078$, and fit time is 1m24s.
 }
 \label{tab:diabetes_score}
-\begin{tabular}{cccccc}
+\begin{tabular}{llll}
 \toprule
-\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} & \textbf{Synthetic(No Heuristic)} & \textbf{Difference(No Heuristic)} \\
+\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} \\
 \midrule
-Demographic Parity  & 0.0135 & 0.0038 & 0.0096 & 0.0015 & 0.0119 \\
-Accuracy Eqaulity   & 0.0077 & 0.0011 & 0.0065 & 0.0011 & 0.0065 \\
-Equalized Odds 1    & 0.0000 & 0.0006 & 0.0006 & 0.0010 & 0.0010 \\
-Equalized Odds 2    & 0.0086 & 0.0106 & 0.0020 & 0.0094 & 0.0008 \\
-Accuracy Equality 1 & 0.0133 & 0.0090 & 0.0042 & 0.0059 & 0.0074 \\
-Accuracy Equality 2 & 0.0216 & 0.0041 & 0.0175 & 0.0019 & 0.0197 \\
+Demographic Parity  & 0.0135 & 0.0015 & 0.0119 \\
+Overall Accuracy Eqaulity   & 0.0077 & 0.0011 & 0.0065 \\
+Equalized Odds (False Positive)    & 0.0000 & 0.0010 & 0.0010 \\
+Equalized Odds (True Positive)    & 0.0086 & 0.0094 & 0.0008 \\
+Condtional Use Accuracy Equality (True Positive) & 0.0133 & 0.0059 & 0.0074 \\
+Condtional Use Accuracy Equality (True Negative) & 0.0216 & 0.0019 & 0.0197 \\
 \bottomrule

### 2024-12-11 paper/paper.tex
progress

@@
 
-% TODO: add more to intro
-
 % fairness
@@
 
-Let $X \in \mathcal{X}$ be a discrete random variable and $p(x) := \prob{X = x}$.
-Its \emph{marginal Shannon entropy} is $\entropy{X} := -\sum_{x \in \mathcal{X}} p(x) \text{log} p(x)$.
-It quantifies the level of uncertainty of $X$.
-Let $Y \in \mathcal{Y}$ be another discrete random variable.
-Their \emph{joint Shannon entropy} is $\entropy{X,Y} := -\sum_{x \in \mathcal{X}} \sum_{y \in \mathcal{Y}} p(x, y) \text{log} p(x, y)$.
-
-Let $X,Y$ be discrete random variables. Their \emph{mutual information} is $\mi{X}{Y} := \entropy{X} + \entropy{Y} - \entropy{X,Y}$. It quantifies the level of dependence between $X$ and $Y$.
+Let $X \in \mathcal{X},Y \in \mathcal{Y}$ be discrete random variables. Their \emph{mutual information} $\mi{X}{Y}$ is
+\[
+\mi{X}{Y} = \sum_{x \in \mathcal{X}} \sum_{y \in \mathcal{Y}} P_{(X,Y)}(x,y) \text{log} \frac{P_{(X,Y)}(x,y)}{P_X(x)P_Y(y)}
+\]
+where $P_{(X,Y)}$ is the joint probability distribution of $X,Y$ and $P_X,P_Y$ are the marginal probability distributions of $X,Y$ respectively.
+It quantifies the level of dependency between $X$ and $Y$.
 % By definition\cite{427884}, the joint entropy is greater than or equal to the marginal entropies $\entropy{X,Y} \geq \text{max}(\entropy{X},\entropy{Y})$.
@@
 
-% TODO: reiterate intro
+AI systems are widely used in various aspects in our society.
+However, these systems may be biased against certain demographic groups.
+For example, COMPAS, the AI system used in American criminal justice system to predict recidivism, has been found to be biased by ProPublica, a third party media.
 
-% TODO: goal of this framework
+To ensure the fairness of AIs, third-party audits such as this is crucial.
+Auditing can reveal instances of unfairness in AI systems, allowing for corrective actions to be taken.
+We hence advocate for a framework that centers around third-party audits.
 
-Our auditing framework is tripartite. It consists of three parties: the data provider, the model maker, and the third-party auditor.
-
-% TODO: write more about these paragraphs
+Our auditing framework is tripartite. It consists of three parties: the data provider, the model maker, and the third-party auditor. The COMPAS investigation could fit in with this framework.
 
 The data provider is responsible for supplying the raw datasets which should originate from trustworthy sources, such as government agencies like a census bureau.
+In the COMPAS example, the data provider is the government agencies that provide criminal justice data, such as the Broward County Sheriff's Office in Florida.
 
-The model maker develops AI models. These are AI companies or research labs specialized in training and optimizing AI models.
+The model maker develops AI models.
+These are AI companies or research labs specialized in training and optimizing AI models.
+The model maker in the COMPAS example is Northpointe, Inc., the company that developed the COMPAS system.
 
@@
 These may be investigative journalists or regulatory bodies.
+ProPublica is the third-party auditor in the COMPAS example, using quantitative methods to evaluate the fairness of the COMPAS system using Florida's data.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\linewidth]{compas}
+  \caption{Roles of each party in the COMPAS example.}
+  \label{fig:compas}
+  \Description{Roles of each party in the COMPAS example.}
+\end{figure}
+
+% TODO: add compas example in the following
 
@@
 
-In the COMPAS example, we may select the marginal (sex,race).
-
 For the competition, \cite{mckenna2021winning} further manually added certain cliques based on his investigation of the competition dataset.
@@
 In addition, they would add some edges based on some sophisticated heuristics tailored to that particular dataset.
-
-We do not consider these additional heuristics for the generality of our approach. Meanwhile, his other apporach where the auditor does access the real dataset does not fit our framework.
+We do not consider these additional heuristics for the generality of our approach.
+Meanwhile, his other apporach where the auditor does access the real dataset does not fit our framework.
 
@@
 This decision was made due to two main factors: first, the need for more specific domain knowledge about the dataset makes it difficult to identify meaningful dependencies; second, prediction targets may differ from dataset to dataset, which means that tailored heuristics could not be effectively generalized.
-By avoiding dataset-specific adjustments, our method remains general and applicable to a wide range of datasets.
-Furthermore, the bare tree structure makes the method more tractable and computationally efficient.
+By avoiding dataset-specific adjustments, our method remains general and applicable to a wide range of datasets, in addition to being more computatioanlly efficient.
 
@@
 
-In the COMPAS example, the selected the marginals are perturbed by Gaussian noise, as shown in Table~\ref{tab:marginal-perturbed}.
+In the COMPAS example, we may select the marginal (sex,race). This marginal is then perturbed by Gaussian noise, as shown in Table~\ref{tab:marginal-perturbed}.
 
@@
 
-In the COMPAS example, if the sensitive attribute is sex and the protected group is female, the protected group predicate would be $S := r(sex) = Female$.
-This can be easily implemented in Python as a comparison function.
-
 The interpretation of the resulting fairness measure values is dependent on the third-party auditors.
 The auditors may have different thresholds $\epsilon$ for different fairness measures or different AI models.
+
+In the COMPAS example, the sensitive attribute is sex and the protected group is female, the protected group predicate would be $S := r(sex) = Female$; prediction is if a person will re-offend $\hat{Y} := \mathcal{M}_{recid}(r)$ where $M$ is the model's prediction of row $r$; ground truth is whether a person does re-offend $Y := r(recid)$.
+These can be easily implemented in Python as a comparison function.
 
@@
 
-% TODO:
-first list formulas
+% % TODO:
+% first list formulas
 
-count vars
+% count vars
 
-theyre not part of marginals
+% theyre not part of marginals
 
-they cant be computed
+% they cant be computed
 
-we can say less about fairness with these with less info
+% we can say less about fairness with these with less info
 
-auditor need to know theyre aproxing scores
+% auditor need to know theyre aproxing scores
 
-auditor need to keep in mind that these scores are for datasets and we preserve these scores thats it. scores may not be accurate. it doesnt mean its less easy to test fairness
+% auditor need to keep in mind that these scores are for datasets and we preserve these scores thats it. scores may not be accurate. it doesnt mean its less easy to test fairness
 
@@
 
-% TODO:
-it works!
+% % TODO:
+% it works!
 
@@
 
-independence
-\[
-P[\hat{Y} | S] - P[\hat{Y} | \overline{S}]
-= \frac{P[\n{\hat{Y}} \cap \y{S}]}{P[\y{S}]} - \frac{P[\n{\hat{Y}} \cap \y{\overline{S}}]}{P[\y{\overline{S}}]}
-\]
+% independence
+% \[
+% P[\hat{Y} | S] - P[\hat{Y} | \overline{S}]
+% = \frac{P[\n{\hat{Y}} \cap \y{S}]}{P[\y{S}]} - \frac{P[\n{\hat{Y}} \cap \y{\overline{S}}]}{P[\y{\overline{S}}]}
+% \]
 
-separation
-\[
-P[\hat{Y} | S, Y] - P[\hat{Y} | \overline{S}, Y]
-= \frac{P[\n{\hat{Y}} \cap \y{S} \cap \y{Y}]}{P[\y{S} \cap \y{Y}]} - \frac{P[\n{\hat{Y}} \cap \y{\overline{S}} \cap \y{Y}]}{P[\y{\overline{S}} \cap \y{Y}]}
-\]
+% separation
+% \[
+% P[\hat{Y} | S, Y] - P[\hat{Y} | \overline{S}, Y]
+% = \frac{P[\n{\hat{Y}} \cap \y{S} \cap \y{Y}]}{P[\y{S} \cap \y{Y}]} - \frac{P[\n{\hat{Y}} \cap \y{\overline{S}} \cap \y{Y}]}{P[\y{\overline{S}} \cap \y{Y}]}
+% \]
 
-sufficiency
-\[
-P[Y | S, \hat{Y}] - P[Y | \overline{S}, \hat{Y}]
-= \frac{P[\y{Y} \cap \y{S} \cap \n{\hat{Y}}]}{P[\y{S} \cap \n{\hat{Y}}]} - \frac{P[\y{Y} \cap \y{\overline{S}} \cap \n{\hat{Y}}]}{P[\y{\overline{S}} \cap \n{\hat{Y}}]}
-\]
+% sufficiency
+% \[
+% P[Y | S, \hat{Y}] - P[Y | \overline{S}, \hat{Y}]
+% = \frac{P[\y{Y} \cap \y{S} \cap \n{\hat{Y}}]}{P[\y{S} \cap \n{\hat{Y}}]} - \frac{P[\y{Y} \cap \y{\overline{S}} \cap \n{\hat{Y}}]}{P[\y{\overline{S}} \cap \n{\hat{Y}}]}
+% \]
 
-accuracy equality
-\[
-P[Y = \hat{Y} | {S} ] - P[Y = \hat{Y} | \overline{S}]
-= \frac{P[\y{Y} = \n{\hat{Y}} \cap \y{S}]}{P[\y{S}]} - \frac{P[\y{Y} = \n{\hat{Y}} \cap \y{\overline{S}}]}{P[\y{\overline{S}}]}
-\]
+% accuracy equality
+% \[
+% P[Y = \hat{Y} | {S} ] - P[Y = \hat{Y} | \overline{S}]
+% = \frac{P[\y{Y} = \n{\hat{Y}} \cap \y{S}]}{P[\y{S}]} - \frac{P[\y{Y} = \n{\hat{Y}} \cap \y{\overline{S}}]}{P[\y{\overline{S}}]}
+% \]
 

### 2024-12-11 paper/paper.tex
progress

@@
 
-% TODO: add compas example in the following
-
 In the framework of our previous work\cite{yuan2024ensuring}, after obtaining real data from the data provider, the 3rd party auditor holds onto the real data for performing fairness audits, and it supposedly retains it indefinitely for the possibility of any future audits.
@@
 
-For security, it creates a point of vulnerability of unauthorized access, and the auditor is now a target of data security attacks.
+For security, it creates a point of vulnerability to unauthorized access, and the auditor is now a target of data security attacks.
 The auditor may not have the necessary resources to defend against these threats.
 A breach at the auditor's end could result in compromises of individuals' sensitive information.
+In the COMPAS example, had the data not been public already, ProPublica may be targeted by hackers to access the sensitive criminal justice data.
 
 As for privacy, on the other hand, it introduces risks of information leakage.
-Releasings of analyses on real data may inadvertently reveal sensitive information by data inference attacks.
+Releasing analyses of real data may inadvertently reveal sensitive information through data inference attacks.
 Attackers can exploit data patterns in outputs or combine outputs with external data to infer sensitive information.
+In the COMPAS example, had the data not been public already, their analyses may inadvertently reveal the identities of individuals in the criminal justice system.
 

### 2024-12-14 paper/paper.tex
minor

@@
 %% allowing the author to define a "short title" to be used in page headers.
-\title{Quantitative Auditing of AI Fairness with differentially private Synthetic Data}
+\title{Quantitative Auditing of AI Fairness with Differentially Private Synthetic Data}
 
@@
 
-In the COMPAS example, the sensitive attribute is sex and the protected group is female, the protected group predicate would be $S := r(sex) = Female$; prediction is if a person will re-offend $\hat{Y} := \mathcal{M}_{recid}(r)$ where $M$ is the model's prediction of row $r$; ground truth is whether a person does re-offend $Y := r(recid)$.
+In the COMPAS example, the sensitive attribute is sex and the protected group is female, the protected group predicate would be $S := r(sex) = Female$; prediction is if a person will re-offend $\hat{Y} := \mathcal{M}_{recid}(r)$ where $\mathcal{M}$ is the model's prediction of row $r$; ground truth is whether a person does re-offend $Y := r(recid)$.
 These can be easily implemented in Python as a comparison function.

### 2024-12-15 paper/paper.tex
Evaluation

@@
 \documentclass[manuscript,screen,review,anonymous]{acmart}
-\usepackage{xcolor}
-\usepackage{mathtools}
 % \documentclass[acmsmall,sigconf]{acmart}
@@
 
+\usepackage{xcolor}
 \usepackage{mathtools}
@@
 \label{tab:adult_score}
-\begin{tabular}{llll}
+\begin{tabular}{lccc}
 \toprule
@@
 \label{tab:compas_score}
-\begin{tabular}{llll}
+\begin{tabular}{lccc}
 \toprule
@@
 \label{tab:diabetes_score}
-\begin{tabular}{llll}
+\begin{tabular}{lccc}
 \toprule
@@
 
-% % TODO:
-% first list formulas
+Before we delve into the results, we must first understand the nature of the fairness measures.
+The fairness measures are defined assuming all the information is readily available.
+This, however, might cause trouble for synthetic data, as they can only work with the information at hand.
 
-% count vars
-
-% theyre not part of marginals
-
-% they cant be computed
-
-% we can say less about fairness with these with less info
-
-% auditor need to know theyre aproxing scores
-
-% auditor need to keep in mind that these scores are for datasets and we preserve these scores thats it. scores may not be accurate. it doesnt mean its less easy to test fairness
-
-\subsection{Positive Results}
-
-% % TODO:
-% it works!
-
-% Our experiments showed that synthetic data generally preserves the fairness properties with a reasonable degree of accuracy.
-The average of the differences between the fairness measure values of the original and synthetic datasets is below 0.1 for all datasets.
-This indicates that synthetic data is a good approximation of the original data in terms of fairness.
-
-% For the adult dataset, the average difference was 0.0431, suggesting a close match between the synthetic and the original data in terms of fairness measures.
-For the diabetes dataset, the average difference was 0.031, which is even lower.
-Even in the case of the COMPAS dataset, which had a higher value, it was still within an acceptable range at 0.069.
-
-% In particular, both the independence and separation measures showed low errors across all datasets, with the differences of all of them below 0.1.
-On the other hand, results of accuracy equality also showed low errors, with the differences of one of them as low as 0.005.
-
-% This demonstrated that synthetic data can accurately reflect the fairness properties of the original data.
-Therefore, fairness analyses performed on synthetic data will yield results consistent with those on the original data.
-
-\subsection{Negative Results}
-
-% The experiments also revealed some limitations of this approach.
-In particular, the sufficiency measure showed higher errors compared to other measures.
-For example, in the COMPAS dataset, the sufficiency measure had an error difference as high as 0.141, while other measures had errors below 0.1.
-
-% By close examination of our scenario, we can observe the following: of the three variables, $(\hat{Y},Y,S)$, two of them, namely $(Y,S)$, are both readily available in the original data.
+By close examination of our scenario, we can observe the following: of the three variables, $(\hat{Y},Y,S)$, two of them, namely $(Y,S)$, are both readily available in the original data.
 In contrast, $\hat{Y}$ is only available in the output of the given AI model, which cannot be captured by the synthetic data at the time of generation.
 
-% Referring back to the definition of the fairness measures, we can see the following: separation is concerned with the form $P[\hat{Y} | S, Y] = \frac{P[\hat{Y} \cap S \cap Y]}{P[{S} \cap Y]}$, and sufficiency is concerned with the form $P[Y | S, \hat{Y}] = \frac{P[Y \cap S \cap \hat{Y}]}{P[{S} \cap \hat{Y}]}$.
-
-% expand all defs and count the nums of avail vars
-
-% This explains why sufficiency measures could have higher errors compared to separation because synthetic data have less information about them.
-While only one variable is missing in the numerator for separation, one more variable is missing in the denominator for sufficiency.
-
-% Therefore, it is harder to approximate sufficiency measures on synthetic data.
-This is a fundamental limitation of this approach, and it is important to be aware of this when interpreting the results of fairness analyses.
-
-% TODO: use = 1
+Let us inspect the definitions of the fairness measures one by one by expanding them by the definition of conditional probability and coloring them according to whether they are in the original data or not; we will color the variables that are in the original data green and those not red.
 
@@
 
-% independence
-% \[
-% P[\hat{Y} | S] - P[\hat{Y} | \overline{S}]
-% = \frac{P[\n{\hat{Y}} \cap \y{S}]}{P[\y{S}]} - \frac{P[\n{\hat{Y}} \cap \y{\overline{S}}]}{P[\y{\overline{S}}]}
-% \]
+For Demographic Parity, we have
+\[
+P[\hat{Y} = 1 | S = 1] - P[\hat{Y} = 1 | S \neq 1]
+= \frac{P[\n{\hat{Y}} = 1 \cap \y{S} = 1]}{P[\y{S} = 1]} - \frac{P[\n{\hat{Y}} = 1 \cap \y{S} \neq 1]}{P[\y{S} \neq 1]}
+\]
 
-% separation
-% \[
-% P[\hat{Y} | S, Y] - P[\hat{Y} | \overline{S}, Y]
-% = \frac{P[\n{\hat{Y}} \cap \y{S} \cap \y{Y}]}{P[\y{S} \cap \y{Y}]} - \frac{P[\n{\hat{Y}} \cap \y{\overline{S}} \cap \y{Y}]}{P[\y{\overline{S}} \cap \y{Y}]}
-% \]
+For Overall Accuracy Equality, we have
+\[
+P[Y = \hat{Y} | {S} = 1 ] - P[Y = \hat{Y} | {S} \neq 1]
+= \frac{P[\y{Y} = \n{\hat{Y}} \cap \y{S} = 1]}{P[\y{S} = 1]} - \frac{P[\y{Y} = \n{\hat{Y}} \cap \y{{S}} \neq 1]}{P[\y{{S}} \neq 1]}
+\]
 
-% sufficiency
-% \[
-% P[Y | S, \hat{Y}] - P[Y | \overline{S}, \hat{Y}]
-% = \frac{P[\y{Y} \cap \y{S} \cap \n{\hat{Y}}]}{P[\y{S} \cap \n{\hat{Y}}]} - \frac{P[\y{Y} \cap \y{\overline{S}} \cap \n{\hat{Y}}]}{P[\y{\overline{S}} \cap \n{\hat{Y}}]}
-% \]
+For Equalized Odds (False Positive), we have
+\[
+P[\hat{Y} = 1 | S = 1, Y = 0] - P[\hat{Y} = 1 | S \neq 1, Y = 0]
+= \frac{P[\n{\hat{Y}} = 1 \cap \y{S} = 1 \cap \y{Y} = 0]}{P[\y{S} = 1 \cap \y{Y} = 0]} - \frac{P[\n{\hat{Y}} = 1 \cap \y{S} \neq 1 \cap \y{Y} = 0]}{P[\y{S} \neq 1 \cap \y{Y} = 0]}
+\]
+Equalized Odds (True Positive) follows the same form as Equalized Odds (False Positive).
 
-% accuracy equality
-% \[
-% P[Y = \hat{Y} | {S} ] - P[Y = \hat{Y} | \overline{S}]
-% = \frac{P[\y{Y} = \n{\hat{Y}} \cap \y{S}]}{P[\y{S}]} - \frac{P[\y{Y} = \n{\hat{Y}} \cap \y{\overline{S}}]}{P[\y{\overline{S}}]}
-% \]
+For Conditional Use Accuracy Equality (True Positive), we have
+\[
+P[Y = 1 | S = 1, \hat{Y} = 1] - P[Y = 1 | S \neq 1, \hat{Y} = 1]
+= \frac{P[\y{Y} = 1 \cap \y{S} = 1 \cap \n{\hat{Y}} = 1]}{P[\y{S} = 1 \cap \n{\hat{Y}} = 1]} - \frac{P[\y{Y} = 1 \cap \y{{S}} \neq 1 \cap \n{\hat{Y}} = 1]}{P[\y{{S}} \neq 1 \cap \n{\hat{Y}} = 1]}
+\]
+Conditional Use Accuracy Equality (True Negative) follows the same form as Conditional Use Accuracy Equality (True Positive).
+
+Now we can count the numbers of available variables in the original data for each fairness measure: Demographic Parity has $\frac{6}{8} = 0.75$; Overall Accuracy Equality has $\frac{4}{6} = 0.6\overline{6}$; Equalized Odds has $\frac{8}{10} = 0.8$; and Conditional Use Accuracy Equality has $\frac{6}{10} = 0.6$.
+
+Hence, we can say less about fairness with the measures with less information, and the measures approximated by synthetic data may be less accurate.
+
+\subsection{Negative Results}
+
+Now, looking at the actual experimental results, first and foremost, across all datasets, we observed that Conditional Use Accuracy Equality did indeed show higher errors than other measures.
+For example, in the COMPAS experiment, both Conditional Use Accuracy Equality measures had an error over 0.1.
+This corroborates our assumption that it is harder to approximate sufficiency measures on synthetic data.
+
+This is a fundamental limitation of this approach, and it is important to be aware of this when interpreting the results of fairness analyses.
+The auditor needs to keep in mind that they are approximating scores, and the scores may not be fully accurate.
+The auditor should be aware that they are approximating fairness.
+
+\subsection{Positive Results}
+
+Although the scores may not be fully accurate, and some measures, due to the nature of their definitions, may be harder to approximate, the results showed that synthetic data generally preserves the fairness properties of the original data with a reasonable degree of accuracy.
+
+The average of the differences between the fairness measure values of the original and synthetic datasets is below 0.1 for all datasets.
+This indicates that synthetic data is a good approximation of the original data in terms of fairness.
+
+This demonstrated that synthetic data can, to an extent, accurately reflect the fairness properties of the original data.
+Therefore, fairness analyses performed on synthetic data will yield results mostly consistent with those on the original data.
 

### 2024-12-17 paper/paper.tex
Eval

@@
 
-Let us inspect the definitions of the fairness measures one by one by expanding them by the definition of conditional probability and coloring them according to whether they are in the original data or not; we will color the variables that are in the original data green and those not red.
+Let us inspect the definitions of the fairness measures one by one by expanding them by the definition of conditional probability and marking them according to whether they are in the original data or not; we will box the variables that are not in the original data.
 
@@
 \newcommand{\mathhighlight}[2]{\colorbox{#1}{$\displaystyle #2$}}
-\newcommand{\y}[1]{\mathhighlight{lightgreen}{#1}}
-\newcommand{\n}[1]{\mathhighlight{lightred}{#1}}
+\newcommand{\y}[1]{{#1}}
+\newcommand{\n}[1]{\boxed{#1}}
 
@@
 = \frac{P[\n{\hat{Y}} = 1 \cap \y{S} = 1]}{P[\y{S} = 1]} - \frac{P[\n{\hat{Y}} = 1 \cap \y{S} \neq 1]}{P[\y{S} \neq 1]}
-\]
-
-For Overall Accuracy Equality, we have
-\[
-P[Y = \hat{Y} | {S} = 1 ] - P[Y = \hat{Y} | {S} \neq 1]
-= \frac{P[\y{Y} = \n{\hat{Y}} \cap \y{S} = 1]}{P[\y{S} = 1]} - \frac{P[\y{Y} = \n{\hat{Y}} \cap \y{{S}} \neq 1]}{P[\y{{S}} \neq 1]}
 \]
@@
 
-Now we can count the numbers of available variables in the original data for each fairness measure: Demographic Parity has $\frac{6}{8} = 0.75$; Overall Accuracy Equality has $\frac{4}{6} = 0.6\overline{6}$; Equalized Odds has $\frac{8}{10} = 0.8$; and Conditional Use Accuracy Equality has $\frac{6}{10} = 0.6$.
+For Overall Accuracy Equality, we have
+\[
+P[Y = \hat{Y} | {S} = 1 ] - P[Y = \hat{Y} | {S} \neq 1]
+= \frac{P[\y{Y} = \n{\hat{Y}} \cap \y{S} = 1]}{P[\y{S} = 1]} - \frac{P[\y{Y} = \n{\hat{Y}} \cap \y{{S}} \neq 1]}{P[\y{{S}} \neq 1]}
+\]
 
-Hence, we can say less about fairness with the measures with less information, and the measures approximated by synthetic data may be less accurate.
+Here we observed that, of the measures considered, only Conditional Use Accuracy Equality has boxed variables that are in both the numerator and the denominator.
+This is in contrast to the other measures, which only have one boxed variable in the numerator.
 
-\subsection{Negative Results}
-
-Now, looking at the actual experimental results, first and foremost, across all datasets, we observed that Conditional Use Accuracy Equality did indeed show higher errors than other measures.
-For example, in the COMPAS experiment, both Conditional Use Accuracy Equality measures had an error over 0.1.
-This corroborates our assumption that it is harder to approximate sufficiency measures on synthetic data.
-
-This is a fundamental limitation of this approach, and it is important to be aware of this when interpreting the results of fairness analyses.
-The auditor needs to keep in mind that they are approximating scores, and the scores may not be fully accurate.
-The auditor should be aware that they are approximating fairness.
+We can say less about fairness with the measures with less information, and thus the measures approximated by synthetic data may be less accurate for Conditional Use Accuracy Equality.
 
@@
 
+In addition, further experiments showed that, in an alternative assumption where the auditor has knowledge of $(S,Y)$ and can add the edge $(S,Y)$ to the Markov random field before fitting, the synthesized data would have been more accurate, even lowering the error of Conditional Use Accuracy Equality in the COMPAS example.
+
 This demonstrated that synthetic data can, to an extent, accurately reflect the fairness properties of the original data.
 Therefore, fairness analyses performed on synthetic data will yield results mostly consistent with those on the original data.
+
+Auditors hence gained an approach to auditing AI fairness alternative to the traditional method of using real data.
+When using synthetic data derived from real data, the fairness properties remain meaningful and can still be enough for auditing purposes.
+
+\subsection{Negative Results}
+
+Looking at the actual experimental results, first and foremost, across all datasets, we observed that Conditional Use Accuracy Equality did indeed show higher errors than other measures.
+
+In the Adult experiment, Conditional Use Accuracy Equality (True Positive) has an error of around 0.16.
+In the COMPAS experiment, both Conditional Use Accuracy Equality measures had an error over 0.1.
+In the Diabetes experiment, Conditional Use Accuracy Equality (True Negative) has an error much higher than other measures.
+
+This corroborates our assumption that it is harder to approximate sufficiency measures on synthetic data.
+As there is less information available for the synthesis process, the measures that require more information will be harder to approximate.
+
+Although further experiments showed that linking $(S,Y)$ before fitting can somewhat alleviate this problem, the auditor may not always have the background knowledge to identify them; moreover, this improvement is not always guaranteed.
+
+This is a fundamental limitation of this approach, and it is important to be aware of this when interpreting the results of fairness analyses.
+The auditor needs to keep in mind that they are approximating scores, and the scores may not be fully accurate.
 

### 2024-12-17 paper/paper.tex
Conclusion

@@
 
+In the delicate dialectic of fairness and privacy, auditing AI models with real data can be dangerous.
+Our work explores a new terrain yet to be touched.
+By leveraging differentially private synthetic data, our proposed framework for fairness auditing offers a refuge from the vulnerabilities of using real data.
+
+Empirical trials across multiple datasets reveal that synthetic data derived from real data remain sufficiently intact to serve as instruments of audit.
+However, evaluating the formulas, we also find some measures betray the inherent imperfection of the synthetic approach, and their error margin corroborates our stipulation.
+
+Auditors are, thus, in our new framework, equipped with a new tool that tempers risk at the cost of nuance.
+Synthetic data, imperfect as it is, emerges as a pragmatic ally, preserving enough fairness properties and auditing utility without sacrificing the sanctuary of privacy.
+
 %%

### 2024-12-17 paper/paper.tex
abstract

@@
 \begin{abstract}
-Ensuring fairness in AI systems is crucial, but auditing these systems often requires sensitive data, which raises security and privacy concerns.
-To address this, we introduce a framework that utilizes differentially private synthetic data for fairness evaluations.
-This approach allows auditors to assess AI systems without exposing sensitive information.
+Auditing AI systems often requires sensitive data, raising security and privacy concerns.
+To address this, we proffer a framework that leverages differentially private synthetic data for fairness evaluations.
+This approach enables auditors to assess AI systems without exposing sensitive information.
 Through experiments on datasets like Adult, COMPAS, and Diabetes, we compare fairness metrics of synthetic and real data.
-Our results ...
-(to be continued)
+Our results show that synthetic data accurately reflect the fairness properties of real data to a reasonable extent.
 \end{abstract}

### 2024-12-18 paper/paper.tex
minor

--- 2024-12-17 paper/paper.tex
@@
 \begin{abstract}
-Ensuring fairness in AI systems is crucial, but auditing these systems often requires sensitive data, which raises security and privacy concerns.
-To address this, we introduce a framework that utilizes differentially private synthetic data for fairness evaluations.
-This approach allows auditors to assess AI systems without exposing sensitive information.
-Through experiments on datasets like Adult, COMPAS, and Diabetes, we compare fairness metrics of synthetic and real data.
-Our results ...
-(to be continued)
+Auditing AI systems often requires sensitive data, raising security and privacy concerns.
+To address this, we propose a framework that leverages differentially private synthetic data for fairness evaluations.
+This approach enables auditors to assess AI systems without exposing sensitive information.
+Through experiments on real datasets like Adult, COMPAS, and Diabetes, we compare fairness metrics of synthetic and real data.
+Our results show that synthetic data accurately reflect the fairness properties of real data to a reasonable extent.
 \end{abstract}
@@
 
+Auditing AI systems with real data can be dangerous.
+We proffer a new approach that leverages differentially private synthetic data.
+The proposed framework under such privacy guarantees offers a refuge from the vulnerabilities of using real data.
+
+Despite the fact that some measures' definitions betray the inherent imperfection of synthetic data, the metrics results remain generally consistent with the original data.
+Empirical trials across multiple real-world datasets and real-world models reveal that synthetic data derived from real data sufficiently maintains the fairness properties to serve as instruments of audit.
+
+Auditors are, thus, in our new framework, equipped with a new tool that tempers risk at the cost of nuance.
+Synthetic data, imperfect as it is, emerges as a pragmatic ally, preserving enough fairness properties for auditing utility without sacrificing the sanctuary of privacy.
+
 %%

### 2024-12-19 paper/paper.tex
Rewrite conclusion

@@
 Auditing AI systems with real data can be dangerous.
-We proffer a new approach that leverages differentially private synthetic data.
-The proposed framework under such privacy guarantees offers a refuge from the vulnerabilities of using real data.
+We propose a new approach that leverages differentially private synthetic data.
+The proposed framework, with its strong privacy guarantees, provides a safe alternative to the risks of using real data.
 
-Despite the fact that some measures' definitions betray the inherent imperfection of synthetic data, the metrics results remain generally consistent with the original data.
-Empirical trials across multiple real-world datasets and real-world models reveal that synthetic data derived from real data sufficiently maintains the fairness properties to serve as instruments of audit.
+Despite the inherent imperfection of synthetic data for some measures, the metrics results remain generally consistent with the original data.
+Experiments on multiple real-world datasets and real-world models reveal that synthetic data derived from real data maintains fairness properties.
 
-Auditors are, thus, in our new framework, equipped with a new tool that tempers risk at the cost of nuance.
-Synthetic data, imperfect as it is, emerges as a pragmatic ally, preserving enough fairness properties for auditing utility without sacrificing the sanctuary of privacy.
+While synthetic data is not perfect, it serves as a practical tool for auditing AI fairness.
+Our framework provides an effective way to audit AI systems without compromising privacy.
+Future work includes applications on larger datasets to validate scalability and explorations of other means of privacy preservation in AI auditing.
 

### 2025-01-07 paper/paper.tex
Added TODOs

@@
 %% article.
+
+% TODO: add to abstract
+
 \begin{abstract}
@@
 \maketitle
+
+% TODO: add to intro to fill 14 pgs
 
@@
 
+% TODO: reverse order
+
 For the competition, \cite{mckenna2021winning} further manually added certain cliques based on his investigation of the competition dataset.
-For example, they manually added the clique (sex,city,income).
-In addition, they would add some edges based on some sophisticated heuristics tailored to that particular dataset.
-We do not consider these additional heuristics for the generality of our approach.
-Meanwhile, his other apporach where the auditor does access the real dataset does not fit our framework.
+For example, they would add some edges based on some sophisticated heuristics tailored to that particular dataset.
+In addition, they manually added the clique (sex,city,income) for the prediction target of income.
+We do not consider these additional ___ for the generality of our approach.
+Meanwhile, his other apporach where the auditor does not access the real dataset does not fit our framework.
 
 While synthetic data generation methods often leverage domain knowledge to improve accuracy, we chose to employ a vanilla approach with only the maximum spanning tree method without incorporating additional heuristics.
-This decision was made due to two main factors: first, the need for more specific domain knowledge about the dataset makes it difficult to identify meaningful dependencies; second, prediction targets may differ from dataset to dataset, which means that tailored heuristics could not be effectively generalized.
+This decision was made due to two main factors: first, the specific domain knowledge about the dataset may not be always readily obvious; second, prediction targets may differ from dataset to dataset, which means that tailored heuristics could not be effectively generalized.
 By avoiding dataset-specific adjustments, our method remains general and applicable to a wide range of datasets, in addition to being more computatioanlly efficient.
@@
 
-Next, several AI models are extracted from various real-life authors from Kaggle.
+Next, several AI models are extracted from various authors from Kaggle.
 They are finetuned to perform well on the original dataset.
@@
 Also, a logistic regression model is finetuned by performing principal component analysis\cite{Prashant1112023}.
+
+% TODO: avg of 100 runs
 
@@
 
+% TODO: clarify "by common sense"
+
 In addition, further experiments showed that, in an alternative assumption where the auditor has knowledge of $(S,Y)$ and can add the edge $(S,Y)$ to the Markov random field before fitting, the synthesized data would have been more accurate, even lowering the error of Conditional Use Accuracy Equality in the COMPAS example.
@@
 
-Although further experiments showed that linking $(S,Y)$ before fitting can somewhat alleviate this problem, the auditor may not always have the background knowledge to identify them; moreover, this improvement is not always guaranteed.
+% Although further experiments showed that linking $(S,Y)$ before fitting can somewhat alleviate this problem. Moreover, this improvement is not always guaranteed.
 

### 2025-01-11 paper/paper.tex
minor

@@
 %% article.
-
-% TODO: add to abstract
 
@@
 
-% TODO: reverse order
-
-For the competition, \cite{mckenna2021winning} further manually added certain cliques based on his investigation of the competition dataset.
+For the competition, \cite{mckenna2021winning} further manually added certain cliques based on their investigation of the competition dataset.
 For example, they would add some edges based on some sophisticated heuristics tailored to that particular dataset.
-In addition, they manually added the clique (sex,city,income) for the prediction target of income.
-We do not consider these additional ___ for the generality of our approach.
-Meanwhile, his other apporach where the auditor does not access the real dataset does not fit our framework.
+In addition, they manually added some particular cliques like (sex,city,income) for the prediction target of income.
+We do not consider these additional optimizations for the generality of our approach.
+Meanwhile, their other apporach where the auditor does not access the real dataset does not fit our framework.
 
@@
 
-% TODO: avg of 100 runs
-
 The AI models and both the original dataset and synthetic datasets are then fed to the fairness checker.
+The synthetic datasets were generated 100 times and the fairness scores averaged across the 100 runs.
 Sensitive attributes are identified based on manual examination with common sense or by referring to \cite{pessach2022review}.
@@
 
-% TODO: clarify "by common sense"
-
-In addition, further experiments showed that, in an alternative assumption where the auditor has knowledge of $(S,Y)$ and can add the edge $(S,Y)$ to the Markov random field before fitting, the synthesized data would have been more accurate, even lowering the error of Conditional Use Accuracy Equality in the COMPAS example.
+In addition, further experiments showed that, by common sense or in an alternative assumption where the auditor has knowledge of $(S,Y)$ and can add the edge $(S,Y)$ to the Markov random field before fitting, the synthesized data would have been more accurate, even lowering the error of Conditional Use Accuracy Equality in the COMPAS example.
 

### 2025-01-11 paper/paper.tex
long abstract draft

@@
 \begin{abstract}
-Auditing AI systems often requires sensitive data, raising security and privacy concerns.
+% fairness auditing
+Fairness auditing of AI systems is essential to prevent inequities.
+By conducting thorough fairness audits, these biases can be identified and quantified.
+% traditional auditing
+Traditional auditing using real-world data raises significant security and privacy risks due to the sensitive nature of the datasets involved.
+It exposes auditors to security risks, as they become custodians of sensitive information and targets for cyberattacks.
+Privacy risks arise even without direct breaches, as analysis of real-world data, even when anonymized or aggregated, can inadvertently expose confidential information.
+% proposed auditing framework
+We propose a framework that employs differentially private synthetic data to audit the fairness of AI systems.
+By applying formal privacy-preserving mechanisms, it generates synthetic data that mirrors key statistical properties of the original dataset while ensuring individual-level privacy.
+This method balances the goal of rigorous fairness auditing and the need of strong privacy protections.
+% contributions
+Through experiments on real datasets like Adult, COMPAS, and Diabetes, we compare fairness metrics of synthetic and real data.
+By analyzing the alignment and discrepancies between these metrics, we assess the capacity of synthetic data to preserve key fairness properties of real data.
+Our results demonstrate the framework's ability to enable meaningful fairness evaluations while safeguarding sensitive information, proving its applicability across various critical and sensitive domains.
+% Auditing AI systems often requires sensitive data, raising security and privacy concerns.
 To address this, we propose a framework that leverages differentially private synthetic data for fairness evaluations.

### 2025-01-12 paper/paper.tex
Expanded intro

--- 2025-01-11 paper/paper.tex
@@
 \begin{abstract}
-Auditing AI systems often requires sensitive data, raising security and privacy concerns.
+Fairness auditing of AI systems can identify and quantify biases.
+However, traditional auditing using real-world data raises security and privacy concerns.
+It exposes auditors to security risks as they become custodians of sensitive information and targets for cyberattacks.
+Privacy risks arise even without direct breaches, as data analyses can inadvertently expose confidential information.
+To address these, we propose a framework that leverages differentially private synthetic data to audit the fairness of AI systems.
+By applying privacy-preserving mechanisms, it generates synthetic data that mirrors the statistical properties of the original dataset while ensuring individual privacy.
+This method balances the goal of rigorous fairness auditing and the need for strong privacy protections.
+Through experiments on real datasets like Adult, COMPAS, and Diabetes, we compare fairness metrics of synthetic and real data.
+By analyzing the alignment and discrepancies between these metrics, we assess the capacity of synthetic data to preserve the fairness properties of real data.
+Our results demonstrate the framework's ability to enable meaningful fairness evaluations while safeguarding sensitive information, proving its applicability across critical and sensitive domains.
+% Auditing AI systems often requires sensitive data, raising security and privacy concerns.
 To address this, we propose a framework that leverages differentially private synthetic data for fairness evaluations.
@@
 
-% TODO: add to intro to fill 14 pgs
-
 \section{Introduction}
@@
 
-Fairness in machine learning has become an important topic as AI systems become widely used.
-Biased AI systems could result in amplified unfairness.
-Ensuring fairness in AI systems is crucial to prevent these biases from being exacerbated by AI systems.
-One approach is to audit the fairness of existing AI systems.
-Quantitative fairness auditing is a process of evaluating the fairness of AI systems with a range of fairness metrics.
-Many metrics have been proposed to help evaluate the fairness of AI systems.
+\subsection{Fairness in AI}
 
-Auditing can evaluate the fairness of AI systems, sometimes revealing cases of unfairness in them.
-For example, investigative journalists at ProPublica found that the COMPAS system, which is used to predict recidivism in the criminal justice system in the United States, is biased against certain demographic groups.
-This highlights the need for fairness auditing conducted by third parties.
+Fairness in machine learning has become an increasingly important topic as AI systems are widely used across various sectors, including healthcare and criminal justice.
+These systems can significantly influence outcomes that impact individuals and communities.
+
+However, AI systems can exhibit bias, which may lead to increased unfairness.
+Biased AI systems have the potential to reinforce historical injustices, erode trust in technology, and exacerbate inequality.
+Therefore, ensuring fairness in AI systems is crucial to prevent the perpetuation of these biases.
+
+For instance, investigative journalists at ProPublica uncovered bias in the COMPAS system, which is used in the United States criminal justice system to predict recidivism.
+Their analysis revealed that the COMPAS system disproportionately affects certain demographic groups.
+
+These findings have raised significant concerns about the fairness and ethical implications of using such AI systems in critical decision-making processes.
+Addressing these biases is essential to ensure that AI systems do not perpetuate existing inequalities and instead contribute to a fairer and more just society.
+
+\subsection{Fairness Auditing}
+
+One effective approach to achieving fairness in AI systems is to conduct audits.
+Quantitative fairness auditing involves evaluating these systems using various fairness metrics to identify potential biases and inequalities.
+Some commonly proposed metrics for assessing AI system fairness include demographic parity, equalized odds, and accuracy equality.
+These metrics provide a quantitative foundation for addressing fairness concerns in AI models.
+
+A well-documented example of fairness auditing is the investigation of the COMPAS system.
+Journalists from ProPublica revealed that COMPAS exhibited bias against certain demographic groups, particularly African Americans.
+The system was more likely to falsely classify African American defendants as high risk for reoffending compared to their white counterparts.
+This finding not only underscored the necessity of fairness auditing but also highlighted the potential harm of deploying biased AI systems in critical areas.
+
+This case emphasizes the importance of independent audits in ensuring fairness.
+Evaluations conducted by third parties, such as those performed by ProPublica, are vital because they operate free from the influence of those who develop or deploy the systems.
+By offering an objective perspective, third-party audits can identify and address biases that internal evaluations might overlook.
+Without such oversight, AI systems risk perpetuating systemic inequalities, making independent auditing a crucial aspect of accountability in AI development.
 
@@
 
+\subsection{Challenges in Auditing}
+
+While fairness auditing is essential, it presents significant challenges, particularly when it involves sensitive data.
 To conduct audits, auditors may rely on access to real datasets containing sensitive information, raising significant security and privacy concerns.
+Auditors often require access to real-world datasets containing sensitive attributes, such as race, gender, or income, to evaluate an AI system's fairness.
+However, this reliance on sensitive data raises concerns about data privacy and security.
+
 This reliance invites data security attacks on auditors, making them targets of unauthorized access.
-Analysis on real data runs the risk of data inference attacks, where confidential information may be deduced from seemingly harmless or aggregated data.
-Various technologies have been developed to mitigate these risks, such as differential privacy, where the idea is that whether or not any individual is in a dataset has a limited impact.
+The use of real datasets for fairness auditing creates a point of vulnerability, making auditors potential targets for data breaches and unauthorized access.
+If sensitive data falls into the wrong hands, it could lead to severe consequences, including identity theft, discrimination, and reputational damage.
 
-To mitigate these risks, the use of synthetic data has been proposed.
-Synthetic data are fake data that is artificially generated from real data.
+Moreover, analyses on real data runs the risk of data inference attacks, where confidential information may be deduced from seemingly harmless or aggregated data.
+Even if the real data is not directly exposed, the results of fairness analyses can sometimes reveal sensitive information through inference attacks.
+For example, attackers could combine publicly available audit results with external datasets to infer private details about individuals in the original dataset.
+
+\subsection{Differentially Privacy}
+
+Various technologies have been developed to mitigate these risks, such as differential privacy.
+Differential privacy is a mathematical framework that ensures the inclusion or exclusion of any individual in a dataset has a minimal and quantifiable impact on the overall results of data analysis.
+This is achieved by introducing carefully calibrated random noise into the computations derived from the data, ensuring that individual records remain indistinguishable while preserving aggregate patterns and trends.
+
+The concept of differential privacy is particularly valuable in scenarios where sensitive information, such as health records or financial data, is involved.
+For example, a differential privacy mechanism could allow researchers to analyze patterns in patient health outcomes without exposing any single patient's medical history.
+This approach strikes a balance between data utility and privacy, enabling meaningful analysis while safeguarding individuals against privacy breaches or inference attacks.
+
+The key idea is that no matter how much background knowledge an attacker has about the data, they cannot determine with high confidence whether a specific individual is included in the dataset.
+This is quantified by some parameters which control the amount of noise introduced.
+Smaller parameters provide stronger privacy but can reduce the accuracy of the analysis, while larger parameters allow for more precise results but with weaker privacy guarantees.
+The challenge is to carefully calibrate the parameters to ensure that privacy is maintained without overly compromising the utility of the data.
+
+\subsection{Synthetic Data}
+
+Synthetic data are fake data that is generated from real data.
+Synthetic data is artificially generated to replicate the statistical properties of real data while protecting individual privacy.
 The principle of this technology is to preserve some statistical properties of the real data while protecting the privacy of the individuals in the real data.
+Unlike anonymized data, synthetic data breaks the link to the original data, reducing the risk of re-identification.
+
 Among the generation techniques, differentially private synthetic data offers a way to investigate the data properties under differential privacy guarantees.
+It stands out for it strong differential privacy guarantees when generating synthetic data.
+This method combines data synthesis with the principles of differential privacy, ensuring that no single individual's information significantly influences the synthetic dataset.
+By introducing controlled randomness during generation, it provides strong privacy guarantees while preserving the overall utility of the data.
+
+Differentially private synthetic data is particularly valuable in sensitive domains like healthcare and finance, enabling researchers to analyze patterns or train AI models without exposing personal details.
+It also supports fairness auditing by allowing the examination of datasets and models without revealing sensitive attributes.
+This dual focus on privacy and utility makes it a valuable tool.
+
+\subsection{Differentially Private Synthetic Data for Fairness Auditing}
 
@@
 Our framework lets the auditors assess the fairness of AI systems without exposing sensitive information.
-Differentially private synthetic data is a technique that generates synthetic data from real data that preserves some statistical properties of the real data while ensuring differential privacy.
-This technology enables auditing without exposing sensitive information.
+By using differentially private synthetic data, auditors can conduct fairness analyses without directly exposing sensitive information.
+
+This method offers a unique solution to reconcile the need for fairness auditing with the imperative to protect privacy.
+By preserving key statistical properties of the original data, synthetic data allows auditors to assess fairness metrics accurately while mitigating the risks of data breaches and privacy violations.
+
+This technology enables auditing without exposing sensitive information, offering a privacy-preserving way to assess AI systems.
 However, synthetic data also introduces new challenges.
+One major concern is whether it accurately reflects the fairness properties of the real data.
 Whether or not it accurately preserves the fairness properties of the real data is a critical question.
+
+Since fairness metrics depend on the relationships between sensitive attributes and outcomes, any discrepancies in how synthetic data mimics these relationships could lead to inaccurate conclusions in fairness audits.
+Ensuring that synthetic data preserves these properties is critical for reliable auditing.
+
+\subsection{Contribution}
 
@@
 
+In this paper, we propose a novel framework for fairness auditing that leverages differentially private synthetic data.
+Our framework enables auditors to evaluate the fairness of AI systems without exposing sensitive information, addressing both privacy and security concerns.
+
 Our work examines the capabilities of existing differentially private synthetic data generation technologies in preserving fairness properties.
 Through empirical experiments on multiple real datasets, we aim to determine the effectiveness of differentially private synthetic data in this respect.
+
+Through our experiments, we evaluate the extent to which synthetic data can approximate fairness metrics computed on original datasets.
+Our findings contribute to the growing body of research on ethical AI and offer insights for practitioners seeking to ensure fairness in AI systems.
+
+\subsection{Structure}
+
+The rest of this paper is organized as follows.
+Section 2 provides the background of related work.
+Section 3 provides the preliminary knowledge.
+Section 4 outlines the motivation behind our proposed framework.
+Section 5 describes our methodology for generating differentially private synthetic data and evaluating fairness metrics.
+Section 6 presents our experimental setup and results.
+Section 7 discusses the implications of our findings.
+Section 8 concludes the paper and outlines future work.
+
+% TODO: future work?
 

### 2025-01-14 paper/paper.tex
Conclusion

@@
 To address these, we propose a framework that leverages differentially private synthetic data to audit the fairness of AI systems.
-By applying privacy-preserving mechanisms, it generates synthetic data that mirrors the statistical properties of the original dataset while ensuring individual privacy.
+By applying privacy-preserving mechanisms, it generates synthetic data that mirrors the statistical properties of the original dataset while ensuring privacy.
 This method balances the goal of rigorous fairness auditing and the need for strong privacy protections.
@@
 Synthetic data are fake data that is generated from real data.
-Synthetic data is artificially generated to replicate the statistical properties of real data while protecting individual privacy.
+Synthetic data is artificially generated to replicate the statistical properties of real data while protecting privacy.
 The principle of this technology is to preserve some statistical properties of the real data while protecting the privacy of the individuals in the real data.
@@
 Section 8 concludes the paper and outlines future work.
-
-% TODO: future work?
 
@@
 We do not consider these additional optimizations for the generality of our approach.
-Meanwhile, their other apporach where the auditor does not access the real dataset does not fit our framework.
+Meanwhile, their other approach where the auditor does not access the real dataset does not fit our framework.
 
@@
 This decision was made due to two main factors: first, the specific domain knowledge about the dataset may not be always readily obvious; second, prediction targets may differ from dataset to dataset, which means that tailored heuristics could not be effectively generalized.
-By avoiding dataset-specific adjustments, our method remains general and applicable to a wide range of datasets, in addition to being more computatioanlly efficient.
+By avoiding dataset-specific adjustments, our method remains general and applicable to a wide range of datasets, in addition to being more computationally efficient.
 
@@
 % Demographic Parity  & 0.1933 & 0.1079 & 0.0853 & 0.0114 & 0.1818 \\
-% Overall Accuracy Eqaulity   & 0.0250 & 0.1399 & 0.1149 & 0.0169 & 0.0080 \\
+% Overall Accuracy Equality   & 0.0250 & 0.1399 & 0.1149 & 0.0169 & 0.0080 \\
 % Equalized Odds (False Positive)    & 0.0175 & 0.0870 & 0.0695 & 0.0060 & 0.0115 \\
@@
 Demographic Parity  & 0.1933 & 0.0114 & 0.1818 \\
-Overall Accuracy Eqaulity   & 0.0250 & 0.0169 & 0.0080 \\
+Overall Accuracy Equality   & 0.0250 & 0.0169 & 0.0080 \\
 Equalized Odds (False Positive)    & 0.0175 & 0.0060 & 0.0115 \\
@@
 Demographic Parity  & 0.1310 & 0.0809 & 0.0501 \\
-Overall Accuracy Eqaulity   & 0.0079 & 0.0146 & 0.0067 \\
+Overall Accuracy Equality   & 0.0079 & 0.0146 & 0.0067 \\
 Equalized Odds (False Positive)    & 0.0249 & 0.0802 & 0.0553 \\
@@
 Demographic Parity  & 0.0135 & 0.0015 & 0.0119 \\
-Overall Accuracy Eqaulity   & 0.0077 & 0.0011 & 0.0065 \\
+Overall Accuracy Equality   & 0.0077 & 0.0011 & 0.0065 \\
 Equalized Odds (False Positive)    & 0.0000 & 0.0010 & 0.0010 \\
 Equalized Odds (True Positive)    & 0.0086 & 0.0094 & 0.0008 \\
-Condtional Use Accuracy Equality (True Positive) & 0.0133 & 0.0059 & 0.0074 \\
-Condtional Use Accuracy Equality (True Negative) & 0.0216 & 0.0019 & 0.0197 \\
+Conditional Use Accuracy Equality (True Positive) & 0.0133 & 0.0059 & 0.0074 \\
+Conditional Use Accuracy Equality (True Negative) & 0.0216 & 0.0019 & 0.0197 \\
 \bottomrule
@@
 
-Auditing AI systems with real data can be dangerous.
-We propose a new approach that leverages differentially private synthetic data.
-The proposed framework, with its strong privacy guarantees, provides a safe alternative to the risks of using real data.
-
-Despite the inherent imperfection of synthetic data for some measures, the metrics results remain generally consistent with the original data.
-Experiments on multiple real-world datasets and real-world models reveal that synthetic data derived from real data maintains fairness properties.
-
-While synthetic data is not perfect, it serves as a practical tool for auditing AI fairness.
-Our framework provides an effective way to audit AI systems without compromising privacy.
-Future work includes applications on larger datasets to validate scalability and explorations of other means of privacy preservation in AI auditing.
+Auditing AI systems with real data can be dangerous due to the potential risks to privacy and the possibility of exposing sensitive information.
+When evaluating an AI system with personal data, there is a real danger of inadvertently leaking private details about individuals involved in the dataset.
+
+To mitigate this risk, we propose a framework that leverages differentially private synthetic data for fairness audits.
+Instead of using real data, it generates synthetic data that preserves key patterns of real data but, at the same time, protects individuals' privacy.
+
+The proposed framework, backed by strong privacy guarantees, offers a secure alternative to directly using real data.
+By applying differential privacy methods, the synthetic data shields individual information from exposure while still enabling thorough fairness evaluations.
+
+Experiments conducted on multiple real-world datasets and models show that synthetic data derived from real data retains essential fairness properties.
+This ensures that any biases present in the original data are captured and reflected in the synthetic counterpart.
+
+While synthetic data is not a flawless substitute for real-world data, it serves as a practical and pragmatic tool for auditing AI fairness in a privacy-preserving manner.
+Our framework offers an effective means of testing AI systems for fairness while mitigating the privacy concerns surrounding using real data in sensitive applications.
+Auditors can perform thorough fairness evaluations by generating and using synthetic data while under strong privacy protections.
+
+Future work could focus on applying this framework to larger, more complex datasets, which would help validate the framework's scalability.
+Furthermore, other privacy-preserving techniques could be explored to complement synthetic data and expand the scope of AI fairness auditing while maintaining privacy.
+Finally, translating these technical advancements into real-world applications requires policy, legal, and industry collaborations.
+Research on the legal, ethical, and societal implications of differential privacy and synthetic data will be crucial for broad adoption.
 

### 2025-01-15 paper/paper.tex
Major

@@
 For instance, investigative journalists at ProPublica uncovered bias in the COMPAS system, which is used in the United States criminal justice system to predict recidivism.
-Their analysis revealed that the COMPAS system disproportionately affects certain demographic groups.
+Their analysis revealed that the COMPAS system disproportionately discriminated against certain demographic groups.
 
@@
 Some commonly proposed metrics for assessing AI system fairness include demographic parity, equalized odds, and accuracy equality.
-These metrics provide a quantitative foundation for addressing fairness concerns in AI models.
+These metrics provide a quantitative basis for addressing fairness concerns in AI models.
 
@@
 Journalists from ProPublica revealed that COMPAS exhibited bias against certain demographic groups, particularly African Americans.
-The system was more likely to falsely classify African American defendants as high risk for reoffending compared to their white counterparts.
+The system was more likely to falsely classify African American defendants as high risk compared to their Caucasian counterparts.
 This finding not only underscored the necessity of fairness auditing but also highlighted the potential harm of deploying biased AI systems in critical areas.
@@
 While fairness auditing is essential, it presents significant challenges, particularly when it involves sensitive data.
-To conduct audits, auditors may rely on access to real datasets containing sensitive information, raising significant security and privacy concerns.
+To conduct audits, auditors may rely on access to real datasets containing sensitive information.
 Auditors often require access to real-world datasets containing sensitive attributes, such as race, gender, or income, to evaluate an AI system's fairness.
-However, this reliance on sensitive data raises concerns about data privacy and security.
+However, this reliance on sensitive data raises concerns about data security and privacy.
 
@@
 
-Moreover, analyses on real data runs the risk of data inference attacks, where confidential information may be deduced from seemingly harmless or aggregated data.
-Even if the real data is not directly exposed, the results of fairness analyses can sometimes reveal sensitive information through inference attacks.
+Moreover, analyses of real data run the risk of data inference attacks, where confidential information may be deduced from seemingly harmless or aggregated data.
+Even if the real data is not directly exposed, the results of analyses can sometimes reveal sensitive information through inference attacks.
 For example, attackers could combine publicly available audit results with external datasets to infer private details about individuals in the original dataset.
@@
 
-Various technologies have been developed to mitigate these risks, such as differential privacy.
+Various technologies have been developed to mitigate privacy risks, such as differential privacy.
 Differential privacy is a mathematical framework that ensures the inclusion or exclusion of any individual in a dataset has a minimal and quantifiable impact on the overall results of data analysis.
@@
 The concept of differential privacy is particularly valuable in scenarios where sensitive information, such as health records or financial data, is involved.
-For example, a differential privacy mechanism could allow researchers to analyze patterns in patient health outcomes without exposing any single patient's medical history.
+For example, a differential privacy mechanism could allow researchers to analyze patterns in patient health data without exposing any single patient's medical history.
 This approach strikes a balance between data utility and privacy, enabling meaningful analysis while safeguarding individuals against privacy breaches or inference attacks.
@@
 It stands out for it strong differential privacy guarantees when generating synthetic data.
-This method combines data synthesis with the principles of differential privacy, ensuring that no single individual's information significantly influences the synthetic dataset.
+This method combines data synthesis with the principles of differential privacy, ensuring that individuals' sensitive information cannot be inferred from the synthetic data.
 By introducing controlled randomness during generation, it provides strong privacy guarantees while preserving the overall utility of the data.
 
-Differentially private synthetic data is particularly valuable in sensitive domains like healthcare and finance, enabling researchers to analyze patterns or train AI models without exposing personal details.
+Differentially private synthetic data is particularly valuable in sensitive domains like healthcare and finance, enabling researchers to analyze patterns or identify trends without exposing personal details.
 It also supports fairness auditing by allowing the examination of datasets and models without revealing sensitive attributes.
@@
 
-\subsection{Differentially Private Synthetic Data for Fairness Auditing}
+\subsection{Contribution}
 
@@
 By using differentially private synthetic data, auditors can conduct fairness analyses without directly exposing sensitive information.
+
+We present an innovative solution to the issue of sensitive data access: auditors generate synthetic data immediately upon receiving the real dataset, which they retain for auditing purposes while discarding the original data.
 
@@
 
-\subsection{Contribution}
-
-% contribution
-
-In this paper, we propose a novel framework for fairness auditing that leverages differentially private synthetic data.
-Our framework enables auditors to evaluate the fairness of AI systems without exposing sensitive information, addressing both privacy and security concerns.
-
 Our work examines the capabilities of existing differentially private synthetic data generation technologies in preserving fairness properties.
-Through empirical experiments on multiple real datasets, we aim to determine the effectiveness of differentially private synthetic data in this respect.
+Through empirical experiments on multiple real datasets, we aim to determine the effectiveness of differentially private synthetic data in fairness auditing.
+
+We perform a comparative analysis of fairness metrics computed on real and synthetic data across multiple real-world datasets, including Adult, COMPAS, and Diabetes.
+By examining the consistency and differences between these metrics, we evaluate how well synthetic data captures the fairness characteristics of real data.
 

### 2025-01-16 paper/paper.tex
Added TODOs
Added 3 models results

@@
 
-\subsection{Fairness in AI}
+% \subsection{Fairness in AI}
 
@@
 
-\subsection{Fairness Auditing}
+% \subsection{Fairness Auditing}
 
@@
 
-\subsection{Challenges in Auditing}
+% \subsection{Challenges in Auditing}
 
@@
 
-\subsection{Differentially Privacy}
+% \subsection{Differentially Privacy}
 
@@
 
-\subsection{Synthetic Data}
-
+% \subsection{Synthetic Data}
+
+One way of auditing while preserving privacy is to use synthetic data.
 Synthetic data are fake data that is generated from real data.
@@
 
-\subsection{Contribution}
+% \subsection{Contribution}
 
@@
 
-\subsection{Structure}
+% \subsection{Structure}
 
@@
 
+% TODO: add to evaluation
+% TODO: add to conclusion
+
 To test the viability of our method, we compare the metrics computed from the synthetic dataset against those of the original dataset.
@@
 They are finetuned to perform well on the original dataset.
-For one, a random forest model is finetuned by searching hyperparameters settings\cite{Ipbyrne2023}.
-Another random forest model is finetuned with over-sampling methods\cite{Jawat2024}.
-Also, a logistic regression model is finetuned by performing principal component analysis\cite{Prashant1112023}.
+For the Adult dataset, we selected three models to experiment: a random forest model is finetuned by hyperparameter search\cite{Ipbyrne2023}; a logistic regression model is finetuned by performing principal component analysis\cite{Prashant1112023}; and a KNN model is manually finetuned\cite{Kothari2020}.
+For the COMPAS dataset, we selected a random forest model finetuned by hyperparameter search\cite{Sky2024}.
+For the Diabetes dataset, we selected a random forest model finetuned by over-sampling and under-sampling techniques\cite{Jawat2024}.
 
 The AI models and both the original dataset and synthetic datasets are then fed to the fairness checker.
-The synthetic datasets were generated 100 times and the fairness scores averaged across the 100 runs.
+The synthetic datasets were generated 100 times for each model and the fairness scores averaged across the 100 runs.
 Sensitive attributes are identified based on manual examination with common sense or by referring to \cite{pessach2022review}.
@@
 We set the sensitive attribute as sex and the protected group as female.
-The results are shown in Table~\ref{tab:adult_score}.
+We tested three models: a random forest model, a logistic regression model, and a KNN model.
+The results are shown in Table~\ref{tab:adult_score_rf}, \ref{tab:adult_score_lr}, and \ref{tab:adult_score_knn}.
+The synthetic data generator fit time is 17 minutes and 1 second.
 
@@
 \caption{
-    Fairness measures experiment results of the Adult dataset.
+    Fairness measures experiment results of the Adult dataset on a random forest model.
     % With heuristic, average difference is $0.0787$, and fit time is 924m15s.
-    Average difference is $0.0775$, and fit time is 17m1s.
+    Average difference is $0.0775$.
 }
-% \label{tab:adult_score}
-% \begin{tabular}{ccccccc}
-% \toprule
-% \textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{difference} & \textbf{Synthetic(No Heuristic)} & \textbf{difference(No Heuristic)} \\
-% \midrule
-% Demographic Parity  & 0.1933 & 0.1079 & 0.0853 & 0.0114 & 0.1818 \\
-% Overall Accuracy Equality   & 0.0250 & 0.1399 & 0.1149 & 0.0169 & 0.0080 \\
-% Equalized Odds (False Positive)    & 0.0175 & 0.0870 & 0.0695 & 0.0060 & 0.0115 \\
-% Equalized Odds (True Positive)    & 0.0114 & 0.0622 & 0.0508 & 0.0303 & 0.0189 \\
-% CU Accuracy Equality (True Positive) & 0.1941 & 0.1466 & 0.0474 & 0.0315 & 0.1626 \\
-% CU Accuracy Equality (True Negative) & 0.1102 & 0.1450 & 0.0348 & 0.0299 & 0.0803 \\
-% \bottomrule
-% \end{tabular}
-% \end{table}
-
-\label{tab:adult_score}
+\label{tab:adult_score_rf}
 \begin{tabular}{lccc}
@@
 
+\begin{table}[h]
+\caption{
+    Fairness measures experiment results of the Adult dataset on a logistic regression model.
+    Average difference is $0.0829$.
+}
+\label{tab:adult_score_lr}
+\begin{tabular}{lccc}
+\toprule
+\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} \\
+\midrule
+Demographic Parity  & 0.0139 & 0.0047 & 0.0092 \\
+Overall Accuracy Equality   & 0.0992 & 0.0149 & 0.0843 \\
+Equalized Odds (False Positive)    & 0.0017 & 0.0066 & 0.0049 \\
+Equalized Odds (True Positive)    & 0.0080 & 0.0072 & 0.0008 \\
+Conditional Use Accuracy Equality (True Positive) & 0.3459 & 0.0305 & 0.3154 \\
+Conditional Use Accuracy Equality (True Negative) & 0.1120 & 0.0291 & 0.0829 \\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[h]
+\caption{
+    Fairness measures experiment results of the Adult dataset on a KNN model.
+    Average difference is $0.0945$.
+}
+\label{tab:adult_score_knn}
+\begin{tabular}{lccc}
+\toprule
+\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} \\
+\midrule
+Demographic Parity & 0.1721 & 0.0046 & 0.1675 \\
+Overall Accuracy Equality &  0.0473 & 0.0128 & 0.0344 \\
+Equalized Odds (False Positive) &   0.0571 & 0.0072 & 0.0499 \\
+Equalized Odds (True Positive) &   0.1667 & 0.0110 & 0.1557 \\
+Conditional Use Accuracy Equality (True Positive) & 0.1009 & 0.0288 & 0.0720 \\
+Conditional Use Accuracy Equality (True Negative) & 0.1193 & 0.0319 & 0.0874 \\
+\bottomrule
+\end{tabular}
+\end{table}
+
 \subsection{COMPAS Dataset}
@@
 The results are shown in Table~\ref{tab:compas_score}.
+The synthetic data generator fit time is 33 seconds.
 
@@
 \caption{
-    Fairness measures experiment results of the COMPAS dataset.
+    Fairness measures experiment results of the COMPAS dataset on a random forest model.
     % With heuristic, average difference is $0.0750$, and fit time is 27m33s.
-    Average difference is $0.0727$, and fit time is 33s.
+    Average difference is $0.0727$.
 }
@@
 The results are shown in Table~\ref{tab:diabetes_score}.
+The synthetic data generator fit time is 1 minute and 24 seconds.
 
@@
 \caption{
-    Fairness measures experiment results of the Diabetes dataset.
+    Fairness measures experiment results of the Diabetes dataset on a random forest model.
     % With heuristic, average difference is $0.0067$, and fit time is 1m44s.
-    Average difference is $0.0078$, and fit time is 1m24s.
+    Average difference is $0.0078$.
 }
@@
 Furthermore, other privacy-preserving techniques could be explored to complement synthetic data and expand the scope of AI fairness auditing while maintaining privacy.
+Other means of auditing for certain fairness metrics, such as Conditional Use Accuracy Equality, that are not well suited for synthetic data can be explored.
 Finally, translating these technical advancements into real-world applications requires policy, legal, and industry collaborations.

### 2025-01-19 paper/paper.tex
Cleared TODOs

@@
 Fairness in machine learning has become an increasingly important topic as AI systems are widely used across various sectors, including healthcare and criminal justice.
-These systems can significantly influence outcomes that impact individuals and communities.
+These AI systems can significantly influence outcomes that impact individuals and communities.
 
@@
 The key idea is that no matter how much background knowledge an attacker has about the data, they cannot determine with high confidence whether a specific individual is included in the dataset.
-This is quantified by some parameters which control the amount of noise introduced.
-Smaller parameters provide stronger privacy but can reduce the accuracy of the analysis, while larger parameters allow for more precise results but with weaker privacy guarantees.
+This is quantified by some parameters which control the amount of noise introduced; smaller parameters provide stronger privacy but can reduce the accuracy of the analysis, while larger parameters allow for more precise results but with weaker privacy guarantees.
 The challenge is to carefully calibrate the parameters to ensure that privacy is maintained without overly compromising the utility of the data.
@@
 
-% TODO: add to evaluation
-% TODO: add to conclusion
-
 To test the viability of our method, we compare the metrics computed from the synthetic dataset against those of the original dataset.
@@
 
-The average of the differences between the fairness measure values of the original and synthetic datasets is below 0.1 for all datasets.
-This indicates that synthetic data is a good approximation of the original data in terms of fairness.
+The average of the differences between the fairness measure values of the original and synthetic datasets is below $0.1$ for all datasets across all models.
+Judging from different metrics, datasets, and models, this indicates that synthetic data is a good approximation of the original data in terms of fairness.
 
@@
 
-In the Adult experiment, Conditional Use Accuracy Equality (True Positive) has an error of around 0.16.
-In the COMPAS experiment, both Conditional Use Accuracy Equality measures had an error over 0.1.
-In the Diabetes experiment, Conditional Use Accuracy Equality (True Negative) has an error much higher than other measures.
+In the Adult random forest experiment, Conditional Use Accuracy Equality (True Positive) has an error of around 0.16.
+In the COMPAS random forest experiment, both Conditional Use Accuracy Equality measures had an error over 0.1.
+In the Diabetes random forest experiment, Conditional Use Accuracy Equality (True Negative) has an error much higher than other measures.
 
@@
 
-Experiments conducted on multiple real-world datasets and models show that synthetic data derived from real data retains essential fairness properties.
+Experiments conducted on multiple real-world datasets and across different models show that synthetic data derived from real data retains essential fairness properties.
 This ensures that any biases present in the original data are captured and reflected in the synthetic counterpart.

### 2025-01-20 paper/paper.tex
minor

@@
 These findings have raised significant concerns about the fairness and ethical implications of using such AI systems in critical decision-making processes.
-Addressing these biases is essential to ensure that AI systems do not perpetuate existing inequalities and instead contribute to a fairer and more just society.
+Addressing these biases is essential to ensure that AI systems do not perpetuate inequalities.
 
@@
 
-The concept of differential privacy is particularly valuable in scenarios where sensitive information, such as health records or financial data, is involved.
+Differential privacy is especially useful in situations that involve sensitive data.
 For example, a differential privacy mechanism could allow researchers to analyze patterns in patient health data without exposing any single patient's medical history.
@@
 
-Differentially private synthetic data is particularly valuable in sensitive domains like healthcare and finance, enabling researchers to analyze patterns or identify trends without exposing personal details.
+Differentially private synthetic data is particularly valuable in sensitive domains like healthcare and criminal justice, enabling researchers to analyze patterns or identify trends without exposing personal details.
 It also supports fairness auditing by allowing the examination of datasets and models without revealing sensitive attributes.

### 2025-01-20 paper/paper.tex
minor

@@
 Different tools have been developed to check the fairness of AI models\cite{saleiro2018aequitas,bellamy2019ai,bird2020fairlearn}.
-We use a tool produced from our previous work\cite{yuan2024ensuring}.
+We use a tool produced from \cite{yuan2024ensuring}.
 
@@
 
-In the framework of our previous work\cite{yuan2024ensuring}, after obtaining real data from the data provider, the 3rd party auditor holds onto the real data for performing fairness audits, and it supposedly retains it indefinitely for the possibility of any future audits.
+In the framework of \cite{yuan2024ensuring}, after obtaining real data from the data provider, the 3rd party auditor holds onto the real data for performing fairness audits, and it supposedly retains it indefinitely for the possibility of any future audits.
 However, this practice raises both security and privacy concerns.
@@
 
-We employed the tools of the winner of the 2018 NIST differential privacy Synthetic Data Challenge competition\cite{NIST2018} by \cite{nist_ryan_2018,McKenna_private-PGM_2021,mckenna2021winning,mckenna2019graphical} and the fairness checker tool from our previous research\cite{yuan2024ensuring}.
+We employed the tools of the winner of the 2018 NIST differential privacy Synthetic Data Challenge competition\cite{NIST2018} by \cite{nist_ryan_2018,McKenna_private-PGM_2021,mckenna2021winning,mckenna2019graphical} and the fairness checker tool from \cite{yuan2024ensuring}.
 

### 2025-01-21 paper/paper.tex
minor

@@
 We employed the tools of the winner of the 2018 NIST differential privacy Synthetic Data Challenge competition\cite{NIST2018} by \cite{nist_ryan_2018,McKenna_private-PGM_2021,mckenna2021winning,mckenna2019graphical} and the fairness checker tool from \cite{yuan2024ensuring}.
-
-This research is conducted in Python Jupyter notebooks and is publicly available.
 
@@
 
+This research is conducted in Python Jupyter notebooks and is publicly available. The experiments were conducted on a macOS laptop with an Intel Core i9-9880H CPU (2.3GHz) and 32GB of RAM.
+
 % \begin{figure}[h]
@@
 The average of the differences between the fairness measure values of the original and synthetic datasets is below $0.1$ for all datasets across all models.
-Judging from different metrics, datasets, and models, this indicates that synthetic data is a good approximation of the original data in terms of fairness.
+Different models applied to the same datasets can yield different results, and judging from different metrics, datasets, and models, this indicates that synthetic data is a good approximation of the original data in terms of fairness.
 

### 2025-05-19 slides/2025_6_3.tex
Added 6.3 slides

\documentclass{beamer}

\usetheme{CambridgeUS}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\usepackage{CJKutf8}
\usepackage{datetime}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{subcaption}
\usepackage{minted}
\usepackage{xcolor}
\usepackage{ulem}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{multirow}
\usepackage{makecell}
\usepackage{url}
\usepackage{placeins}

\graphicspath{{images/}}
\DeclareGraphicsExtensions{.pdf}

\newdate{date}{03}{06}{2025}
\date{\displaydate{date}}
\title[Fairness]{Quantitative Auditing of AI Fairness with Differentially Private Synthetic Data}
\author[Rex]{
    \begin{CJK}{UTF8}{bsmi}袁至誠\end{CJK}\newline
    Chih-cheng Rex Yuan\newline
    \href{https://rexyuan.com/}{rexyuan.com}
    }
\institute[IIS,AS]{Institute of Information Science, Academia Sinica}

\DeclarePairedDelimiter{\set}{\{}{\}}
\DeclarePairedDelimiter{\tuple}{(}{)}
\DeclarePairedDelimiter{\abs}{\lvert}{\rvert}

\let\oldleq\leq
\renewcommand{\leq}[1][]{\oldleq_{#1}}
\renewcommand{\implies}{\rightarrow}

\newcommand{\bye}[1]{}

\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\sred}[1]{\textcolor{red}{\sout{#1}}}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}{Why Fairness Audits Matter}
  \begin{itemize}
    \item AI systems are influencing justice, health, finance.
    \item Bias in AI means real-world discrimination.
    \item Example: COMPAS audit by ProPublica.
  \end{itemize}
\end{frame}

\begin{frame}{Auditing Framework Overview}
    \includegraphics[width=\linewidth]{compas}
\end{frame}

\begin{frame}{The Privacy Problem}
  \begin{itemize}
    \item Auditors need sensitive data to test fairness.
    \item But holding this data introduces security and privacy risks.
    \item Security risk: hackers could steal the data.
    \item Privacy risk: published stats could expose insights.
  \end{itemize}
\end{frame}

\begin{frame}{Solution: Privacy-Preserving Audits}
  \begin{itemize}
    \item Use synthetic data generated from real data.
    \item Apply differentially private synthetic data to ensure individual info stays hidden.
    \item Auditors only keep the synthetic data and not the real data.
  \end{itemize}
\end{frame}

\begin{frame}{What Is Differentially Private Synthetic Data?}
  \begin{itemize}
    \item Fake data that mimic the real data's patterns.
    \item Generated with differential privacy, which adds noise to protect privacy.
    \item Lets auditors analyze fairness without exposing personal data.
  \end{itemize}
\end{frame}

\begin{frame}{How The Synthetic Data Are Generated}
  \begin{itemize}
    \item We use a proven method that won a U.S. government competition (NIST, 2018).
    \item It adds noise to protect privacy while preserving overall patterns.
    \item The result: data that looks real but contains no real individuals.
  \end{itemize}
\end{frame}

\begin{frame}{Does It Work?}
  \begin{itemize}
    \item Compared fairness metrics on real and synthetic data.
    \item Datasets: Adult, COMPAS, Diabetes.
    \item Most metrics are within negligible difference.
  \end{itemize}
\end{frame}

\begin{frame}{Policy Implications}
  \begin{itemize}
    \item Enables safer third-party audits under privacy guarantees.
    \item Avoids liability for storing sensitive datasets.
  \end{itemize}
\end{frame}

\begin{frame}{Conclusion}
  \begin{itemize}
    \item Synthetic data can support fairness audits with privacy.
    \item Our framework is practical and provably private.
    \item Opens new pathways for legal oversight of AI systems.
  \end{itemize}

  Slides: \url{https://github.com/RexYuan/Eunectes}.
\end{frame}

\end{document}

### 2025-05-25 slides/2025_6_3.tex
Added to slides

@@
 
-\begin{frame}{Auditing Framework Overview}
+\begin{frame}
+    \frametitle{COMPAS}
+    \textbf{recidivism} \textit{noun} \\
+    \hspace*{1em} the tendency of a convicted criminal to reoffend.
+    \begin{columns}[T]
+        \begin{column}{.5\textwidth}
+            \centering
+            \includegraphics[width=.5\textwidth]{PRATER.jpg}
+            \footnotesize
+            \begin{itemize}
+                \item Prior Offenses: 2 armed robberies, 1 attempted armed robbery
+                \item Subsequent Offenses: 1 grand theft
+                \item Risk Score: 3
+            \end{itemize}
+        \end{column}
+        \begin{column}{.5\textwidth}
+            \centering
+            \includegraphics[width=.5\textwidth]{BORDEN.jpg}
+            \footnotesize
+            \begin{itemize}
+                \item Prior Offenses: 4 juvenile misdemeanors
+                \item Subsequent Offenses: None
+                \item Risk Score: 8
+            \end{itemize}
+        \end{column}
+    \end{columns}
+\end{frame}
+
+\begin{frame}
+    \frametitle{COMPAS}
+    \begin{itemize}
+        \item COMPAS is an algorithm
+        used by U.S. courts for predicting recidivism based on a
+        questionaire.
+        \item In 2016, ProPublica found that the algorithm is biased.
+        \begin{quote}
+            Black defendants were often predicted to be at a higher risk of recidivism than they actually were.
+            White defendants were often predicted to be less risky than they were.
+        \end{quote}
+        \item The false-positive rates vary significantly across
+        black people and white people, violating \textit{equalized odds}.
+    \end{itemize}
+    \footnotetext[1]{\href{https://www.propublica.org/article/how-we-analyzed-the-compas-recidivism-algorithm}{(Link) ProPublica - How We Analyzed the COMPAS Recidivism Algorithm}}
+    \footnotetext[2]{\href{https://www.youtube.com/watch?v=TqnYf2h6A-k}{(Link) Vsauce2 - The Dangerous Math Used To Predict Criminals}}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Fairness Metrics: Equalized Odds}
+    \begin{itemize}
+        \item Equalized odds measures whether a model's error rates are balanced across groups.
+        \item In other words, it asks: \textit{Does the model make mistakes equally, regardless of group membership?}
+        \item Formally, it requires that
+        \begin{align*}
+            \abs{P[\hat{Y} = 1 | S = 1, Y = 0] - P[\hat{Y} = 1 | S \neq 1, Y = 0]} & \leq \epsilon \\
+            \abs{P[\hat{Y} = 1 | S = 1, Y = 1] - P[\hat{Y} = 1 | S \neq 1, Y = 1]} & \leq \epsilon
+        \end{align*}
+        where $\hat{Y}$ is the predicted outcome, $Y$ is the ground truth, and $S$ is the sensitive attribute.
+        \item It ensures that both false positive and true positive rates are similar across groups.
+    \end{itemize}
+\end{frame}
+
+\begin{frame}{Auditing Framework}
     \includegraphics[width=\linewidth]{compas}
@@
 \begin{frame}{The Privacy Problem}
+  The COMPAS audit was possible only because the U.S. law made the data
+  publicly accessible. Otherwise, such audits would be infeasible.
   \begin{itemize}
@@
     \item But holding this data introduces security and privacy risks.
-    \item Security risk: hackers could steal the data.
-    \item Privacy risk: published stats could expose insights.
+    \item Security risk: hackers could steal the data. \\ Example: \href{https://en.wikipedia.org/wiki/23andMe_data_leak}{(Link) 23andMe data breach}.
+    \item Privacy risk: published stats could expose insights. \\ Example: \href{https://pmc.ncbi.nlm.nih.gov/articles/PMC8766950/}{(Link) All of Us inference attack}.
   \end{itemize}
@@
     \item Use synthetic data generated from real data.
-    \item Apply differentially private synthetic data to ensure individual info stays hidden.
+    \item Apply differentially private synthetic data generation techniques to ensure individual info stays hidden.
     \item Auditors only keep the synthetic data and not the real data.
@@
 
-\begin{frame}{What Is Differentially Private Synthetic Data?}
+\begin{frame}{Data Marginals}
+  \begin{columns}
+    \begin{column}{0.48\textwidth}
+      \centering
+      \textbf{Original Data}
+      \begin{tabular}{|l|l|l|}
+        \hline
+        \textbf{ID} & \textbf{Sex} & \textbf{Race} \\
+        \hline
+        1 & Male   & White \\
+        2 & Female & White \\
+        3 & Female & Black \\
+        4 & Male   & Black \\
+        5 & Female & Black \\
+        6 & Female & White \\
+        \hline
+      \end{tabular}
+    \end{column}
+
+    \begin{column}{0.48\textwidth}
+      \centering
+      \textbf{(Sex,Race) Marginal}
+      \begin{tabular}{|l|l|r|}
+        \hline
+        \textbf{Sex} & \textbf{Race} & \textbf{Count} \\
+        \hline
+        Male   & White & 1 \\
+        Female & White & 2 \\
+        Male   & Black & 1 \\
+        Female & Black & 2 \\
+        \hline
+      \end{tabular}
+    \end{column}
+  \end{columns}
+\end{frame}
+
+\begin{frame}{Differentially Private Synthetic Data}
   \begin{itemize}
     \item Fake data that mimic the real data's patterns.
-    \item Generated with differential privacy, which adds noise to protect privacy.
+    \item Generated with differential privacy, which adds noise to marginals to protect privacy.
     \item Lets auditors analyze fairness without exposing personal data.
@@
 
+\begin{frame}{Noising Marginal}
+  \begin{columns}
+    \begin{column}{0.48\textwidth}
+      \centering
+      \textbf{Original Marginal}
+      \begin{tabular}{|l|l|r|}
+        \hline
+        \textbf{Sex} & \textbf{Race} & \textbf{Count} \\
+        \hline
+        Male   & White & 1 \\
+        Female & White & 2 \\
+        Male   & Black & 1 \\
+        Female & Black & 2 \\
+        \hline
+      \end{tabular}
+    \end{column}
+
+    \begin{column}{0.48\textwidth}
+      \centering
+      \textbf{Noised Marginal}
+      \begin{tabular}{|l|l|r|}
+        \hline
+        \textbf{Sex} & \textbf{Race} & \textbf{Count} \\
+        \hline
+        Male   & White & 0.8 \\
+        Female & White & 2.1 \\
+        Male   & Black & 0.4 \\
+        Female & Black & 1.9 \\
+        \hline
+      \end{tabular}
+    \end{column}
+  \end{columns}
+\end{frame}
+
 \begin{frame}{How The Synthetic Data Are Generated}
   \begin{itemize}
-    \item We use a proven method that won a U.S. government competition (NIST, 2018).
+    \item We use a proven method that won a U.S.
+government competition: \href{https://www.nist.gov/ctl/pscr/open-innovation-prize-challenges/past-prize-challenges/2018-differential-privacy-synthetic}{(Link) NIST 2018}.
     \item It adds noise to protect privacy while preserving overall patterns.
@@
 
+\begin{frame}{Synthetic Data}
+  \begin{columns}
+
+    \begin{column}{0.48\textwidth}
+      \centering
+      \textbf{Original Data}
+      \begin{tabular}{|l|l|l|}
+        \hline
+        \textbf{ID} & \textbf{Sex} & \textbf{Race} \\
+        \hline
+        1 & Male   & White \\
+        2 & Female & White \\
+        3 & Female & Black \\
+        4 & Male   & Black \\
+        5 & Female & Black \\
+        6 & Female & White \\
+        \hline
+      \end{tabular}
+    \end{column}
+
+    \begin{column}{0.48\textwidth}
+      \centering
+      \textbf{Synthetic Data}
+      \begin{tabular}{|l|l|l|}
+        \hline
+        \textbf{ID} & \textbf{Sex} & \textbf{Race} \\
+        \hline
+        1 & Male   & White \\
+        2 & Female & Black \\
+        3 & Female & Black \\
+        4 & Male   & White \\
+        5 & Female & White \\
+        6 & Female & Black \\
+        \hline
+      \end{tabular}
+    \end{column}
+  \end{columns}
+\end{frame}
+
 \begin{frame}{Does It Work?}
   \begin{itemize}
-    \item Compared fairness metrics on real and synthetic data.
-    \item Datasets: Adult, COMPAS, Diabetes.
+    \item We experimented on real datsets: Adult, COMPAS, Diabetes.
+    \item We compared fairness metrics of original and synthetic data.
     \item Most metrics are within negligible difference.
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Equalized Odds on COMPAS: Original vs. Synthetic}
+  \centering
+  \begin{tabular}{|l|c|c|c|}
+    \hline
+    \textbf{Metric} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} \\
+    \hline
+    Equalized Odds (False Positive) & 0.0249 & 0.0802 & 0.0553 \\
+    Equalized Odds (True Positive)  & 0.0177 & 0.0825 & 0.0648 \\
+    \hline
+  \end{tabular}
+\end{frame}
+
+\begin{frame}{Limitations}
+  \begin{itemize}
+    \item Results are not guaranteed to be accurate.
+    \item Complex patterns may be missed.
+    \item Privacy vs precision trade-off.
   \end{itemize}
